### 2020-03-11 paper/sections/abstract.tex
add the paper framework

\begin{abstract}
With the growth of computer vision based applications and services, an explosive amount of images have been uploaded to cloud servers that host such computer vision algorithms, usually in the form of deep learning models. JPEG has been used as the {\em de facto} compression and encapsulation method before one uploads the images, due to its wide adaptation. However, standard JPEG configuration does not always perform well for compressing images that are to be processed by a deep learning model, e.g., the standard quality level of JPEG leads to 50\% of size overhead (compared with the best quality level selection) on ImageNet under the same inference accuracy in popular computer vision models including InceptionNet, ResNet, etc. Knowing this, designing a better JPEG configuration for online computer vision services is still extremely challenging: 1) Cloud-based computer vision models are usually a black box to end-users; thus it is difficult to design JPEG configuration without knowing their model structures. 2) JPEG configuration has to change when different users use it since different input image's features and backend deep learning models. In this paper, we propose a reinforcement learning based JPEG configuration framework. In particular, we design an agent that adaptively chooses the compression quality level according to the input image's features and backend deep learning models. Then we train the agent in a reinforcement learning way to adapt it for different deep learning cloud services that act as the {\em interactive training environment} and feeding a reward with comprehensive consideration of accuracy and data size. In our real-world evaluation on Amazon Rekognition, Face++ and Baidu Vision, our approach can reduce the size of images by 1/2 -- 1/3 while the overall classification accuracy only decreases slightly. To make the solution adaptive to the changing input images, we propose an explore-exploit mechanism to adapt the agent to different ``scenery'' online. In our experiment, once capturing the scenery change, AdaCompress either reloads or retrains the RL agent based on the performance of the cached model to make a proper compression strategy and maintain the inference accuracy.
\end{abstract}

### 2020-03-11 paper/sections/conclusion.tex
add the paper framework

\section{Conclusion}
\label{sec: conclusion}

To reduce the upload traffic load of deep learning applications, most researchers focus on modifying the deep learning model, but this does not apply to the industry because the backend deep model is usually inaccessible for users. We present a heuristic solution using an reinforcement learning based agent to decide the proper compression quality level for each image, according to the input image and the backend service. Our experiments show that for different backend deep learning cloud services and different input image sceneries, using different quality selection strategy can significantly reduce the upload file size overhead while keeping comparable accuracy. Moreover, we design the inference-estimation-querying-retraining mechanism to cope with the input image scenery change and make a proper compression selection strategy for the current scenery. Our experiment result shows that once the scenery changes, the mechanism would either reload a pre-trained agent model or retrain a new
agent intelligently to achieve lower upload file size overhead while maintaining the inference accuracy.

### 2020-03-11 paper/sections/design.tex
add the paper framework

\section{Detailed Design}
\label{sec: design}

\begin{figure*}
    %\begin{tabular}{cc}
    \begin{minipage}{\linewidth}
        \centerline{\includegraphics[width=0.8\linewidth]{figures/conventional-framework.pdf}}
        \begin{center}
            {(a) Conventional solution: fixed user-defined compression quality level}
        \end{center}
%        \vspace{0.3cm}
    \end{minipage}
    \vfill
    \vspace{0.4cm}
    \begin{minipage}{\linewidth}
        \centerline{\includegraphics[width=0.8\linewidth]{figures/adaptive-framework.pdf}}
        \vspace{0.2cm}
        \begin{center}
            {(b) AdaCompress solution: input image and model aware compression}
        \end{center}
    \end{minipage}
    %\end{tabular}
    \vspace{0.1cm}
    \caption{Comparing to the conventional solution, our solution can update the compression strategy based on the backend model feedback}
    \label{fig: framework}
\end{figure*}

A brief framework of AdaCompress is shown in Figure \ref{fig: framework}. Briefly, it is an RL (reinforcement learning) based system to train an agent to choose the proper compression quality level $ c $ for one image to be compressed by JPEG. We discuss the formulation, agent design, reinforcement learning framework, feedback reward, and inference-estimation-querying-retraining mechanism separately in the following subsections. We provide experimental details of all the hyperparameters in Sec. \ref{sec: evaluation}. %% \\

\subsection{Problem Formulation}
\label{subsec: formulation}

% \colorbox{red}{notation table}

Without loss of generality, we denote the cloud deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $, and it has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input $ x \in X_{\rm ref} $. We use this $ \vec{y}_{\rm ref} $ as the ground truth label, and for each image $ x_c $ compressed at compression quality level $ c $, the output $ \vec{y}_c = M(x_c) $. Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $. In general, we use the top-5 accuracy as the following $ \mathcal{A} $, the same as the classification metric of ILSVRC2012~\cite{ILSVRC12}.

\begin{align}
\mathcal{A} =& \frac{1}{k} \sum_{k}\max_jd(l_j, g_k) \\
& l_j \in \vec{y}_c, \quad j=1,...,5 \\
& g_k \in \vec{y}_{\rm ref}, \quad k=1, ..., {\rm length}(\vec{y}_{\rm ref}) \\
& d(x, y) = 1 \ \text{if} \ x=y  \ \text{else} \ 0 
\end{align}

Where $ j = 1,...,5 $ indicates the prediction labels at top-5 score, $ k = 1,...,{\rm length}(\vec{y}_{\rm ref}) $ means that if anyone of the top-5 predicted labels matches one of the predictions from $ \vec{y}_{\rm ref} $, it would be regarded as a correct prediction. In general, we cannot get the cloud deep learning model's in-layer details (e.g., softmax probabilities) for a cloud deep learning service, therefore we use a binary hard label $ d(x, y) \in \{0, 1\} $ to evaluate the accuracy. %% $ d(x, y) \in \{0, 1\} $

We also denote JPEG input images as $ f_{ic} = J(x_i, c) $ that for an input image $ x_i $ and a given compression quality level $ c $, and it outputs a compressed file $ f_{ic} $ at the size of $ s_{ic} $. Especially for a reference compression quality level $ c_{\rm ref} $, the compressed file size is $ s_{\rm ref} $. Besides, the input image from a specific location usually belongs to a particular contextual group. For example, in daytime scenery, the input images are expected to have a bright background and high contrast while nighttime images are usually gray-scaled thermal images. Therefore, the agent in one place and one scenery does not need to know all the contextual features in all places and all sceneries. We formulate this as contextual group $ \mathcal{X} $. This contextual grouping concept is also discussed in the study ~\cite{mcdnn}.

Initially, the agent tries different compression quality levels $ c_{\min} < c < c_{\max}, c \in \mathbb{N} $ to obtain compressed image $ x_c $ from input image $ x $, and an image compressed at a reference level $ c_{\rm ref} $ is also uploaded to the cloud to obtain $ \vec{y}_{\rm ref} $. Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, we can obtain the reference file size $ s_{\rm ref} $ and compressed file size $ s_c $, therefore compute the file compression ratio $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.

\subsection{RL Agent Design}

The RL agent is expected to give a proper compression quality level $ c $ that minimizing the file size $ s_c $ while keeping the accuracy $ \mathcal{A} $. For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $, therefore we can use Deep Q-learning Network \cite{DQN} as the RL agent. But naive Deep Q-learning Network can't work well in this task because of the following challenges: %% \\

\begin{itemize}
    \item The state space of reinforcement learning is too large, and to preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge. 
    \item It takes a long time to train one step in a large inference neural network, making the training process too time-consuming.
    \item The RL agent starts training from random trials and starts learning after it finds better feedback reward. When training from a randomly initialized neural network, the feedback reward is very sparse, making it difficult for the agent to learn.
\end{itemize}

To address these challenges, we use the early layers of a well-trained neural network to extract the structural information of an input image. This is a commonly used strategy in training a deep neural network~\cite{finetunning,finetunning2}. Therefore instead of training an RL agent directly from the input image, we use a pre-trained small neural network to extract the features from the input image to reduce the input dimension and accelerate the training procedure. In this work, we use the early convolution layers of MobileNetV2~\cite{MobileNetV2} as the image feature extractor $ \mathcal{E}(\cdot) $ for its efficiency in image classification. The Deep Q-learning Network $ \phi $ is connected to the feature extractor's last convolution layer. We update the RL agent's policy by changing the parameters of the Deep Q-learning Network $ \phi $ while the feature extractor $ \mathcal{E} $ remains fixed. %% \\

\subsection{Reinforcement Learning Framework}

In a specific scenery where the user input image $ x $ belongs context group $ \mathcal{X} $, we define the contextual information $ \mathcal{X} $, along with the backend cloud model $ M $, as the \emph{emulator environment} $ \{\mathcal{X}, M\} $ of the reinforcement learning problem.

Based on this insight, we formulate the feature extractor's output $ \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}. In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $. We denote the \emph{action-value function} as $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $, then the optimal compression quality level at time $ t $ is $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. In such reinforcement learning formulation, the training phase is to minimize a loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where $ s = \mathcal{E}(f_t) $, and $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $ is the target for the iteration $ i $. Especially, $ r $ is the feedback reward, and $ \rho(s, c) $ is a probability distribution over sequences $ s $ and compression quality level $ c $~\cite{DQN}. When minimizing the distance of the action-value function's output $ Q(\cdot) $ and target $ y_i $, the action-value function $ Q(\cdot) $ outputs a more accurate estimation of an action.

In such a formulation, it is similar to the Deep Q-learning Network problem but not the same. Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, therefore there is no signal from the environment telling that an episode has finished. Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $. In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction, and we decrease the randomness when training. All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its action by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge as the agent's randomness keeps decaying. Finally, the agent's action is based on its historical optimal experiences. The training procedure is presented in Algorithm \ref{alg: rl-train}, and we list the parameters in Sec.~\ref{sec: evaluation}.

\begin{algorithm}[htbp]
    \caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
    \label{alg: rl-train}
    \begin{algorithmic}[1]
        \STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
        \STATE Initialize action-value function $ Q $ with random weights $ \theta $
        \STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
        \FOR {t = 1, $ K $}
        \STATE With probability $ \epsilon $ select a random compression level $ c_t $ otherwise select $ c_t = {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
        \STATE Compress image $ x_t $ at quality $ c_t $ and upload it to the cloud to get result $ (\vec{y}_{\rm ref}, \vec{y}_c) $ and calculate reward $ r = R(\Delta s, \mathcal{A}_c) $
        \STATE Set $ s_{t+1} = s_t $, generate $ c_t, x_{t+1} $ and preprocess $ \phi_{t+1} = \phi \big(\mathcal{E}(f_{t+1})\big) $
        \STATE Store transition $ (\phi_t, c_t, r_t, \phi_{t+1}) $ in $ \mathcal{D} $
        \IF {$ t \mod T == 0 $ and $ t \geq T_{\rm start} $}
        \STATE Sample randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
        \STATE Set $ y_i = r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
        \STATE Compute decay exploration rate \\
        $ \epsilon = 
        \begin{cases}
        \mu_{\rm dec}\cdot \epsilon & \text{ if } \ \mu_{\rm dec}\cdot \epsilon > \epsilon_{\min} \\ 
        \epsilon_{\min}             & \text{ if } \ \mu_{\rm dec}\cdot \epsilon \leq \epsilon_{\min}
        \end{cases} $
        \STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to ~\cite{DQN}
        \ENDIF
        \ENDFOR
    \end{algorithmic}
\end{algorithm}

\subsection{Feedback Reward Design}

In our solution, the agent is trained by the feedback reward from the environment $ \{\mathcal{X}, M\} $. In the above formulation, we defined compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ in compression quality level $ c $. Basically, we want the agent to choose a proper compression quality level that minimizing the file size while remaining acceptable accuracy, therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $. We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the reward function $ R(\Delta s, \mathcal{A}) $. %% \\

\subsection{Inference-Estimation-Querying-Retraining Mechanism}

As a running system, we introduce an inference-estimation-querying-retraining mechanism to cope with the scenery change in the inference phase, building a system with different components to inferring, capturing the scenery change, then either reloading or retraining the RL agent based on the performance of the cached model. The overall system diagram is illustrated in Figure \ref{fig: diagram}.

%\begin{figure}[H]
%    \includegraphics[width=\linewidth]{figures/overall-diagram.pdf}
%    \caption{Diagram of AdaCompress architecture}
%    \label{fig: diagram}
%\end{figure}

\begin{figure*}[htbp]
    \centerline{\includegraphics[width=0.8\linewidth]{figures/overall-diagram.pdf}}
    \vspace{0.2cm}
    \caption{Diagram of AdaCompress architecture}
    \label{fig: diagram}
\end{figure*}

%% The system diagram is shown in Figure \ref{fig: diagram}.
We build up the memory buffer $ \mathcal{D} $ and RL (reinforcement learning) training kernel based on the compression and upload driver. When the RL kernel is called, it will load transitions from the memory buffer $ \mathcal{D} $ to train the compression quality level predictor $ \phi $. When the system is deployed, the pre-trained RL agent $ \phi $ guides the compression driver to compress the input image with an adaptive compression quality level $ c $ according to the input image, then uploads the compressed image to cloud. %% \\

After the AdaCompress is deployed, the input images scenery context $ \mathcal{X} $ may change (e.g., day to night, sunny to rainy), when the scenery changes, the older RL agent's compression selection strategy may not be suitable anymore, causing the overall accuracy decreases. To cope with the scenery change, we invoke an estimator with a probability $ p_{\rm est} $. We do this by generating a random value $ \xi \in (0,1) $ and comparing it to $ p_{\rm est} $. If $ \xi \leq p_{\rm est} $ the estimator would be invoked, and AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, therefore calculate $ \mathcal{A}_i $, and save the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ to the memory buffer $ \mathcal{D} $. The estimator also compares the recent $ n $ steps' average accuracy $ \bar{\mathcal{A}}_n $ and the initial accuracy threshold $ \mathcal{A}_0 $ in memory $ \mathcal{D} $. Once the recent average accuracy is much lower than the initial accuracy threshold, the estimator would query an RL agent model to replace the current agent model and test the performance of the reloaded model. To test the reloaded model's performance, the estimator computes the average accuracy $ \bar{\mathcal{A}}^*_n $. If $ \bar{\mathcal{A}}^*_n $ is still lower than the accuracy threshold, the estimator would invoke the RL training kernel to retrain the agent. Once the estimator discovers that the trained reward is higher than the reward threshold, it would stop the training kernel, cache the trained RL agent and switch back to the normal inference state.

Since the reference image $ x_{\rm ref} $ and the compressed image $ x_i $ are both needed in the retraining phase, causing a large uploading file size overhead, especially when the scenery changes frequently (e.g., day to night, then night to day). To avoid unnecessary upload traffic load in the retraining phase, we build up the model caching library to cache the trained RL agent models. When capturing the scenery change, we query a pre-trained model from the model caching library rather than retraining from scratch. %% \\

AdaCompress adaptively switch itself between four states. The switching policy is shown as Figure~\ref{fig: state-switching}.

%\begin{figure}[H]
%    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm, semithick]
%    \tikzstyle{every state}=[ellipse, align=center, draw=blue, text=black]
%    
%    \node[initial, state] (B)                    {inference};
%    \node[state]         (C) [below right of=B] {retrain};
%    \node[state]         (D) [above right of=C] {estimate};
%    
%    \path   (B) edge [loop above] node {$ \xi > p_{\rm est} $} (B)
%    (B.10)    edge                node {$ \xi \leq p_{\rm est} $} (D.170)
%    (C) edge [below left]      node {$ \bar{r}_n > r_{\rm th} $} (B)
%    edge [loop below] node {$ \bar{r}_n \leq r_{\rm th} $}     (C)
%    (D) edge [loop right] node {$ \xi \leq p_{\rm est} $} (D)
%    (D.190)    edge              node {$ \xi > p_{\rm est} $} (B.-10)
%    (D.225)    edge [below right]      node {$ \bar{\mathcal{A}_n} < \mathcal{A}_0 $} (C);
%    \end{tikzpicture}
%    % \vspace{-0.3cm}
%    \caption{State switching policy}
%    \label{fig: state-switching}
%    %\vspace{-0.8cm}
%\end{figure}

\begin{figure}[H]
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.1cm, semithick]
    \tikzstyle{every state}=[ellipse, align=center, draw=blue, text=black]

    \node[initial, state] (B)                    {inference};
    \node[state]         (C) [below of=B] {retraining};
    \node[state]         (D) [right of=B, node distance=4cm] {estimation};
    \node[state]         (E) [right of=C, node distance=4cm] {model querying};
%    \node[state][rectangle]   (F) [below right of=C, node distance=2.5cm] {Model Library};

    \path   (B) edge [loop above] node {$ \xi > p_{\rm est} $} (B)
    (B.10)    edge                node {$ \xi \leq p_{\rm est} $} (D.170)
    (C) edge [below left]      node {$ \bar{r}_n > r_{\rm th} $} (B)
    edge [loop below] node {$ \bar{r}_n \leq r_{\rm th} $}     (C)
    (D) edge [loop above] node {$ \xi \leq p_{\rm est} $} (D)
    (D.190)    edge              node {$ \xi > p_{\rm est} $} (B.-10)
    (D)    edge [below right]      node {$ \bar{\mathcal{A}_n} < \mathcal{A}_0 $} (E)
    (E) edge [below left] node [left] {$ \bar{\mathcal{A}^*_n} \geq \mathcal{A}_0 $} (B)
    (E) edge [below left] node [below] {$ \bar{\mathcal{A}^*_n} < \mathcal{A}_0 $} (C);
%    (C) edge [below right] node [left] {cache model} (F)
%    (F) edge [below right] node [right] {load model} (E);
    \end{tikzpicture}
    % \vspace{-0.3cm}
    \caption{State switching policy}
    \label{fig: state-switching}
    %\vspace{-0.8cm}
\end{figure}

\subsubsection{\textbf{Inference:}}

For most times, AdaCompress runs in this state. In this state, only the compressed images are uploaded to the cloud to achieve minimum uploading file size overhead. To keep a stable accuracy performance even the input image scenery changes, the agent would occasionally switch to the estimation state with the probability of $ p_{\rm est} $, meanwhile remain the inference state with the probability of $ 1 - p_{\rm est} $. %% \\

\subsubsection{\textbf{Estimation:}}

In this state, the reference image $ x_{\rm ref} $ and compressed image $ x_i $ are uploaded to the cloud simultaneously to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $ which are used to calculate $ \mathcal{A}_i $. In each epoch $ i $ the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ is logged in a memory buffer $ \mathcal{D} $. When the average accuracy $ \bar{\mathcal{A}}_n $ of the latest $ n $ steps is higher than the accuracy threshold $ \mathcal{A}_0 $, it stays in the estimation state with the probability of $ p_{\rm est} $ or switches back into the inference state with the probability of $ 1 - p_{\rm est} $. Once the average accuracy $ \bar{\mathcal{A}}_n $ is lower than the initial accuracy threshold $ \mathcal{A}_0 $, indicating that the current agent is no more suitable for the current input image scenery, AdaCompress turns into the model querying state and loads a new RL agent model from the model caching library. %% \\

Therefore, the estimating probability of $ p_{\rm est} $ is vital to the whole system. On the one hand, the estimator should be invoked occasionally to estimate current agent's accuracy, so that to capture the scenery change on time; on the other hand, the estimator uploads the reference image $ x_{\rm ref} $ along with the compressed image, therefore the uploading file size overhead is greater than the conventional benchmark solution, causing higher upload traffic load. %% \\

To achieve trade-off between the risk of the scenery change and the objective of reducing upload traffic load, we design an accuracy-aware dynamic $ p_{\rm est} $ solution. We first define that after running for $ N $ steps, the recent $ n $ steps' average accuracy is:

\begin{align*}
\bar{\mathcal{A}_n} &=
\begin{cases}
\frac{1}{n}\sum_{i=N-n}^{N} \mathcal{A}_i & \text{ if } N \geq n \\ 
\frac{1}{n}\sum_{i=1}^{n} \mathcal{A}_i & \text{ if } N < n 
\end{cases}
\end{align*}

With this definition, an intuitive formulation of the change of $ p_{\rm est} $ is in inverse proportion of the gradient of $ \mathcal{A} $, meaning that when the recent accuracy is going down, the estimation probability $ p_{\rm est} $ would increase. We formulate that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a scaling factor. With this recursive formula, we have the general term of $ p_{\rm est} $ with an initial estimation probability $ p_0 $ is $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $.

\subsubsection{\textbf{Model Querying:}}

The model querying state is designed to cope with the scenery change before retraining. It loads a new RL agent model from the model caching library and tests whether the loaded agent model is suitable for the current scenery by re-calculating the average accuracy. If the new average accuracy $ \bar{\mathcal{A}}^*_n $ is higher than the accuracy threshold $ \mathcal{A}_0 $, indicating that the loaded agent model is suitable for the current scenery, AdaCompress would switch back to the normal inference state using the loaded agent model. Otherwise, AdaCompress would switch into the retraining state and invokes the RL training kernel to retrain a new RL agent for the current scenery.

In this way, AdaCompress is capable to cope with the scenery change in a cached ``memory'' manner, avoiding retraining the agent model at every scenery change, therefore cutting down the uploading file size overhead. Meanwhile, the agent caching strategy would cause a little storage overhead on local terminal devices.

\subsubsection{\textbf{Retraining:}}

This state is to adapt the agent to the current input image scenery by retraining it with the memory buffer $ \mathcal{D} $, which is similar to the training procedure. The retraining phase has finished upon the recent $ n $ steps' average reward $ \bar{r}_n $ is higher than the user-defined threshold $ r_{\rm th} $. And when the retraining procedure finishes, the memory buffer $ \mathcal{D} $ would be flushed, preparing to save new transitions for the retraining of a next scenery change. The trained RL agent model would be cached in the model caching library and be used to switch to the inference state.

\subsection{Insight of RL Agent's Behavior}
\label{subsec:insight}

In the inference phase, the pre-trained RL agent predicts a proper compression quality level according to the input image's feature. The reference image is not uploaded to the cloud anymore; only the compressed image is uploaded, therefore, the upload traffic load is reduced. We notice that the RL agent's behaviors are various for different input image sceneries and backend cloud services, therefore we try to make further investigations by plotting the RL agent's "attention map" (i.e., visual explanations of why the agent chooses a compression quality level). %% \\

\subsubsection{\textbf{Compression Level Choice Variation:}}

In our experiment, we find that in different cloud application environments, the agent's final chosen compression quality levels can be quite different. As shown in Figure \ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's choices are distributed more evenly. Therefore, the optimal compression strategy should be different for different backend cloud services. This variation is caused by the interaction between the agent and the backend cloud model in the training phase. Since the agent's training procedure is based on a specific backend cloud model $ M_1 $, for another backend cloud model $ M_2 $, the interaction between the agent and $ M_2 $ is quite different. Therefore the agent's best compression quality level selection presents variation for different backend cloud models.

\begin{figure}[htb]
    \includegraphics[width=\linewidth]{figures/quality_chosen.pdf}
    \caption{Histogram of RL agent's best compression quality level selection for different cloud services}
    \label{fig: quality_chosen}
    % \vspace{-0.3cm}
\end{figure}

Moreover, in our experiment, the agent presents different behaviors when the input images change from one dataset to another. Figure \ref{fig: dataset_change} shows the agent's choices for the same backend cloud model (Baidu Vision) but different image datasets. We prepare two datasets indicating two contextual sceneries. We randomly sample images from ImageNet~\cite{ImageNet} whose images are mostly taken in the daytime, to act as a daytime scenery, and randomly select nighttime images from the FLIR Thermal Dataset~\cite{FLIR} to form another dataset to act as a nighttime scenery. The histogram shown in Figure~\ref{fig: dataset_change} points out that, for the ImageNet images, the agent prefers a lower compression quality level, but its choices are distributed more evenly. For the FLIR Thermal images, the agent's choices are more accumulated in some relatively high compression quality levels. We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection changes as well. This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features. %% \\

%\begin{figure}[H]
%    \includegraphics[width=\linewidth]{figures/dataset_change.pdf}
%    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
%    \label{fig: dataset_change}
%\end{figure}

\begin{figure}[htb]
    \includegraphics[width=\linewidth]{figures/dataset_change.eps}
    \caption{Histogram of RL agent's best compression quality level selection for different input image sceneries}
    \label{fig: dataset_change}
\end{figure}

\subsubsection{\textbf{Attention Map Variation:}}
\label{subsec: attention map}

To take insight investigations, we plot the importance map of a chosen compression quality level. We leverage a conventional visualization algorithm, Grad-Cam, to observe the Deep Q-Learning Network's interest when choosing compression quality levels. Grad-Cam is a widely used solution to present the importance map of a deep neural network, it is done by calculating the gradients of each target concept and backtracking to the final convolution layer. In this work, we plot the RL agent's attention map by Grad-Cam in Figure~\ref{fig: attention}. %% \\

\begin{figure*}[htbp]
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure1.png}}
        \centerline{(1a) Q=5}
    \end{minipage}
    \hfill
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure2.png}}
        \centerline{(1b) Q=15}
    \end{minipage}
    \hfill
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure3.png}}
        \centerline{(1c) Q=15}
    \end{minipage}
    \hfill
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure4.png}}
        \centerline{(1d) Q=15}
    \end{minipage}

    \vfill
    \vspace{0.4cm}

    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure1.png}}
        \centerline{(2a) Q=85}
    \end{minipage}
    \hfill
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure2.png}}
        \centerline{(2b) Q=85}
    \end{minipage}
    \hfill
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure3.png}}
        \centerline{(2c) Q=75}
    \end{minipage}
    \hfill
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure4.png}}
        \centerline{(2d) Q=75}
    \end{minipage}
    \vspace{0.2cm}
    \caption{Visualization of the importance map for the RL agent to choose a compression quality level}
    \label{fig: attention}
\end{figure*}

In our investigations, we find that in different environments $ \{\mathcal{X}, M\} $, the RL agent picks up compression quality level based on the visual textures of different regions in the image. As shown in Figure \ref{fig: attention}, picture 1a -- 1d are some pictures that the agent chooses to compress highly, the agent selects lower compression quality levels based on the complex texture of the images. On the contrary, for pictures 2a -- 2d, the agent chooses higher compression quality levels to preserve more details, and the agent's interest falls on some smooth regions. Especially for 1a and 2a, in picture 1a, the agent chooses a lower quality compression level based on the rough central region though there are smooth regions around it, and in picture 2a, the agent chooses a relatively higher compression quality level based on the surrounding smooth region rather than the central region. %% \\

### 2020-03-11 paper/sections/evaluation.tex
add the paper framework

\section{Evaluation}
\label{sec: evaluation}

In this section, we present AdaCompress's behavior and effectiveness by some real-world experiments. %% \\

\subsection{Experiment Setup}

We carry out real-world experiments to verify our solution's performance. We use a desktop PC with an NVIDIA 1080ti graphic card as the edge infrastructure. For the cloud deep learning services, we choose Baidu Vision, Face++ object detection services, and Amazon Rekognition. In the experiments, we use two datasets mentioned before in Sec.\ref{subsec:insight}, ImageNet dataset indicating daytime scenery and the FLIR Thermal Dataset indicating nighttime scenery. Some important hyperparameters in our experiments are given in Table \ref{tab: parameters}.

\begin{table}[H]
    \centering
    %     \begin{tabular}{llllll}
    \begin{tabular}{cccccc}
        \toprule
        notation          & value & & & notation     & value  \\ \midrule
        $c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
        $\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
        $\gamma$      & 0.95  & & & $\omega$ & -3   \\
        $ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
        $r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ \bottomrule
    \end{tabular}
    \caption{Experiment parameter settings}
    \label{tab: parameters}
    %     \vspace{-0.3cm}
\end{table}

\subsection{Dataset}

We use two datasets, the ImageNet dataset and the FLIR Thermal Dataset. The Imagenet dataset is a Large-Scale Hierarchical Image, in which each node of the hierarchy is depicted by hundreds and thousands of images. Its images are mostly taken in the daytime, and therefore we use it as a daytime scenery. Usually, a surveillance camera captures colored images in the daytime and gray-scaled thermal images in the nighttime. Therefore we choose a thermal image dataset to act as a nighttime image dataset. The FLIR Thermal Dataset is such a dataset having more than 14000 images collected by thermal sensors.

We use the ImageNet dataset in size reduction and accuracy performance experiment, DeepN-JPEG comparative experiment, and end-to-end latency simulation. Moreover, we use ImageNet and the FLIR Thermal Dataset alternately to simulate the scenery change in the inference-estimation-querying-retraining mechanism experiment, and analyze the RL agent's best compression strategy selection in different input image sceneries.

\subsection{Metrics}
\label{subsec:metrics}

The default compression quality level for JPEG is usually 75~\cite{pillow_benchmark,imgmin}, therefore we regard this as a typical value $ c_{\rm ref} = 75 $ of the conventional benchmark. %% \\

In our experiments, we measure the compressed and original image's file size to obtain the compression rate $ \Delta s $. Since we don't have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric, the formula of $ \mathcal{A} $ is presented in Sec. ~\ref{subsec: formulation}.

\subsection{Upload Size Overhead}

\begin{figure}[htbp]
    \includegraphics[width=\linewidth]{figures/train_steps_new.pdf}
    \caption{Size overhead in training and inference phase}
    \label{fig: train_steps}
    % \vspace{-0.3cm}
\end{figure}

Figure \ref{fig: train_steps} presents the upload traffic load of the training and inference phase, to be more intuitionistic, we plot the size overhead $ \frac{s}{s_{\rm ref}} $ as the $ y $-axis where $ s $ is the real upload size of AdaCompress, $ s_{\rm ref} $ is the benchmark upload size. Therefore $ y \geq 1 $ means that our solution uploads more data then benchmark, and $ y < 1 $ means the compression rate of AdaCompress. From Figure \ref{fig: train_steps} we can see that as the training procedure runs, the upload size decreases because the RL agent learns to choose better compression quality levels to upload fewer data. In the training phase, to train the agent while remaining a convincing recognition result, we have to upload the original image to the cloud to get the real result, along with the compressed image to obtain reward feedback, therefore the upload traffic load is even higher than the conventional solution. But once the training phase has finished, the upload traffic load is much lower than the benchmark. As shown in Figure \ref{fig: compress_performance}, in the inference phase, AdaCompress's upload size is only 1/2 of the benchmark's. %% \\

\subsection{Size Reduction and Accuracy Performance}

\begin{figure}[htbp]
    \includegraphics[width=\linewidth]{figures/compress-performance.pdf}
    \caption{Average size and relative accuracy on different cloud services}
    \label{fig: compress_performance}
    % \vspace{-0.3cm}
\end{figure}

Figure \ref{fig: compress_performance} presents the compression performance in the inference phase for each cloud service. We test AdaCompress on Face++, Baidu Vision and Amazon Rekognition, comparing to the conventional compression level, for all tested cloud services, our solution can reduce the upload size by more than 1/2, meanwhile, the relative accuracy, indicated by brown bars, only decreases about 7\% on average, proving the efficiency of our design. %% \\

\subsection{DeepN-JPEG Comparative Experiment}

\begin{figure}[htbp]
    \includegraphics[width=\linewidth]{figures/compare_DeepN.eps}
    \caption{Comparative compression performance between DeepN-JPEG and AdaCompress}
    \label{fig: compare_DeepN}
    % \vspace{-0.3cm}
\end{figure}

\begin{figure*}[htbp]
    \begin{minipage}{0.3\linewidth}
        \centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_q75.jpeg}}
        \centerline{(1a) Origin Image (Q=75)}
        \centerline{Baidu prediction \ = \ ["parrot"]}
    \end{minipage}
    \hfill
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_q15.jpeg}}
        \centerline{(1b) AdaCompress (choose Q=15)}
        \centerline{Baidu prediction \ = \ ["parrot"]}
    \end{minipage}
    \hfill
    \begin{minipage}{0.3\linewidth}
        \centerline{\includegraphics[width=4.0cm,trim=0 80 0 100,clip ]{figures/parrot_deepn.jpeg}}
        \centerline{(1c) DeepN-JPEG}
        \centerline{Baidu prediction \ = \ ["parrot"]}
    \end{minipage}

    \vfill
    \vspace{0.4cm}

    \begin{minipage}{0.3\linewidth}
        \centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_q75.jpeg}}
        \centerline{(2a) Origin Image (Q=75)}
        \centerline{Baidu prediction \ = \ ["cake"]}
    \end{minipage}
    \hfill
    \begin{minipage}{0.2\linewidth}
        \centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_q65.jpeg}}
        \centerline{(2b) AdaCompress (choose Q=65)}
        \centerline{Baidu prediction \ = \ ["cake"]}
    \end{minipage}
    \hfill
    \begin{minipage}{0.3\linewidth}
        \centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_deepn.jpeg}}
        \centerline{(2c) DeepN-JPEG}
        \centerline{Baidu prediction \ = \ ["fossil"]}
    \end{minipage}
    \vspace{0.2cm}
    \caption{Comparative compressed images of DeepN-JPEG and AdaCompress}
    \label{fig: compare_image}
\end{figure*}

Figure \ref{fig: compare_DeepN} presents a comparison performance between DeepN-JPEG and AdaCompress for each cloud service. As we can see, both DeepN-JPEG and AdaCompress cut down the upload size overhead more than 1/2. However, for all tested cloud services, AdaCompress's accuracy is higher than DeepN-JPEG's slightly. Compared with DeepN-JPEG's average accuracy is about 85\% on three cloud services, while AdaCompress achieves a better average accuracy of 93\%. In a word, comparing to the DeepN-JPEG framework, AdaCompress presents a similar upload traffic load reduction performance but achieving higher inference accuracy for computer vision cloud services.

AdaCompress compresses images in a more adaptive manner rather than DeepN-JPEG. (i.e., the explanation of why AdaCompress achieves a better accuracy). As shown in Figure \ref{fig: compare_image}, for picture 1a, compared to DeepN-JPEG, AdaCompress compresses the image at the compression quality level of 15, a more aggressive compression quality level to reduce upload size overhead. On the contrary, for picture 2a of Figure \ref{fig: compare_image}, DeepN-JPEG compresses the image with the same quantization table, but AdaComperss chooses a higher compression quality level to preserve more details so that the backend deep learning model can still recognize the picture. Being different from the DeepN-JPEG framework compresses all images with the same quantization table, our RL agent chooses a lower compression quality level for picture 1a and a relatively higher compression quality level for picture 2a based on the feature of the input image.

%Comparing to DeepN-JPEG, AdaCompress compresses images more adaptively for different images and cloud computer vision services to achieve higher accuracy, while maintaining a similar average upload size overhead.

Comparing to DeepN-JPEG, AdaCompress has three advantages and one disadvantage as following: %% \\    
    \begin{itemize}
        \item AdaCompress and DeepN-JPEG both decrease the upload size overhead more than 1/2, but AdaCompress maintains higher inference accuracy.
        \item DeepN-JPEG requires the original dataset information to redesign the quantization table, while AdaCompress chooses compression quality level adaptively without any pre-knowledge of the original dataset. 
        \item When the scenery changes, DeepN-JPEG still compresses images with the same quantization table, while AdaCompress's inference-estimation-querying-retraining mechanism captures the scenery change and invokes either model querying method or retraining kernel to generate a more suitable compression selection strategy for the current scenery.
        \item DeepN-JPEG redesigns the quantization table locally, while AdaCompress needs to upload origin images and compressed images to the cloud in the training phase, leading some upload size overhead at the beginning. 
    \end{itemize}

\subsection{Adaptively Cope With the Scenery Change}

To evaluate the efficiency of the inference-estimation-querying-retraining mechanism, we feed AdaCompress with a combined dataset whose first 2000 images from FLIR Thermal images, the later 3000 images randomly sampled from ImageNet, and the last 2000 images from FLIR Thermal images. We adapt AdaCompress's current RL agent to FLIR Thermal nighttime scenery by training it on the FLIR Dataset, and we run AdaCompress on the combined dataset, observing AdaCompress's behavior upon the scenery changes at step 2000 and 5000. %% \\

We illustrate AdaCompress's behavior in Figure \ref{fig: running-retrain}, the $ x $-axis indicates steps, the vertical red line means the dataset change (i.e. scenery change). We plot AdaCompress's overall accuracy as the green line and the estimation probability $ p_{\rm est} $ as the gray line. At the bottom of Figure \ref{fig: running-retrain}, we also plot the scaled upload size of AdaCompress and benchmark solution to illustrate the upload size overhead in the inference phase.
%with a $ \Delta $ mark on $ x $-axis

%\begin{figure}[htbp]
%    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
%    \caption{AdaCompress's reaction upon scenery change}
%%    \vspace{-0.2cm}
%    \label{fig: running-retrain}
%\end{figure}

\begin{figure}[htbp]
    \includegraphics[width=\linewidth]{figures/running-retrain.eps}
    \caption{AdaCompress's reaction upon scenery change}
    %    \vspace{-0.2cm}
    \label{fig: running-retrain}
\end{figure}

From Figure \ref{fig: running-retrain} we can see that AdaCompress can adaptively update the estimation probability $ p_{\rm est} $, usually, when the overall accuracy decreases, AdaCompress would increase the estimation probability, trying to capture the scenery change. When the overall accuracy is stable and high enough, the estimation probability $ p_{\rm est} $ decreases to reduce transmission. %% \\

Upon the first data scenery changes (i.e., night to day) shown as the first vertical red line in Figure \ref{fig: running-retrain}, comparing to the earlier steps, the accuracy decreases dramatically and therefore $ p_{\rm est} $ raises to determine whether the scenery changes. The accuracy keeps dropping in the following estimations, indicating that the current RL agent is no more suitable for the current input scenery. At the moment, AdaCompress should switch into the model querying state and reload a new RL agent model from the model caching library. However, there is no model except the current RL agent in the model caching library at that time. Therefore, AdaCompress starts to retrain at once, to adapt the RL agent into the current scenery. The retraining steps are shown as the light-blue region in Figure~\ref{fig: running-retrain}. In the retraining phase, AdaCompress always uses the reference image's prediction label $ \vec{y}_{\rm ref} $ as the output result, therefore the accuracy $ \mathcal{A} $ and $ p_{\rm est} $ are locked to 1. After finishing retraining the agent in the daytime scenery, the trained agent is cached in the model cachling library, and in the following iterations, sometimes the accuracy decreases accidentally, and the estimation probability $ p_{\rm est} $ also raises to get more samples. The accuracy is not lower than the accuracy threshold $ \mathcal{A}_0 $ , therefore the retraining phase would not be triggered again until the second data scenery changes. %% \\

Upon the second data scenery changes (i.e., day to night) shown as the second vertical red line in Figure \ref{fig: running-retrain}, like the first scenery change, the accuracy decreases and $ p_{\rm est} $ raises, indicating that the current RL agent is no more suitable again. AdaCompress switches into the model querying state at once and reloades a new RL agent model (i.e., the initial model trained on the FLIR Thermal images) from the model caching library. When using the new agent in this scenery, the accuracy stops decreasing and maintains above the accuracy threshold, indicating the current RL agent is suitable for the current scenery.  %% \\

From Figure \ref{fig: running-retrain} we can also observe the uploading file size overhead in different phases, in retraining phase, AdaCompress uploads more data than the conventional benchmark, but in inference phase, AdaCompress's upload size is only half of the benchmark's. Especially when the second data scenery changes, AdaCompress achieves a lower upload traffic load by loading a suitable RL agent model rather than retraining from scratch. %% \\

\subsection{End-to-End Latency Simulation}

Comparing to the conventional solution that uploads the image directly, in our solution, the image is passed to the RL agent first to estimate the compression level. Running this RL agent brings extra latency to the whole system. In this subsection, we evaluate this latency overhead. %% \\

We test the RL agent's inference time and compressed file size for batches of images, and simulate the latency of uploading such compressed images. We test the average inference latency on 1000 ImageNet images and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb. 2019, to verify the end-to-end latency performance. The latency comparison is listed in Table \ref{tab: latency-overhead}. %% \\

\begin{table}[htbp]
    % \begin{table}[H]
    \centering
    %     \begin{tabular}{lll}
    \begin{tabular}{ccc}
        \toprule
        & Benchmark & AdaCompress  \\ \midrule
        Average upload size          & 42.68 KB  &  18.46 KB            \\
        Inference latency    & 0 s       & 2.09 ms          \\
        Transmission latency & 12.35 ms       & 5.34 ms          \\
        Overall latency      & 12.35 ms       & 7.43 ms          \\ \bottomrule
    \end{tabular}
    \caption{Latency between image upload and inference result feedback}
    \label{tab: latency-overhead}
    % \vspace{-0.5cm}
\end{table}

Our solution brings in inference latency to the end-to-end latency, but the transmission latency is much lower by shrinking the upload file size. In today's network architecture where the edge infrastructure's computational power is increasing significantly ~\cite{satyanarayanan2017emergence,hu2015mobile}, we can use the computing power of the edge infrastructure in exchange for the reduction of upload traffic load and transmission latency. %% \\

### 2020-03-11 paper/sections/introduction.tex
add the paper framework

\section{Introduction}
\label{sec: introduction}

\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning based computer vision applications. Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires 20 GFLOPs of GPU resource), in today's computer vision applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load. For example, a picture taken by a cellphone at the resolution of $3968 \times 2976$ when saved as JPEG format at the default compression quality level, has a size up to 3MB. %% \\

To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it. Though JPEG has been used as the {\em de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory, because JPEG was originally designed for the Human-Visual System. Liu et al.~\cite{DeepN-JPEG} showed that by redesigning the \emph{quantization table} in the default JPEG configuration, by retraining it on the original dataset, one can compress an image to a smaller version while maintaining the inference accuracy for a fixed deep computer vision algorithm. We then raise an intuitive question: to make it practically useful, can we improve the JPEG configuration adaptively for different cloud computer vision services, without any pre-knowledge of the original model and dataset? %% \\

Our answer to this question is a new learning-based compression methodology for today's cloud computer vision services. We tackle the following challenges in our design. %% \\

\begin{itemize}
\item \textbf{Lack of information about the cloud computer vision models.} Different from the studies ~\cite{DeepN-JPEG,torfason2018towards,gueguen2018faster}, in which the computer vision models are available so that one can adjust the JPEG configuration according to the model structure or retrain the parameters in it, e.g., one can greedily search a gradient descent to reach an optimal compression quality level in JPEG. In our study, however, the details of the online cloud computer vision model are inaccessible. %% \\

\item \textbf{Different cloud computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different cloud computer vision services, i.e., it can \emph{generate} JPEG configuration for different models. However, today's cloud computer vision algorithms, based one deep and convolutional computations, are quite hard to understand. The same compression quality level could lead to a totally different accuracy performance. Some examples are shown in Figure \ref{fig: compress_accuracy}, picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning models give different inference results, only because they are compressed at different quality levels. And such a relationship is not apparent, e.g., picture 3b is highly compressed and looks destroyed comparing to picture 3a, but the deep learning model can still recognize it. This phenomenon is also presented in~\cite{delac2005effects} and commonly seen in adversarial neural network researches~\cite{yuan2019adversarial, evtimov2018robust}. %% \\

\item \textbf{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which image should be compressed to which quality level, as in conventional supervised deep learning tasks. In practice, such an image compression module is usually utilized in an online manner, and the solution has to learn from the images it uploads automatically. 
\end{itemize}

\begin{figure*}[htbp]
%	\begin{tabular}{cc}
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q75.jpeg}}
		\centerline{(1a) Q=75}
%		\centerline{Face++ prediction=["donut"]}
		\centerline{Face++ prediction \ = \ ["donut"]}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q55.jpeg}}
		\centerline{(1b) Q=55}
%		\centerline{Face++ prediction=[]}
		\centerline{Face++ prediction \ = \ ["biscuit"]}
		\vspace{0.4cm}
	\end{minipage}
	\vfill	
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q75.jpeg}}
		\centerline{(2a) Q=75}
% 		\centerline{\quad Baidu prediction=["chameleon"]}
		\centerline{Baidu prediction \ = \ ["chameleon"]}
		\vspace{0.4cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q55.jpeg}}
		\centerline{(2b) Q=55}
% 		\centerline{\qquad Baidu prediction=["electric fan"]}
 		\centerline{Baidu prediction \ = \ ["electric fan"]}
 		\vspace{0.4cm}
	\end{minipage}
	\vfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_highq.jpeg}}
		\centerline{(3a) Q=75}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ ["leopard"]}
		\vspace{0.3cm}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_lowq.jpeg}}
		\centerline{(3b) Q=5}
%		\centerline{Baidu prediction=["leopard"]}
		\centerline{Baidu prediction \ = \ ["leopard"]}
		\vspace{0.3cm}
	\end{minipage}
%	\end{tabular}
	\caption{The prediction of a deep learning model is not completely related to the input image's quality, making it difficult to use a fixed compression quality for all images. For image 1a, 1b and 2a, 2b, minor changes cause different predictions though they are visually similar; for image 3a and 3b, the cloud model still output correct label from a severely compressed image though they look very different}
	\label{fig: compress_accuracy}
%	\vspace{-0.1cm}
\end{figure*}

To address the above challenges, we present a reinforcement learning (RL) based solution, AdaCompress, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner. We open-sourced\footnote{\url{https://github.com/hosea1008/AdaCompress}} our JPEG configuration module that works with today's cloud computing vision APIs upon acceptance of this paper \cite{2019adacompress}. In particular, our contributions are summarized as follows: %% \\

\begin{itemize} \item First, we design an interactive training environment that can be applied to different computer vision cloud services at different times, then we propose a Deep Q-learning Network based agent to evaluate and predict the performance of a compression quality level on an input image. In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU \cite{google-tpu}, Huawei Atlas 500 edge station \cite{huawei-atlas500}).

	\item Second, we build up a reinforcement learning framework to train the agent in the above environment. The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward comprehensively considering accuracy and data size into it. To make the solution adaptive to the changing input images, we propose an explore-exploit mechanism to adapt the agent to different ``scenery'' online. After deploying the agent, an inference-estimate-retrain mechanism is designed to restart the training procedure once the scenery changes and the existing running agent cannot guarantee stable accuracy performance.

	\item Finally, we provide analysis and insights on our design. We analyze the Q network's behavior by introducing Grad-Cam ~\cite{grad-cam}, explain why the Q network chooses a specific compression quality level and provide some general patterns. Generally speaking, images that contain large smooth areas are more sensitive to compression, while the images with complex textures are more robust to compression when shown to deep learning models. We evaluate our system on some most popular cloud deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to 1/2 while maintaining comparable overall accuracy. \end{itemize}

This paper is an extension of the earlier conference version \cite{2019adacompress}, our work contains significant new components as follows:

\begin{itemize}
	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work \cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase. Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load. In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to \cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance. Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG. Moreover, we provide illustrative image examples to present that AdaCompress compresses images more adaptively to achieve higher accuracy.
	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
\end{itemize}

The rest of this paper is organized as follows. We discuss related works in Sec. \ref{sec: related_works}. In Sec. \ref{sec: design} we present our framework and detailed design. We present our solution's performance in Sec. \ref{sec: evaluation} and conclude the paper in Sec. \ref{sec: conclusion}.

%The rest of this paper is organized as follows. We present our framework and detailed design in Sec. \ref{sec: design}. In Sec. \ref{sec: evaluation} we present our solution's performance. We discuss related works in Sec. \ref{sec: related_works} and conclude the paper in Sec. \ref{sec: conclusion}.

### 2020-03-11 paper/sections/relatedwork.tex
add the paper framework

\section{Related Works}
\label{sec: related_works}

As cloud-based computer vision services have become the norm for today's applications ~\cite{huynh2017deepmon, agrawal2015cloudcv}, many studies have been devoted to improving the cloud-based model execution, including model compression and data compression.

\subsection{Model Compression}

Though the accurate term is still for the community to debate, we use ``model compression'' to represent the studies on {\em compressing} and {\em moving} the deep learning models close to users. Many studies tried to compress the deep learning models and deploy them \emph{locally} ~\cite{prun_quanti, pruning_han, quantize, quantize_3bit, quantization, structured_pruning}, i.e., running an alternative ``smaller version'' of a computer vision model at the user end, to avoid the image upload so that to improve the inference efficiency. Other studies proposed to run a part of a deep learning model locally ~\cite{ILP_Decoupling, jalad, Edge_LBP, Neurosurgeon}, by decoupling the deep learning model into different parts, e.g., based on the layers in the deep learning model, so that a part of the inference is done locally to save some execution time. However, these solutions usually need to \emph{re-train} the model, using the original dataset of the model, which is not practical for today's cloud computer vision services that are merely a black box to end-users, e.g., in the form of a RESTful API.

\subsection{Data Compression}

Data compression solutions study how to compress the original data (e.g., a video or image) to be inferred by the cloud deep learning model, so that less traffic is used to upload the data to improve inference speed. Conventional data compression solutions (e.g., JPEG \cite{jpeg}, WebP \cite{calore2010meet}, JPEG2000 \cite{rabbani2002jpeg2000} etc.) and some recent neural network based compression solutions ~\cite{toderici2017full,theis2017lossy,toderici2015variable, rippel2017real} are initially designed for the Human-Visual System. In recent years, researchers found that the human visually optimized data compression solutions are not usually applicable to deep learning vision models. Delac et al.~\cite{delac2005effects} observed that, in some cases, higher compression level does not always deteriorate the model inference accuracy, even improves it slightly. Dodge et al.~\cite{dodge2016understanding} further discovered that besides the JPEG compression, four types of quality distortions (blur, noise, contrast, and the JPEG2000 compression) can also affect the performance in deep learning inference. Liu et al.~\cite{DeepN-JPEG} proposed that the conventional JPEG image compression framework is designed for the Human-Visual System which is not suitable for the deep neural network, leading to cloud computer vision services' accuracy degradation at lower images' compression quality level. %% \\

Based on these insights, Robert et al. \cite{torfason2018towards} tried to train the deep neural network from the compressed representations of an auto-encoder. Chao et al. \cite{chao2011preserving} proposed using variable quantization which is supported by the JPEG standard extension syntax \cite{dis199110918} to compress the macroblocks in images. Furthermore, they \cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance with reduced image size. Liu et al. \cite{DeepN-JPEG} proposed DeepN-JPEG that redesigns the quantization table by linking statistical information of refined features and defining quantization values so that the compressed image size is reduced for deep learning models. Chamain et al. \cite{2019quannet} proposed a joint optimization of image classification network coupled with the image quantization, achieving image size reduction of JPGE2000 \cite{rabbani2002jpeg2000} encoded images. Recently, Lionel et al. \cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform (DCT) coefficients in the middle of the JPEG codec. Baluja et al.~\cite{baluja2019task} proposed task-specific compression that compresses images based on the end-use of images. %% \\

However, such proposals all need one to understand the characteristics of the cloud-end deep learning model and have access to the original training dataset, to generate the appropriate color space and/or compression schemes. To the best of our knowledge, we are the first to propose an adaptive compression configuration solution named AdaCompress \cite{2019adacompress} that learns the deep learning model by itself. We design an agent that adaptively chooses the compression level according to the input image's features and backend deep learning models.

In this extension paper, we improve previous mechanism to cut down the uploading file size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly. Especially on the DeepN-JPEG comparative experiment, since Liu et al. \cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on the ImageNet dataset by using four state-of-the-art DNN models (AlexNet \cite{AlexNet-krizhevsky2012imagenet}, VGG \cite{VGG-simonyan2014very}, GoogLeNet \cite{GoogleNet-szegedy2015going} and ResNet \cite{ResNet-he2016deep}) on local terminal devices, which are different from cloud computer vision services. For comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using the ImageNet dataset and the metrics in Sec.\ref{subsec:metrics} on three cloud deep learning services (Amazon Rekognition, Face++ and Baidu Vision), the same experiment configuration as the AdaCompress's.

%Liu et al. \cite{DeepN-JPEG} developed the DeepN-JPEG framework, a deep %neural network favorable JPEG-based image compression framework.

### 2020-03-12 paper/sections/abstract.tex
abstract

@@
 \begin{abstract}
-With the growth of computer vision based applications and services, an explosive amount of images have been uploaded to cloud servers that host such computer vision algorithms, usually in the form of deep learning models.
-JPEG has been used as the {\em de facto} compression and encapsulation method before one uploads the images, due to its wide adaptation.
-However, standard JPEG configuration does not always perform well for compressing images that are to be processed by a deep learning model, e.g., the standard quality level of JPEG leads to 50\% of size overhead (compared with the best quality level selection) on ImageNet under the same inference accuracy in popular computer vision models including InceptionNet, ResNet, etc.
-Knowing this, designing a better JPEG configuration for online computer vision services is still extremely challenging: 1) Cloud-based computer vision models are usually a black box to end-users; thus it is difficult to design JPEG configuration without knowing their model structures.
-2) JPEG configuration has to change when different users use it since different input image's features and backend deep learning models.
-In this paper, we propose a reinforcement learning based JPEG configuration framework.
-In particular, we design an agent that adaptively chooses the compression quality level according to the input image's features and backend deep learning models.
-Then we train the agent in a reinforcement learning way to adapt it for different deep learning cloud services that act as the {\em interactive training environment} and feeding a reward with comprehensive consideration of accuracy and data size.
-In our real-world evaluation on Amazon Rekognition, Face++ and Baidu Vision, our approach can reduce the size of images by 1/2 -- 1/3 while the overall classification accuracy only decreases slightly.
-To make the solution adaptive to the changing input images, we propose an explore-exploit mechanism to adapt the agent to different ``scenery'' online.
-In our experiment, once capturing the scenery change, AdaCompress either reloads or retrains the RL agent based on the performance of the cached model to make a proper compression strategy and maintain the inference accuracy.
+
+With the growth of computer vision-based applications, an explosive amount of images have been uploaded to cloud servers that host such online computer vision algorithms, usually in the form of deep learning models.
+JPEG has been used as the {\em de facto} compression and encapsulation method for images.
+However, standard JPEG configuration does not always perform well for compressing images that are to be processed by a deep learning model, e.g., the standard quality level of JPEG leads to $50\%$ of size overhead (compared with the best quality level selection) on ImageNet under the same inference accuracy in popular computer vision models (e.g., InceptionNet and ResNet).
+Knowing this, designing a better JPEG configuration for online computer vision services is still extremely challenging: 1) Cloud-based computer vision models are usually a black box to end-users; thus, it is challenging to design JPEG configuration without knowing their model structures.
+2) The ``optimal'' JPEG configuration is not fixed; instead, it is determined by confounding factors, including the characteristics of the input images and the model, the expected accuracy and image size, etc.
+In this paper, we propose a reinforcement learning (RL)-based adaptive JPEG configuration framework, AdaCompress.
+In particular, we design an edge (i.e., user-side) reinforcement learning agent that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.
+Furthermore, we design an explore-exploit mechanism to let the framework fast switch an agent when it detects a performance degradation, mainly due to the input change (e.g., images captured across daytime and night).
+Our evaluation experiments using real-world online computer vision APIs from Amazon Rekognition, Face++, and Baidu Vision, show that our approach outperforms existing baselines by reducing the size of images by 1/2 -- 1/3 while the overall classification accuracy only decreases slightly; Meanwhile, AdaCompress adaptively retrains or reloads the RL agent promptly to maintain the performance.
+
 \end{abstract}

### 2020-03-12 paper/sections/introduction.tex
abstract

@@
 \IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning based computer vision applications.
-Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires 20 GFLOPs of GPU resource), in today's computer vision applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.
-For example, a picture taken by a cellphone at the resolution of $3968 \times 2976$ when saved as JPEG format at the default compression quality level, has a size up to 3MB.
-%% \\
+Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19 \cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's computer vision applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.
 
 To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it.
-Though JPEG has been used as the {\em de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory, because JPEG was originally designed for the Human-Visual System.
-Liu et al.~\cite{DeepN-JPEG} showed that by redesigning the \emph{quantization table} in the default JPEG configuration, by retraining it on the original dataset, one can compress an image to a smaller version while maintaining the inference accuracy for a fixed deep computer vision algorithm.
-We then raise an intuitive question: to make it practically useful, can we improve the JPEG configuration adaptively for different cloud computer vision services, without any pre-knowledge of the original model and dataset?
-%% \\
+Though JPEG has been used as the {\em de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory.
+Liu et al.~\cite{DeepN-JPEG} showed that by redesigning the \emph{quantization table} in the default JPEG configuration, one can compress an image to a smaller version while maintaining the same inference accuracy for a deep computer vision model.
+However, such quantization solutions usually assume the inference model is fixed.
 
-Our answer to this question is a new learning-based compression methodology for today's cloud computer vision services. We tackle the following challenges in our design. %% \\
+We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different cloud computer vision services, without any prior knowledge of the original model and input images?
+Such adaptive image compression for online computer vision services are facing the following design challenges.
 
 \begin{itemize}
-\item \textbf{Lack of information about the cloud computer vision models.} Different from the studies ~\cite{DeepN-JPEG,torfason2018towards,gueguen2018faster}, in which the computer vision models are available so that one can adjust the JPEG configuration according to the model structure or retrain the parameters in it, e.g., one can greedily search a gradient descent to reach an optimal compression quality level in JPEG.
-In our study, however, the details of the online cloud computer vision model are inaccessible.
-%% \\
+
+\item \textbf{Lack of information about the cloud computer vision models.} Previous studies \cite{DeepN-JPEG,torfason2018towards,gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging a original computer vision model into it.
+However, the structure details of online cloud computer vision models are usually propriotary and not open to the users.
 
 \item \textbf{Different cloud computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different cloud computer vision services, i.e., it can \emph{generate} JPEG configuration for different models.
-However, today's cloud computer vision algorithms, based one deep and convolutional computations, are quite hard to understand.
+However, today's cloud computer vision algorithms, based on deep and convolutional computations, are quite hard to understand.
 The same compression quality level could lead to a totally different accuracy performance.
@@
 This phenomenon is also presented in~\cite{delac2005effects} and commonly seen in adversarial neural network researches~\cite{yuan2019adversarial, evtimov2018robust}.
-%% \\
 

### 2020-03-12 paper/sections/introduction.tex
intro minor

@@
 We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different cloud computer vision services, without any prior knowledge of the original model and input images?
-Such adaptive image compression for online computer vision services are facing the following design challenges.
+In this paper, we propose a reinforcement learning based framework to select JPEG configurations adaptively.
+In our solution, we tackle the following design challenges.
 
@@
 
-\item \textbf{Lack of information about the cloud computer vision models.} Previous studies \cite{DeepN-JPEG,torfason2018towards,gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging a original computer vision model into it.
-However, the structure details of online cloud computer vision models are usually propriotary and not open to the users.
+\item \emph{Lack of information about the cloud computer vision models.} Previous studies \cite{DeepN-JPEG,torfason2018towards,gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging the original computer vision model into it.
+However, the structure details of online cloud computer vision models are usually proprietary and not open to the users.
 
-\item \textbf{Different cloud computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different cloud computer vision services, i.e., it can \emph{generate} JPEG configuration for different models.
+\item \emph{Different cloud computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different cloud computer vision services, i.e., it can \emph{generate} JPEG configuration for different models.
 However, today's cloud computer vision algorithms, based on deep and convolutional computations, are quite hard to understand.
 The same compression quality level could lead to a totally different accuracy performance.
-Some examples are shown in Figure \ref{fig: compress_accuracy}, picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning models give different inference results, only because they are compressed at different quality levels.
+Some examples are shown in Figure \ref{fig: compress_accuracy}: picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning models give different inference results, only because they are compressed at different quality levels.
 And such a relationship is not apparent, e.g., picture 3b is highly compressed and looks destroyed comparing to picture 3a, but the deep learning model can still recognize it.
@@
 
-\item \textbf{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which image should be compressed to which quality level, as in conventional supervised deep learning tasks.
+\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which image should be compressed to which quality level, as in conventional supervised deep learning tasks.
 In practice, such an image compression module is usually utilized in an online manner, and the solution has to learn from the images it uploads automatically.
@@
 
-To address the above challenges, we present a reinforcement learning (RL) based solution, AdaCompress, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner.
-We open-sourced\footnote{\url{https://github.com/hosea1008/AdaCompress}} our JPEG configuration module that works with today's cloud computing vision APIs upon acceptance of this paper \cite{2019adacompress}.
-In particular, our contributions are summarized as follows: %% \\
+To address the above challenges, we present a reinforcement learning based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner.
+This paper is an extension of our earlier conference paper \cite{2019adacompress}, with the following contributions:
 
-\begin{itemize} \item First, we design an interactive training environment that can be applied to different computer vision cloud services at different times, then we propose a Deep Q-learning Network based agent to evaluate and predict the performance of a compression quality level on an input image.
+$\rhd$ We design an interactive training environment that can be applied to different computer vision cloud services.
+We propose a Deep Q-learning Network based agent to evaluate and predict the performance of a compression quality level on an input image.
 In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU \cite{google-tpu}, Huawei Atlas 500 edge station \cite{huawei-atlas500}).
 
-	\item Second, we build up a reinforcement learning framework to train the agent in the above environment.
-The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward comprehensively considering accuracy and data size into it.
-To make the solution adaptive to the changing input images, we propose an explore-exploit mechanism to adapt the agent to different ``scenery'' online.
-After deploying the agent, an inference-estimate-retrain mechanism is designed to restart the training procedure once the scenery changes and the existing running agent cannot guarantee stable accuracy performance.
+$\rhd$ We build a reinforcement learning framework to train the agent in the above environment.
+The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size.
+Based on \cite{2019adacompress}, we further propose an \emph{explore-exploit} mechanism let the agent switch between ``sceneries''.
+In particular, after deploying the agent, an \emph{inference-estimate-retrain} solution is designed to restart the training once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.
 
-	\item Finally, we provide analysis and insights on our design.
-We analyze the Q network's behavior by introducing Grad-Cam ~\cite{grad-cam}, explain why the Q network chooses a specific compression quality level and provide some general patterns.
-Generally speaking, images that contain large smooth areas are more sensitive to compression, while the images with complex textures are more robust to compression when shown to deep learning models.
-We evaluate our system on some most popular cloud deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to 1/2 while maintaining comparable overall accuracy.
-\end{itemize}
+$\rhd$ In this journal extension, we provide more analysis and insights on our design.
+By analyzing the Q network's behaviors using Grad-Cam \cite{grad-cam}, we provide the reasons that the Q network chooses a specific compression quality level.
+We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.
 
-This paper is an extension of the earlier conference version \cite{2019adacompress}, our work contains significant new components as follows:
+$\rhd$ We evaluate our system on representative cloud deep learning services, including Amazon Rekognition \cite{amazon_rekognition}, Face++ \cite{face++_service} and Baidu Vision \cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy.
+Compared to baseline DeepN-JPEG \cite{DeepN-JPEG}, the inference accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.
 
-\begin{itemize}
-	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work \cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase.
+% \begin{itemize}
+% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work \cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase.
 Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load.
 In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
-	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to \cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance.
+% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to \cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance.
 Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG.
 Moreover, we provide illustrative image examples to present that AdaCompress compresses images more adaptively to achieve higher accuracy.
-	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
-\end{itemize}
+% 	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
+% \end{itemize}
 
 The rest of this paper is organized as follows.
-We discuss related works in Sec.
-\ref{sec: related_works}.
-In Sec.
-\ref{sec: design} we present our framework and detailed design.
-We present our solution's performance in Sec.
-\ref{sec: evaluation} and conclude the paper in Sec.
-\ref{sec: conclusion}.
+We discuss related works in Sec.~\ref{sec: related_works}.
+In Sec.~\ref{sec: design} we present our framework and detailed design.
+We present our solution's performance in Sec.~\ref{sec: evaluation} and conclude the paper in Sec.~\ref{sec: conclusion}.
 
 %The rest of this paper is organized as follows.
-We present our framework and detailed design in Sec.
-\ref{sec: design}.
-In Sec.
-\ref{sec: evaluation} we present our solution's performance.
-We discuss related works in Sec.
-\ref{sec: related_works} and conclude the paper in Sec.
-\ref{sec: conclusion}.
+We present our framework and detailed design in Sec.~\ref{sec: design}.
+In Sec.~\ref{sec: evaluation} we present our solution's performance.
+We discuss related works in Sec.~\ref{sec: related_works} and conclude the paper in Sec.~\ref{sec: conclusion}.

### 2020-03-14 paper/sections/abstract.tex
improve consistency

@@
 With the growth of computer vision-based applications, an explosive amount of images have been uploaded to cloud servers that host such online computer vision algorithms, usually in the form of deep learning models.
-JPEG has been used as the {\em de facto} compression and encapsulation method for images.
+JPEG has been used as the \emph{de facto} compression and encapsulation method for images.
 However, standard JPEG configuration does not always perform well for compressing images that are to be processed by a deep learning model, e.g., the standard quality level of JPEG leads to $50\%$ of size overhead (compared with the best quality level selection) on ImageNet under the same inference accuracy in popular computer vision models (e.g., InceptionNet and ResNet).
-Knowing this, designing a better JPEG configuration for online computer vision services is still extremely challenging: 1) Cloud-based computer vision models are usually a black box to end-users; thus, it is challenging to design JPEG configuration without knowing their model structures.
+Knowing this, designing a better JPEG configuration for online computer vision-based services is still extremely challenging: 1) Cloud-based computer vision models are usually a black box to end-users; thus, it is challenging to design JPEG configuration without knowing their model structures.
 2) The ``optimal'' JPEG configuration is not fixed; instead, it is determined by confounding factors, including the characteristics of the input images and the model, the expected accuracy and image size, etc.
@@
 In particular, we design an edge (i.e., user-side) reinforcement learning agent that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.
-Furthermore, we design an explore-exploit mechanism to let the framework fast switch an agent when it detects a performance degradation, mainly due to the input change (e.g., images captured across daytime and night).
-Our evaluation experiments using real-world online computer vision APIs from Amazon Rekognition, Face++, and Baidu Vision, show that our approach outperforms existing baselines by reducing the size of images by 1/2 -- 1/3 while the overall classification accuracy only decreases slightly; Meanwhile, AdaCompress adaptively retrains or reloads the RL agent promptly to maintain the performance.
+Furthermore, we design an \emph{explore-exploit} mechanism to let the framework fast switch an agent when it detects a performance degradation, mainly due to the input change (e.g., images captured across daytime and night).
+Our evaluation experiments using real-world online computer vision-based APIs from Amazon Rekognition, Face++, and Baidu Vision, show that our approach outperforms existing baselines by reducing the size of images by 1/2 -- 1/3 while the overall classification accuracy only decreases slightly; Meanwhile, AdaCompress adaptively re-trains or re-loads the RL agent promptly to maintain the performance.
 

### 2020-03-14 paper/sections/conclusion.tex
improve consistency

@@
 To reduce the upload traffic load of deep learning applications, most researchers focus on modifying the deep learning model, but this does not apply to the industry because the backend deep model is usually inaccessible for users.
-We present a heuristic solution using an reinforcement learning based agent to decide the proper compression quality level for each image, according to the input image and the backend service.
-Our experiments show that for different backend deep learning cloud services and different input image sceneries, using different quality selection strategy can significantly reduce the upload file size overhead while keeping comparable accuracy.
-Moreover, we design the inference-estimation-querying-retraining mechanism to cope with the input image scenery change and make a proper compression selection strategy for the current scenery.
-Our experiment result shows that once the scenery changes, the mechanism would either reload a pre-trained agent model or retrain a new
-agent intelligently to achieve lower upload file size overhead while maintaining the inference accuracy.
+We present a heuristic solution using an reinforcement learning agent to decide the proper compression quality level for each image, according to the input image and the backend service.
+Our experiments show that for different backend deep learning cloud services and different input image ``sceneries'', using different quality selection strategy can significantly reduce the upload file size overhead while keeping comparable accuracy.
+Moreover, we design the \emph{inference-estimation-querying-retraining} mechanism to cope with the input image scenery change and make a proper compression selection strategy for the current scenery.
+Our experiment result shows that once the scenery changes, the mechanism would either re-load a pre-trained agent model or re-train a new
+agent intelligently to achieve lower upload image size overhead while maintaining the inference accuracy.

### 2020-03-14 paper/sections/design.tex
change the figure format
improve consistency

@@
 
-A brief framework of AdaCompress is shown in Figure \ref{fig: framework}.
-Briefly, it is an RL (reinforcement learning) based system to train an agent to choose the proper compression quality level $ c $ for one image to be compressed by JPEG.
-We discuss the formulation, agent design, reinforcement learning framework, feedback reward, and inference-estimation-querying-retraining mechanism separately in the following subsections.
-We provide experimental details of all the hyperparameters in Sec.
-\ref{sec: evaluation}.
+A brief framework of AdaCompress is shown in Figure~\ref{fig: framework}.
+Briefly, it is an reinforcement learning (Rl)-based system to train an agent to choose the proper compression quality level $ c $ for one image to be compressed by JPEG.
+We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, and \emph{inference-estimation-querying-retraining} mechanism separately in the following subsections.
+We provide experimental details of all the hyperparameters in Sec.~\ref{sec: evaluation}.
 %% \\
@@
 % \colorbox{red}{notation table}
-
-Without loss of generality, we denote the cloud deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $, and it has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input $ x \in X_{\rm ref} $.
+Without loss of generality, we denote the cloud-based deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $, and it has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input image $ x \in X_{\rm ref} $.
 We use this $ \vec{y}_{\rm ref} $ as the ground truth label, and for each image $ x_c $ compressed at compression quality level $ c $, the output $ \vec{y}_c = M(x_c) $.
@@
 
-Where $ j = 1,...,5 $ indicates the prediction labels at top-5 score, $ k = 1,...,{\rm length}(\vec{y}_{\rm ref}) $ means that if anyone of the top-5 predicted labels matches one of the predictions from $ \vec{y}_{\rm ref} $, it would be regarded as a correct prediction.
-In general, we cannot get the cloud deep learning model's in-layer details (e.g., softmax probabilities) for a cloud deep learning service, therefore we use a binary hard label $ d(x, y) \in \{0, 1\} $ to evaluate the accuracy.
+Where $ j = 1,...,5 $ indicates the prediction labels at top-5 score, meaning that if anyone of the top-5 predicted labels matches the ground truth label $ \vec{y}_{\rm ref} $, it would be regarded as a correct prediction.
+In general, we cannot get the cloud-based deep learning model's in-layer details (e.g., softmax probabilities) for a cloud-based deep learning service, therefore we use a binary hard label $ d(x, y) \in \{0, 1\} $ to evaluate the accuracy.
 %% $ d(x, y) \in \{0, 1\} $
@@
 For example, in daytime scenery, the input images are expected to have a bright background and high contrast while nighttime images are usually gray-scaled thermal images.
-Therefore, the agent in one place and one scenery does not need to know all the contextual features in all places and all sceneries.
+Therefore, the agent in one place and one scenery does not need to know all the contextual features in all places and all ``sceneries''.
 We formulate this as contextual group $ \mathcal{X} $.
-This contextual grouping concept is also discussed in the study ~\cite{mcdnn}.
+This contextual grouping concept is also discussed in the study~\cite{mcdnn}.
 
-Initially, the agent tries different compression quality levels $ c_{\min} < c < c_{\max}, c \in \mathbb{N} $ to obtain compressed image $ x_c $ from input image $ x $, and an image compressed at a reference level $ c_{\rm ref} $ is also uploaded to the cloud to obtain $ \vec{y}_{\rm ref} $.
-Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, we can obtain the reference file size $ s_{\rm ref} $ and compressed file size $ s_c $, therefore compute the file compression ratio $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.
+Initially, the agent tries different compression quality levels $ c_{\min} < c < c_{\max}, c \in \mathbb{N} $ to obtain compressed image $ x_c $ from input image $ x $, and an image compressed at a reference level $ c_{\rm ref} $ is also uploaded to the cloud-end to obtain $ \vec{y}_{\rm ref} $.
+Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud-end recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, we can obtain the reference file size $ s_{\rm ref} $ and compressed file size $ s_c $, therefore compute the file compression ratio $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.
 
@@
 The RL agent is expected to give a proper compression quality level $ c $ that minimizing the file size $ s_c $ while keeping the accuracy $ \mathcal{A} $.
-For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $, therefore we can use Deep Q-learning Network \cite{DQN} as the RL agent.
-But naive Deep Q-learning Network can't work well in this task because of the following challenges: %% \\
+For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $, therefore we can use the Deep Q-learning Network~ as the RL agent.
+But naive the Deep Q-learning Network can't work well in this task because of the following challenges: %% \\
 
@@
     \item It takes a long time to train one step in a large inference neural network, making the training process too time-consuming.
-    \item The RL agent starts training from random trials and starts learning after it finds better feedback reward.
-When training from a randomly initialized neural network, the feedback reward is very sparse, making it difficult for the agent to learn.
+    \item The RL agent starts training from random trials and learns from the reward feedback.
+When training from a randomly initialized neural network, the reward feedback is very sparse, making it difficult for the agent to learn.
 \end{itemize}
@@
 
-\subsection{Reinforcement Learning Framework}
+\subsection{reinforcement learning-based Framework}
 
@@
 In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $.
-We denote the \emph{action-value function} as $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $, then the optimal compression quality level at time $ t $ is $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
-In such reinforcement learning formulation, the training phase is to minimize a loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where $ s = \mathcal{E}(f_t) $, and $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $ is the target for the iteration $ i $.
-Especially, $ r $ is the feedback reward, and $ \rho(s, c) $ is a probability distribution over sequences $ s $ and compression quality level $ c $~\cite{DQN}.
-When minimizing the distance of the action-value function's output $ Q(\cdot) $ and target $ y_i $, the action-value function $ Q(\cdot) $ outputs a more accurate estimation of an action.
+We denote the \emph{action-value function} as $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $, and the optimal compression quality level at time $ t $ is $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
+In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where $ s = \mathcal{E}(f_t) $, and $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $ is the target for each iteration.
+Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over sequences $ s $ and compression quality level $ c $~\cite{DQN}.
+When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.
 
 In such a formulation, it is similar to the Deep Q-learning Network problem but not the same.
-Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, therefore there is no signal from the environment telling that an episode has finished.
+Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, i.e., there is no signal from the environment telling that an episode has finished.
 Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $.
-In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction, and we decrease the randomness when training.
-All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its action by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
-The training procedure would converge as the agent's randomness keeps decaying.
-Finally, the agent's action is based on its historical optimal experiences.
-The training procedure is presented in Algorithm \ref{alg: rl-train}, and we list the parameters in Sec.~\ref{sec: evaluation}.
+In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction, and decreases the randomness when training.
+All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
+The training procedure would converge when the agent's randomness keeps decaying.
+Finally, the agent's action is based on its historical ``optimal'' experiences.
+The training procedure is presented in Algorithm~\ref{alg: rl-train}, and we list the parameters in Sec.~\ref{sec: evaluation}.
 
@@
         \end{cases} $
-        \STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to ~\cite{DQN}
+        \STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
         \ENDIF
@@
 
-\subsection{Feedback Reward Design}
+\subsection{Reward Feedback Design}
 
-In our solution, the agent is trained by the feedback reward from the environment $ \{\mathcal{X}, M\} $.
-In the above formulation, we defined compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ in compression quality level $ c $.
-Basically, we want the agent to choose a proper compression quality level that minimizing the file size while remaining acceptable accuracy, therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $.
-We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the reward function $ R(\Delta s, \mathcal{A}) $.
+In our solution, the agent is trained by the reward feedback from the environment $ \{\mathcal{X}, M\} $.
+In the above formulation, we defined compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at compression quality level $ c $.
+Basically, we want the agent to choose a proper compression quality level that minimizing the upload image size while remaining acceptable accuracy, therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $.
+We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $.
 %% \\
@@
 
-As a running system, we introduce an inference-estimation-querying-retraining mechanism to cope with the scenery change in the inference phase, building a system with different components to inferring, capturing the scenery change, then either reloading or retraining the RL agent based on the performance of the cached model.
-The overall system diagram is illustrated in Figure \ref{fig: diagram}.
+As a running system, we introduce an \emph{inference-estimation-querying-retraining} mechanism to cope with the scenery change in the inference phase, building a system with different components to inferring, capturing the scenery change, then either re-loading or re-training the RL agent based on the performance of the cached model.
+The overall system diagram is illustrated in Figure~\ref{fig: diagram}.
 
@@
 
-%% The system diagram is shown in Figure \ref{fig: diagram}.
-We build up the memory buffer $ \mathcal{D} $ and RL (reinforcement learning) training kernel based on the compression and upload driver.
-When the RL kernel is called, it will load transitions from the memory buffer $ \mathcal{D} $ to train the compression quality level predictor $ \phi $.
-When the system is deployed, the pre-trained RL agent $ \phi $ guides the compression driver to compress the input image with an adaptive compression quality level $ c $ according to the input image, then uploads the compressed image to cloud.
+%% The system diagram is shown in Figure~\ref{fig: diagram}.
+We build up the memory buffer $ \mathcal{D} $ and reinforcement learning (RL) training kernel based on the compression and upload driver.
+When the RL training kernel is called, it would load transitions from the memory buffer $ \mathcal{D} $ to train the compression quality level predictor $ \phi $.
+When the system is deployed, the pre-trained RL agent $ \phi $ guides the compression driver to compress the input image at an adaptive compression quality level $ c $ according to the input image, then uploads the compressed image to cloud.
 %% \\
 
-After the AdaCompress is deployed, the input images scenery context $ \mathcal{X} $ may change (e.g., day to night, sunny to rainy), when the scenery changes, the older RL agent's compression selection strategy may not be suitable anymore, causing the overall accuracy decreases.
+After the AdaCompress is deployed, the input image scenery context $ \mathcal{X} $ may change (e.g., day to night, sunny to rainy), when the scenery changes, the older RL agent's compression selection strategy may not be suitable anymore, causing the overall accuracy decreases.
 To cope with the scenery change, we invoke an estimator with a probability $ p_{\rm est} $.
 We do this by generating a random value $ \xi \in (0,1) $ and comparing it to $ p_{\rm est} $.
-If $ \xi \leq p_{\rm est} $ the estimator would be invoked, and AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, therefore calculate $ \mathcal{A}_i $, and save the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ to the memory buffer $ \mathcal{D} $.
-The estimator also compares the recent $ n $ steps' average accuracy $ \bar{\mathcal{A}}_n $ and the initial accuracy threshold $ \mathcal{A}_0 $ in memory $ \mathcal{D} $.
-Once the recent average accuracy is much lower than the initial accuracy threshold, the estimator would query an RL agent model to replace the current agent model and test the performance of the reloaded model.
-To test the reloaded model's performance, the estimator computes the average accuracy $ \bar{\mathcal{A}}^*_n $.
-If $ \bar{\mathcal{A}}^*_n $ is still lower than the accuracy threshold, the estimator would invoke the RL training kernel to retrain the agent.
+If $ \xi \leq p_{\rm est} $, the estimator would be invoked, and AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, therefore calculate $ \mathcal{A}_i $, and save the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ to the memory buffer $ \mathcal{D} $.
+The estimator also compares the recent $ n $ steps' average accuracy $ \bar{\mathcal{A}}_n $ and the initial accuracy threshold $ \mathcal{A}_0 $.
+Once the recent average accuracy is lower than the initial accuracy threshold, the estimator would query an RL agent model to replace the current agent model and test the performance of the loaded model.
+To test the loaded model's performance, the estimator computes the average accuracy $ \bar{\mathcal{A}}^*_n $.
+If $ \bar{\mathcal{A}}^*_n $ is still lower than the accuracy threshold, the estimator would invoke the RL training kernel to re-train the agent.
 Once the estimator discovers that the trained reward is higher than the reward threshold, it would stop the training kernel, cache the trained RL agent and switch back to the normal inference state.
 
-Since the reference image $ x_{\rm ref} $ and the compressed image $ x_i $ are both needed in the retraining phase, causing a large uploading file size overhead, especially when the scenery changes frequently (e.g., day to night, then night to day).
-To avoid unnecessary upload traffic load in the retraining phase, we build up the model caching library to cache the trained RL agent models.
-When capturing the scenery change, we query a pre-trained model from the model caching library rather than retraining from scratch.
+Since the reference image $ x_{\rm ref} $ and the compressed image $ x_i $ are both needed in the re-training phase, causing a large upload image size overhead, especially when the scenery changes frequently (e.g., day to night, then night to day).
+To avoid unnecessary upload traffic load in the re-training phase, we build up the model caching library to cache the trained RL agent models.
+When capturing the scenery change, we query a pre-trained model from the model caching library rather than re-training from scratch.
 %% \\
@@
 AdaCompress adaptively switch itself between four states. The switching policy is shown as Figure~\ref{fig: state-switching}.
-
 %\begin{figure}[H]
@@
 %    \node[initial, state] (B)                    {inference};
-%    \node[state]         (C) [below right of=B] {retrain};
+%    \node[state]         (C) [below right of=B] {re-train};
 %    \node[state]         (D) [above right of=C] {estimate};
@@
 %\end{figure}
-
 \begin{figure}[H]
@@
     \node[initial, state] (B)                    {inference};
-    \node[state]         (C) [below of=B] {retraining};
+    \node[state]         (C) [below of=B] {re-training};
     \node[state]         (D) [right of=B, node distance=4cm] {estimation};
@@
 
-\subsubsection{\textbf{Inference:}}
+\subsubsection{\textbf{Inference}}
 
 For most times, AdaCompress runs in this state.
-In this state, only the compressed images are uploaded to the cloud to achieve minimum uploading file size overhead.
+In this state, only the compressed images are uploaded to the cloud to achieve minimum upload image size overhead.
 To keep a stable accuracy performance even the input image scenery changes, the agent would occasionally switch to the estimation state with the probability of $ p_{\rm est} $, meanwhile remain the inference state with the probability of $ 1 - p_{\rm est} $.
@@
 
-\subsubsection{\textbf{Estimation:}}
+\subsubsection{\textbf{Estimation}}
 
@@
 When the average accuracy $ \bar{\mathcal{A}}_n $ of the latest $ n $ steps is higher than the accuracy threshold $ \mathcal{A}_0 $, it stays in the estimation state with the probability of $ p_{\rm est} $ or switches back into the inference state with the probability of $ 1 - p_{\rm est} $.
-Once the average accuracy $ \bar{\mathcal{A}}_n $ is lower than the initial accuracy threshold $ \mathcal{A}_0 $, indicating that the current agent is no more suitable for the current input image scenery, AdaCompress turns into the model querying state and loads a new RL agent model from the model caching library.
+Once the average accuracy $ \bar{\mathcal{A}}_n $ is lower than the initial accuracy threshold $ \mathcal{A}_0 $, indicating that the current agent is no more suitable for the current input image scenery, AdaCompress would turn into the model querying state and loads a new RL agent model from the model caching library.
 %% \\
 
-Therefore, the estimating probability of $ p_{\rm est} $ is vital to the whole system.
-On the one hand, the estimator should be invoked occasionally to estimate current agent's accuracy, so that to capture the scenery change on time; on the other hand, the estimator uploads the reference image $ x_{\rm ref} $ along with the compressed image, therefore the uploading file size overhead is greater than the conventional benchmark solution, causing higher upload traffic load.
+Therefore, the estimation probability of $ p_{\rm est} $ is vital to the whole system.
+On the one hand, the estimator should be invoked occasionally to estimate current agent's accuracy, so that to capture the scenery change on time; on the other hand, the estimator uploads the reference image $ x_{\rm ref} $ along with the compressed image, therefore the upload image size overhead is greater than the conventional benchmark solution, causing higher upload traffic load.
 %% \\
@@
 
-With this definition, an intuitive formulation of the change of $ p_{\rm est} $ is in inverse proportion of the gradient of $ \mathcal{A} $, meaning that when the recent accuracy is going down, the estimation probability $ p_{\rm est} $ would increase.
+With this definition, an intuitive formulation of the change of $ p_{\rm est} $ is in inverse proportion of the gradient of $ \mathcal{A} $, meaning that when the recent accuracy decreases, the estimation probability $ p_{\rm est} $ would increase.
 We formulate that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a scaling factor.
-With this recursive formula, we have the general term of $ p_{\rm est} $ with an initial estimation probability $ p_0 $ is $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $.
+With this recursive formula, we have the general term of $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $, with an initial estimation probability $ p_0 $.
 
-\subsubsection{\textbf{Model Querying:}}
+\subsubsection{\textbf{Model Querying}}
 
-The model querying state is designed to cope with the scenery change before retraining.
+The model querying state is designed to cope with the scenery change before re-training.
 It loads a new RL agent model from the model caching library and tests whether the loaded agent model is suitable for the current scenery by re-calculating the average accuracy.
 If the new average accuracy $ \bar{\mathcal{A}}^*_n $ is higher than the accuracy threshold $ \mathcal{A}_0 $, indicating that the loaded agent model is suitable for the current scenery, AdaCompress would switch back to the normal inference state using the loaded agent model.
-Otherwise, AdaCompress would switch into the retraining state and invokes the RL training kernel to retrain a new RL agent for the current scenery.
+Otherwise, AdaCompress would switch into the re-training state and invokes the RL training kernel to re-train a new RL agent for the current scenery.
 
-In this way, AdaCompress is capable to cope with the scenery change in a cached ``memory'' manner, avoiding retraining the agent model at every scenery change, therefore cutting down the uploading file size overhead.
-Meanwhile, the agent caching strategy would cause a little storage overhead on local terminal devices.
+In this way, AdaCompress is capable to cope with the scenery change in a cached ``memory'' manner, avoiding re-training the agent model at every scenery change, therefore cutting down the upload image size overhead.
+However, the agent caching strategy would cause a little storage overhead on local terminal devices.
 
-\subsubsection{\textbf{Retraining:}}
+\subsubsection{\textbf{re-training}}
 
-This state is to adapt the agent to the current input image scenery by retraining it with the memory buffer $ \mathcal{D} $, which is similar to the training procedure.
-The retraining phase has finished upon the recent $ n $ steps' average reward $ \bar{r}_n $ is higher than the user-defined threshold $ r_{\rm th} $.
-And when the retraining procedure finishes, the memory buffer $ \mathcal{D} $ would be flushed, preparing to save new transitions for the retraining of a next scenery change.
+This state is to adapt the agent to the current input image scenery by re-training it with the memory buffer $ \mathcal{D} $, which is similar to the training procedure.
+The re-training phase has finished upon the recent $ n $ steps' average reward $ \bar{r}_n $ is higher than the user-defined threshold $ r_{\rm th} $.
+And when the re-training procedure finishes, the memory buffer $ \mathcal{D} $ would be flushed, preparing to save new transitions for the re-training of a next scenery change.
 The trained RL agent model would be cached in the model caching library and be used to switch to the inference state.
@@
 
-In the inference phase, the pre-trained RL agent predicts a proper compression quality level according to the input image's feature.
+In the inference phase, the pre-trained RL agent chooses a proper compression quality level according to the input image's feature.
 The reference image is not uploaded to the cloud anymore; only the compressed image is uploaded, therefore, the upload traffic load is reduced.
-We notice that the RL agent's behaviors are various for different input image sceneries and backend cloud services, therefore we try to make further investigations by plotting the RL agent's "attention map" (i.e., visual explanations of why the agent chooses a compression quality level).
+We notice that the RL agent's behaviors are various for different input image ``sceneries'' and backend cloud services, therefore we try to make further investigations by plotting the RL agent's "attention map" (i.e., visual explanations of why the agent chooses a compression quality level).
 %% \\
 
-\subsubsection{\textbf{Compression Level Choice Variation:}}
+\subsubsection{\textbf{Compression Level Choice Variation}}
 
-In our experiment, we find that in different cloud application environments, the agent's final chosen compression quality levels can be quite different.
-As shown in Figure \ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's choices are distributed more evenly.
-Therefore, the optimal compression strategy should be different for different backend cloud services.
+In our experiment, we find that in different cloud application environments, the agent's chosen compression quality levels can be quite different.
+As shown in Figure~\ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's choices are distributed more evenly.
+Therefore, the ``optimal'' compression strategy should be different for different backend cloud services.
 This variation is caused by the interaction between the agent and the backend cloud model in the training phase.
@@
 
-Moreover, in our experiment, the agent presents different behaviors when the input images change from one dataset to another.
-Figure \ref{fig: dataset_change} shows the agent's choices for the same backend cloud model (Baidu Vision) but different image datasets.
-We prepare two datasets indicating two contextual sceneries.
+Moreover, in our experiment, the agent presents different behaviors when the input image changes from one dataset to another.
+Figure~\ref{fig: dataset_change} shows the agent's choices for the same backend cloud model (Baidu Vision) but different image datasets.
+We prepare two datasets indicating two contextual ``sceneries''.
 We randomly sample images from ImageNet~\cite{ImageNet} whose images are mostly taken in the daytime, to act as a daytime scenery, and randomly select nighttime images from the FLIR Thermal Dataset~\cite{FLIR} to form another dataset to act as a nighttime scenery.
@@
 \begin{figure}[htb]
-    \includegraphics[width=\linewidth]{figures/dataset_change.eps}
-    \caption{Histogram of RL agent's best compression quality level selection for different input image sceneries}
+    \includegraphics[width=\linewidth]{figures/dataset_change.pdf}
+    \caption{Histogram of RL agent's best compression quality level selection for different input image ``sceneries''}
     \label{fig: dataset_change}
@@
 
-\subsubsection{\textbf{Attention Map Variation:}}
+\subsubsection{\textbf{Attention Map Variation}}
 \label{subsec: attention map}
@@
 To take insight investigations, we plot the importance map of a chosen compression quality level.
-We leverage a conventional visualization algorithm, Grad-Cam, to observe the Deep Q-Learning Network's interest when choosing compression quality levels.
+We leverage a conventional visualization algorithm, Grad-Cam, to observe the Deep Q-Learning Network-based agent's interest when choosing compression quality levels.
 Grad-Cam is a widely used solution to present the importance map of a deep neural network, it is done by calculating the gradients of each target concept and backtracking to the final convolution layer.
@@
 In our investigations, we find that in different environments $ \{\mathcal{X}, M\} $, the RL agent picks up compression quality level based on the visual textures of different regions in the image.
-As shown in Figure \ref{fig: attention}, picture 1a -- 1d are some pictures that the agent chooses to compress highly, the agent selects lower compression quality levels based on the complex texture of the images.
-On the contrary, for pictures 2a -- 2d, the agent chooses higher compression quality levels to preserve more details, and the agent's interest falls on some smooth regions.
-Especially for 1a and 2a, in picture 1a, the agent chooses a lower quality compression level based on the rough central region though there are smooth regions around it, and in picture 2a, the agent chooses a relatively higher compression quality level based on the surrounding smooth region rather than the central region.
+As shown in Figure~\ref{fig: attention}, picture 1a -- 1d are some pictures which the agent chooses to compress highly, the agent selects lower compression quality levels based on the complex texture of the images.
+On the contrary, for pictures 2a -- 2d, the agent chooses higher compression quality levels to preserve more details since its interest falls on some smooth regions.
+Especially for 1a and 2a, in picture 1a, the agent chooses a lower quality compression level based on the rough central region though there are smooth regions around it, but in picture 2a, the agent chooses a relatively higher compression quality level based on the surrounding smooth region rather than the central region.
 %% \\

### 2020-03-14 paper/sections/evaluation.tex
change the figure format
improve consistency

@@
 For the cloud deep learning services, we choose Baidu Vision, Face++ object detection services, and Amazon Rekognition.
-In the experiments, we use two datasets mentioned before in Sec.\ref{subsec:insight}, ImageNet dataset indicating daytime scenery and the FLIR Thermal Dataset indicating nighttime scenery.
-Some important hyperparameters in our experiments are given in Table \ref{tab: parameters}.
+In the experiments, we use two datasets mentioned before in Sec.~\ref{subsec:insight}, ImageNet dataset indicating daytime scenery and the FLIR Thermal Dataset indicating nighttime scenery.
+Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.
 
@@
 We use the ImageNet dataset in size reduction and accuracy performance experiment, DeepN-JPEG comparative experiment, and end-to-end latency simulation.
-Moreover, we use ImageNet and the FLIR Thermal Dataset alternately to simulate the scenery change in the inference-estimation-querying-retraining mechanism experiment, and analyze the RL agent's best compression strategy selection in different input image sceneries.
+Moreover, we use ImageNet and the FLIR Thermal Dataset alternately to simulate the scenery change in the \emph{inference-estimation-querying-retraining} mechanism experiment, and analyze the RL agent's best compression strategy selection in different input image ``sceneries''.
 
@@
 In our experiments, we measure the compressed and original image's file size to obtain the compression rate $ \Delta s $.
-Since we don't have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric, the formula of $ \mathcal{A} $ is presented in Sec.
-~\ref{subsec: formulation}.
+Since we don't have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric, the formula of $ \mathcal{A} $ is presented in Sec.~\ref{subsec: formulation}.
 
-\subsection{Upload Size Overhead}
+\subsection{Upload Image Size Overhead}
 
@@
 
-Figure \ref{fig: train_steps} presents the upload traffic load of the training and inference phase, to be more intuitionistic, we plot the size overhead $ \frac{s}{s_{\rm ref}} $ as the $ y $-axis where $ s $ is the real upload size of AdaCompress, $ s_{\rm ref} $ is the benchmark upload size.
+Figure~\ref{fig: train_steps} presents the upload traffic load of the training and inference phase, to be more intuitionistic, we plot the size overhead $ \frac{s}{s_{\rm ref}} $ as the $ y $-axis where $ s $ is the real upload size of AdaCompress, $ s_{\rm ref} $ is the benchmark upload size.
 Therefore $ y \geq 1 $ means that our solution uploads more data then benchmark, and $ y < 1 $ means the compression rate of AdaCompress.
-From Figure \ref{fig: train_steps} we can see that as the training procedure runs, the upload size decreases because the RL agent learns to choose better compression quality levels to upload fewer data.
+From Figure~\ref{fig: train_steps} we can see that as the training procedure runs, the upload image size decreases because the RL agent learns to choose better compression quality levels to upload fewer data.
 In the training phase, to train the agent while remaining a convincing recognition result, we have to upload the original image to the cloud to get the real result, along with the compressed image to obtain reward feedback, therefore the upload traffic load is even higher than the conventional solution.
-But once the training phase has finished, the upload traffic load is much lower than the benchmark.
-As shown in Figure \ref{fig: compress_performance}, in the inference phase, AdaCompress's upload size is only 1/2 of the benchmark's.
+But once the training phase has finished, the upload traffic load is lower than the benchmark.
+As shown in Figure~\ref{fig: compress_performance}, in the inference phase, AdaCompress's upload size is only 1/2 of the benchmark's.
 %% \\
@@
 
-Figure \ref{fig: compress_performance} presents the compression performance in the inference phase for each cloud service.
+Figure~\ref{fig: compress_performance} presents the compression performance in the inference phase for each cloud service.
 We test AdaCompress on Face++, Baidu Vision and Amazon Rekognition, comparing to the conventional compression level, for all tested cloud services, our solution can reduce the upload size by more than 1/2, meanwhile, the relative accuracy, indicated by brown bars, only decreases about 7\% on average, proving the efficiency of our design.
@@
 \begin{figure}[htbp]
-    \includegraphics[width=\linewidth]{figures/compare_DeepN.eps}
+    \includegraphics[width=\linewidth]{figures/compare_DeepN.pdf}
     \caption{Comparative compression performance between DeepN-JPEG and AdaCompress}
@@
 
-Figure \ref{fig: compare_DeepN} presents a comparison performance between DeepN-JPEG and AdaCompress for each cloud service.
+Figure~\ref{fig: compare_DeepN} presents a comparison performance between DeepN-JPEG and AdaCompress for each cloud service.
 As we can see, both DeepN-JPEG and AdaCompress cut down the upload size overhead more than 1/2.
@@
 Compared with DeepN-JPEG's average accuracy is about 85\% on three cloud services, while AdaCompress achieves a better average accuracy of 93\%.
-In a word, comparing to the DeepN-JPEG framework, AdaCompress presents a similar upload traffic load reduction performance but achieving higher inference accuracy for computer vision cloud services.
+In a word, comparing to the DeepN-JPEG framework, AdaCompress presents a similar upload traffic load reduction performance but achieving higher inference accuracy for online computer vision-based services.
 
@@
 (i.e., the explanation of why AdaCompress achieves a better accuracy).
-As shown in Figure \ref{fig: compare_image}, for picture 1a, compared to DeepN-JPEG, AdaCompress compresses the image at the compression quality level of 15, a more aggressive compression quality level to reduce upload size overhead.
-On the contrary, for picture 2a of Figure \ref{fig: compare_image}, DeepN-JPEG compresses the image with the same quantization table, but AdaComperss chooses a higher compression quality level to preserve more details so that the backend deep learning model can still recognize the picture.
+As shown in Figure~\ref{fig: compare_image}, for picture 1a, compared to DeepN-JPEG, AdaCompress compresses the image at the compression quality level of 15, a more aggressive compression quality level to reduce upload size overhead.
+On the contrary, for picture 2a of Figure~\ref{fig: compare_image}, DeepN-JPEG compresses the image with the same quantization table, but AdaComperss chooses a higher compression quality level to preserve more details so that the backend deep learning model can still recognize the picture.
 Being different from the DeepN-JPEG framework compresses all images with the same quantization table, our RL agent chooses a lower compression quality level for picture 1a and a relatively higher compression quality level for picture 2a based on the feature of the input image.
@@
         \item AdaCompress and DeepN-JPEG both decrease the upload size overhead more than 1/2, but AdaCompress maintains higher inference accuracy.
-        \item DeepN-JPEG requires the original dataset information to redesign the quantization table, while AdaCompress chooses compression quality level adaptively without any pre-knowledge of the original dataset.
-        \item When the scenery changes, DeepN-JPEG still compresses images with the same quantization table, while AdaCompress's inference-estimation-querying-retraining mechanism captures the scenery change and invokes either model querying method or retraining kernel to generate a more suitable compression selection strategy for the current scenery.
-        \item DeepN-JPEG redesigns the quantization table locally, while AdaCompress needs to upload origin images and compressed images to the cloud in the training phase, leading some upload size overhead at the beginning.
+        \item DeepN-JPEG requires the original dataset information to re-design the quantization table, while AdaCompress chooses compression quality level adaptively without any pre-knowledge of the original dataset.
+        \item When the scenery changes, DeepN-JPEG still compresses images with the same quantization table, while AdaCompress's \emph{inference-estimation-querying-retraining} mechanism captures the scenery change and invokes either model querying method or retraining kernel to \emph{generate} a more suitable compression selection strategy for the current scenery.
+        \item DeepN-JPEG re-designs the quantization table \emph{locally}, while AdaCompress needs to upload origin images and compressed images to the cloud in the training phase, leading some upload size overhead at the beginning.
     \end{itemize}
@@
 
-To evaluate the efficiency of the inference-estimation-querying-retraining mechanism, we feed AdaCompress with a combined dataset whose first 2000 images from FLIR Thermal images, the later 3000 images randomly sampled from ImageNet, and the last 2000 images from FLIR Thermal images.
-We adapt AdaCompress's current RL agent to FLIR Thermal nighttime scenery by training it on the FLIR Dataset, and we run AdaCompress on the combined dataset, observing AdaCompress's behavior upon the scenery changes at step 2000 and 5000.
+To evaluate the efficiency of the \emph{inference-estimation-querying-retraining} mechanism, we feed AdaCompress with a combined dataset whose first 2000 images from FLIR Thermal images, the later 3000 images randomly sampled from ImageNet, and the last 2000 images from FLIR Thermal images.
+We adapt AdaCompress's current RL agent to FLIR Thermal nighttime scenery by training it on the FLIR dataset, and we run AdaCompress on the combined dataset, observing AdaCompress's behavior upon the scenery changes at step 2000 and 5000.
 %% \\
 
-We illustrate AdaCompress's behavior in Figure \ref{fig: running-retrain}, the $ x $-axis indicates steps, the vertical red line means the dataset change (i.e.
+We illustrate AdaCompress's behavior in Figure~\ref{fig: running-retrain}, the $ x $-axis indicates steps, the vertical red line means the dataset change (i.e.
 scenery change).
 We plot AdaCompress's overall accuracy as the green line and the estimation probability $ p_{\rm est} $ as the gray line.
-At the bottom of Figure \ref{fig: running-retrain}, we also plot the scaled upload size of AdaCompress and benchmark solution to illustrate the upload size overhead in the inference phase.
+At the bottom of Figure~\ref{fig: running-retrain}, we also plot the scaled upload size of AdaCompress and benchmark solution to illustrate the upload size overhead in the inference phase.
 %with a $ \Delta $ mark on $ x $-axis
@@
 %\end{figure}
-
-\begin{figure}[htbp]
-    \includegraphics[width=\linewidth]{figures/running-retrain.eps}
+\begin{figure}[H]
+    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
     \caption{AdaCompress's reaction upon scenery change}
@@
 
-From Figure \ref{fig: running-retrain} we can see that AdaCompress can adaptively update the estimation probability $ p_{\rm est} $, usually, when the overall accuracy decreases, AdaCompress would increase the estimation probability, trying to capture the scenery change.
+From Figure~\ref{fig: running-retrain} we can see that AdaCompress can adaptively update the estimation probability $ p_{\rm est} $, usually, when the overall accuracy decreases, AdaCompress would increase the estimation probability, trying to capture the scenery change.
 When the overall accuracy is stable and high enough, the estimation probability $ p_{\rm est} $ decreases to reduce transmission.
@@
 
-Upon the first data scenery changes (i.e., night to day) shown as the first vertical red line in Figure \ref{fig: running-retrain}, comparing to the earlier steps, the accuracy decreases dramatically and therefore $ p_{\rm est} $ raises to determine whether the scenery changes.
+Upon the first data scenery changes (i.e., night to day) shown as the first vertical red line in Figure~\ref{fig: running-retrain}, comparing to the earlier steps, the accuracy decreases dramatically and therefore $ p_{\rm est} $ raises to determine whether the scenery changes.
 The accuracy keeps dropping in the following estimations, indicating that the current RL agent is no more suitable for the current input scenery.
-At the moment, AdaCompress should switch into the model querying state and reload a new RL agent model from the model caching library.
+At the moment, AdaCompress should switch into the model querying state and re-load a new RL agent model from the model caching library.
 However, there is no model except the current RL agent in the model caching library at that time.
-Therefore, AdaCompress starts to retrain at once, to adapt the RL agent into the current scenery.
-The retraining steps are shown as the light-blue region in Figure~\ref{fig: running-retrain}.
-In the retraining phase, AdaCompress always uses the reference image's prediction label $ \vec{y}_{\rm ref} $ as the output result, therefore the accuracy $ \mathcal{A} $ and $ p_{\rm est} $ are locked to 1.
-After finishing retraining the agent in the daytime scenery, the trained agent is cached in the model cachling library, and in the following iterations, sometimes the accuracy decreases accidentally, and the estimation probability $ p_{\rm est} $ also raises to get more samples.
-The accuracy is not lower than the accuracy threshold $ \mathcal{A}_0 $ , therefore the retraining phase would not be triggered again until the second data scenery changes.
+Therefore, AdaCompress starts to re-train at once, to adapt the RL agent into the current scenery.
+The re-training steps are shown as the light-blue region in Figure~\ref{fig: running-retrain}.
+In the re-training phase, AdaCompress uses the reference image's prediction label $ \vec{y}_{\rm ref} $ as the output result, therefore the accuracy $ \mathcal{A} $ and $ p_{\rm est} $ are locked to 1.
+After finishing re-training the agent in the daytime scenery, the trained agent is cached in the model cachling library, and in the following iterations, sometimes the accuracy decreases accidentally, and the estimation probability $ p_{\rm est} $ also raises to get more samples.
+The accuracy is not lower than the accuracy threshold $ \mathcal{A}_0 $ , therefore the re-training phase would not be triggered again until the second data scenery changes.
 %% \\
 
-Upon the second data scenery changes (i.e., day to night) shown as the second vertical red line in Figure \ref{fig: running-retrain}, like the first scenery change, the accuracy decreases and $ p_{\rm est} $ raises, indicating that the current RL agent is no more suitable again.
-AdaCompress switches into the model querying state at once and reloades a new RL agent model (i.e., the initial model trained on the FLIR Thermal images) from the model caching library.
+Upon the second data scenery changes (i.e., day to night) shown as the second vertical red line in Figure~\ref{fig: running-retrain}, like the first scenery change, the accuracy decreases and $ p_{\rm est} $ raises, indicating that the current RL agent is no more suitable again.
+AdaCompress switches into the model querying state at once and re-loades a new RL agent model (i.e., the initial model trained on the FLIR Thermal images) from the model caching library.
 When using the new agent in this scenery, the accuracy stops decreasing and maintains above the accuracy threshold, indicating the current RL agent is suitable for the current scenery.
@@
 
-From Figure \ref{fig: running-retrain} we can also observe the uploading file size overhead in different phases, in retraining phase, AdaCompress uploads more data than the conventional benchmark, but in inference phase, AdaCompress's upload size is only half of the benchmark's.
-Especially when the second data scenery changes, AdaCompress achieves a lower upload traffic load by loading a suitable RL agent model rather than retraining from scratch.
+From Figure~\ref{fig: running-retrain} we can also observe the uploading file size overhead in different phases, in re-training phase, AdaCompress uploads more data than the conventional benchmark, but in inference phase, AdaCompress's upload size is only half of the benchmark's.
+Especially when the second data scenery changes, AdaCompress achieves a lower upload traffic load by loading a suitable RL agent model rather than re-training from scratch.
 %% \\
@@
 2019, to verify the end-to-end latency performance.
-The latency comparison is listed in Table \ref{tab: latency-overhead}.
+The latency comparison is listed in Table~\ref{tab: latency-overhead}.
 %% \\

### 2020-03-14 paper/sections/introduction.tex
improve consistency

@@
 
-\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning based computer vision applications.
-Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19 \cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's computer vision applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.
+\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications.
+Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.
 
 To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it.
-Though JPEG has been used as the {\em de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory.
-Liu et al.~\cite{DeepN-JPEG} showed that by redesigning the \emph{quantization table} in the default JPEG configuration, one can compress an image to a smaller version while maintaining the same inference accuracy for a deep computer vision model.
+Though JPEG has been used as the \emph{de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory.
+Liu et al.~\cite{DeepN-JPEG} showed that by re-designing the quantization table in the default JPEG configuration, one can compress an image to a smaller version while maintaining the same inference accuracy for a deep computer vision model.
 However, such quantization solutions usually assume the inference model is fixed.
 
-We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different cloud computer vision services, without any prior knowledge of the original model and input images?
-In this paper, we propose a reinforcement learning based framework to select JPEG configurations adaptively.
+We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different online computer vision-based services, without any prior knowledge of the original model and input images?
+In this paper, we propose a reinforcement learning-based framework to select JPEG configurations adaptively.
 In our solution, we tackle the following design challenges.
@@
 
-\item \emph{Lack of information about the cloud computer vision models.} Previous studies \cite{DeepN-JPEG,torfason2018towards,gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging the original computer vision model into it.
-However, the structure details of online cloud computer vision models are usually proprietary and not open to the users.
+\item \emph{Lack of information about the cloud-based computer vision models.} Previous studies~\cite{DeepN-JPEG, torfason2018towards, gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging the original computer vision model into it.
+However, the structure details of online computer vision models are usually proprietary and not open to the users.
 
-\item \emph{Different cloud computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different cloud computer vision services, i.e., it can \emph{generate} JPEG configuration for different models.
-However, today's cloud computer vision algorithms, based on deep and convolutional computations, are quite hard to understand.
+\item \emph{Different cloud-based computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different online computer vision-based services, i.e., it can \emph{generate} JPEG configuration for different models.
+However, today's cloud-based computer vision algorithms, based on deep and convolutional computations, are quite hard to understand.
 The same compression quality level could lead to a totally different accuracy performance.
-Some examples are shown in Figure \ref{fig: compress_accuracy}: picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning models give different inference results, only because they are compressed at different quality levels.
+Some examples are shown in Figure~\ref{fig: compress_accuracy}: picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning model gives different inference results, only because they are compressed at different quality levels.
 And such a relationship is not apparent, e.g., picture 3b is highly compressed and looks destroyed comparing to picture 3a, but the deep learning model can still recognize it.
@@
 
-To address the above challenges, we present a reinforcement learning based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner.
-This paper is an extension of our earlier conference paper \cite{2019adacompress}, with the following contributions:
+To address the above challenges, we present a reinforcement learning-based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision-based APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner.
+This paper is an extension of our earlier conference paper~\cite{2019adacompress}, with the following contributions:
 
-$\rhd$ We design an interactive training environment that can be applied to different computer vision cloud services.
-We propose a Deep Q-learning Network based agent to evaluate and predict the performance of a compression quality level on an input image.
-In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU \cite{google-tpu}, Huawei Atlas 500 edge station \cite{huawei-atlas500}).
+$\rhd$ We design an interactive training environment that can be applied to different online computer vision-based services.
+We propose a Deep Q-learning Network-based~\cite{DQN} agent to evaluate and predict the performance of a compression quality level on an input image.
+In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU~\cite{google-tpu}, Huawei Atlas 500 edge station~\cite{huawei-atlas500}).
 
-$\rhd$ We build a reinforcement learning framework to train the agent in the above environment.
+$\rhd$ We build a reinforcement learning-based framework to train the agent in the above environment.
 The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size.
-Based on \cite{2019adacompress}, we further propose an \emph{explore-exploit} mechanism let the agent switch between ``sceneries''.
+Based on~\cite{2019adacompress}, we further propose an \emph{explore-exploit} mechanism to let the agent switch between ``sceneries''.
 In particular, after deploying the agent, an \emph{inference-estimate-retrain} solution is designed to restart the training once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.
 
-$\rhd$ In this journal extension, we provide more analysis and insights on our design.
-By analyzing the Q network's behaviors using Grad-Cam \cite{grad-cam}, we provide the reasons that the Q network chooses a specific compression quality level.
+$\rhd$~~In this journal extension, we provide more analysis and insights on our design.
+By analyzing the Deep Q-learning Network-based agent's behaviors using Grad-Cam~\cite{grad-cam}, we provide the reasons that the agent chooses a specific compression quality level.
 We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.
 
-$\rhd$ We evaluate our system on representative cloud deep learning services, including Amazon Rekognition \cite{amazon_rekognition}, Face++ \cite{face++_service} and Baidu Vision \cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy.
-Compared to baseline DeepN-JPEG \cite{DeepN-JPEG}, the inference accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.
+$\rhd$ We evaluate our system on representative cloud deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy.
+Compared to baseline DeepN-JPEG~\cite{DeepN-JPEG}, the overall accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.
 
 % \begin{itemize}
-% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work \cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase.
+% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work~\cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase.
 Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load.
 In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
-% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to \cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance.
+% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to~\cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance.
 Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG.
@@
 % \end{itemize}
-
 The rest of this paper is organized as follows.

### 2020-03-14 paper/sections/relatedwork.tex
improve consistency

@@
 
-As cloud-based computer vision services have become the norm for today's applications ~\cite{huynh2017deepmon, agrawal2015cloudcv}, many studies have been devoted to improving the cloud-based model execution, including model compression and data compression.
+As online computer vision-based services have become the norm for today's applications~\cite{huynh2017deepmon, agrawal2015cloudcv}, many studies have been devoted to improving the cloud-based model execution, including model compression and data compression.
 
@@
 
-Though the accurate term is still for the community to debate, we use ``model compression'' to represent the studies on {\em compressing} and {\em moving} the deep learning models close to users.
-Many studies tried to compress the deep learning models and deploy them \emph{locally} ~\cite{prun_quanti, pruning_han, quantize, quantize_3bit, quantization, structured_pruning}, i.e., running an alternative ``smaller version'' of a computer vision model at the user end, to avoid the image upload so that to improve the inference efficiency.
-Other studies proposed to run a part of a deep learning model locally ~\cite{ILP_Decoupling, jalad, Edge_LBP, Neurosurgeon}, by decoupling the deep learning model into different parts, e.g., based on the layers in the deep learning model, so that a part of the inference is done locally to save some execution time.
-However, these solutions usually need to \emph{re-train} the model, using the original dataset of the model, which is not practical for today's cloud computer vision services that are merely a black box to end-users, e.g., in the form of a RESTful API.
+Though the accurate term is still for the community to debate, we use ``model compression'' to represent the studies on \emph{compressing} and \emph{moving} the deep learning models close to users.
+Many studies tried to compress the deep learning models and deploy them \emph{locally}~\cite{prun_quanti, pruning_han, quantize, quantize_3bit, quantization, structured_pruning}, i.e., running an alternative ``smaller version'' of a computer vision model at the user-side, to avoid the image upload so that to improve the inference efficiency.
+Other studies proposed to run a part of a deep learning model \emph{locally}~\cite{ILP_Decoupling, jalad, Edge_LBP, Neurosurgeon}, by decoupling the deep learning model into different parts, e.g., based on the layers in the deep learning model, so that a part of the inference is done \emph{locally} to save some execution time.
+However, these solutions usually need to \emph{re-train} the model, using the original dataset of the model, which is not practical for today's online computer vision-based services that are merely a black box to end-users, e.g., in the form of a RESTful API.
 
@@
 
-Data compression solutions study how to compress the original data (e.g., a video or image) to be inferred by the cloud deep learning model, so that less traffic is used to upload the data to improve inference speed.
-Conventional data compression solutions (e.g., JPEG \cite{jpeg}, WebP \cite{calore2010meet}, JPEG2000 \cite{rabbani2002jpeg2000} etc.) and some recent neural network based compression solutions ~\cite{toderici2017full,theis2017lossy,toderici2015variable, rippel2017real} are initially designed for the Human-Visual System.
-In recent years, researchers found that the human visually optimized data compression solutions are not usually applicable to deep learning vision models.
-Delac et al.~\cite{delac2005effects} observed that, in some cases, higher compression level does not always deteriorate the model inference accuracy, even improves it slightly.
-Dodge et al.~\cite{dodge2016understanding} further discovered that besides the JPEG compression, four types of quality distortions (blur, noise, contrast, and the JPEG2000 compression) can also affect the performance in deep learning inference.
-Liu et al.~\cite{DeepN-JPEG} proposed that the conventional JPEG image compression framework is designed for the Human-Visual System which is not suitable for the deep neural network, leading to cloud computer vision services' accuracy degradation at lower images' compression quality level.
+Data compression solutions study how to compress the original data (e.g., a video or image) to be inferred by the cloud-based deep learning model, so that less traffic is used to upload the data to improve inference speed.
+Conventional data compression solutions (e.g., JPEG~\cite{jpeg}, WebP~\cite{calore2010meet} and JPEG2000~\cite{rabbani2002jpeg2000}, etc.) and some recent neural network-based compression solutions~\cite{toderici2017full, theis2017lossy, toderici2015variable, rippel2017real} are initially designed for the Human-Visual System.
+In recent years, researchers found that the human visually optimized-based data compression solutions are not usually applicable to deep learning vision models.
+Delac et al.~\cite{delac2005effects} observed that, in some cases, a higher compression quality level does not always deteriorates the model inference performance, even improves it slightly.
+Dodge et al.~\cite{dodge2016understanding} further discovered that besides the JPEG compression, four types of quality distortions (blur, noise, contrast, and the JPEG2000 compression~\cite{rabbani2002jpeg2000}) can also affect the inference performance of the deep learning models.
+Liu et al.~\cite{DeepN-JPEG} proposed that the conventional JPEG image compression framework is designed for the Human-Visual System which is not suitable for the deep neural network, leading to computer vision models' inference performance degradation at lower images' compression quality levels.
 %% \\
 
-Based on these insights, Robert et al.
-\cite{torfason2018towards} tried to train the deep neural network from the compressed representations of an auto-encoder.
-Chao et al.
-\cite{chao2011preserving} proposed using variable quantization which is supported by the JPEG standard extension syntax \cite{dis199110918} to compress the macroblocks in images.
-Furthermore, they \cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance with reduced image size.
-Liu et al.
-\cite{DeepN-JPEG} proposed DeepN-JPEG that redesigns the quantization table by linking statistical information of refined features and defining quantization values so that the compressed image size is reduced for deep learning models.
-Chamain et al.
-\cite{2019quannet} proposed a joint optimization of image classification network coupled with the image quantization, achieving image size reduction of JPGE2000 \cite{rabbani2002jpeg2000} encoded images.
-Recently, Lionel et al.
-\cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform (DCT) coefficients in the middle of the JPEG codec.
+Based on these insights, Robert et al.~\cite{torfason2018towards} tried to train the deep neural network from the compressed representations of an auto-encoder.
+Chao et al.~\cite{chao2011preserving} proposed using variable quantization which is supported by the JPEG standard extension syntax~\cite{dis199110918} to compress the macroblocks in images.
+Furthermore, they~\cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance with reduced image size.
+Liu et al.~\cite{DeepN-JPEG} proposed DeepN-JPEG that re-designs the quantization table by linking statistical information of defined features and defined quantization values so that the compressed image size is reduced for deep learning models.
+Chamain et al.~\cite{2019quannet} proposed a joint optimization of image classification network coupled with the image quantization, achieving image size reduction of JPGE2000~\cite{rabbani2002jpeg2000} encoded images.
+Recently, Lionel et al.~\cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform (DCT) coefficients in the middle of the JPEG codec.
 Baluja et al.~\cite{baluja2019task} proposed task-specific compression that compresses images based on the end-use of images.
@@
 
-However, such proposals all need one to understand the characteristics of the cloud-end deep learning model and have access to the original training dataset, to generate the appropriate color space and/or compression schemes.
-To the best of our knowledge, we are the first to propose an adaptive compression configuration solution named AdaCompress \cite{2019adacompress} that learns the deep learning model by itself.
-We design an agent that adaptively chooses the compression level according to the input image's features and backend deep learning models.
+However, such proposals all need one to understand the characteristics of the cloud-based deep learning model and have access to the original training dataset, to \emph{generate} the appropriate color space and/or compression schemes.
+To the best of our knowledge, we are the first to propose an adaptive compression configuration solution named AdaCompress~\cite{2019adacompress} that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.
 
-In this extension paper, we improve previous mechanism to cut down the uploading file size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly.
-Especially on the DeepN-JPEG comparative experiment, since Liu et al.
-\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on the ImageNet dataset by using four state-of-the-art DNN models (AlexNet \cite{AlexNet-krizhevsky2012imagenet}, VGG \cite{VGG-simonyan2014very}, GoogLeNet \cite{GoogleNet-szegedy2015going} and ResNet \cite{ResNet-he2016deep}) on local terminal devices, which are different from cloud computer vision services.
-For comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using the ImageNet dataset and the metrics in Sec.\ref{subsec:metrics} on three cloud deep learning services (Amazon Rekognition, Face++ and Baidu Vision), the same experiment configuration as the AdaCompress's.
+In this extension paper, we improve previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly.
+Especially on the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local terminal devices, which are different from online computer vision-based services.
+For comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Sec.~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision), the same experiment configuration as AdaCompress's.
 
-%Liu et al. \cite{DeepN-JPEG} developed the DeepN-JPEG framework, a deep %neural network favorable JPEG-based image compression framework.
+%Liu et al.~\cite{DeepN-JPEG} developed the DeepN-JPEG framework, a deep %neural network favorable JPEG-based image compression framework.

### 2020-03-22 paper/sections/conclusion.tex
proofread

--- 2020-03-11 paper/sections/conclusion.tex
@@
 \section{Conclusion}
-\label{sec: conclusion}
+\label{Section: conclusion}
 
-To reduce the upload traffic load of deep learning applications, most researchers focus on modifying the deep learning model, but this does not apply to the industry because the backend deep model is usually inaccessible for users.
-We present a heuristic solution using an reinforcement learning based agent to decide the proper compression quality level for each image, according to the input image and the backend service.
-Our experiments show that for different backend deep learning cloud services and different input image sceneries, using different quality selection strategy can significantly reduce the upload file size overhead while keeping comparable accuracy.
-Moreover, we design the inference-estimation-querying-retraining mechanism to cope with the input image scenery change and make a proper compression selection strategy for the current scenery.
-Our experiment result shows that once the scenery changes, the mechanism would either reload a pre-trained agent model or retrain a new
-agent intelligently to achieve lower upload file size overhead while maintaining the inference accuracy.
+To reduce the upload traffic load of deep learning applications, most researchers focus on modifying the deep learning model, but this does not apply to the industry because the backend deep learning model is usually inaccessible to users.
+We present a heuristic solution using a reinforcement learning agent to decide the proper compression quality level for each image according to the image's features and the backend service.
+Our experiment results show that for different backend deep learning cloud services and different input image ``sceneries'', using different compression strategies can significantly reduce the upload file size overhead while keeping comparable accuracy.
+Moreover, we design the \emph{inference-estimation-querying-retraining} mechanism to cope with the input image scenery change and make a proper compression strategy for the current scenery.
+Our experiment results show that once the scenery changes, the mechanism would either re-load a pre-trained agent or re-train a new agent intelligently to achieve low upload image size overhead while maintaining the inference accuracy.

### 2020-03-22 paper/sections/design.tex
proofread

@@
 \section{Detailed Design}
-\label{sec: design}
+\label{Section: design}
 
@@
 A brief framework of AdaCompress is shown in Figure~\ref{fig: framework}.
-Briefly, it is an reinforcement learning (Rl)-based system to train an agent to choose the proper compression quality level $ c $ for one image to be compressed by JPEG.
-We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, and \emph{inference-estimation-querying-retraining} mechanism separately in the following subsections.
-We provide experimental details of all the hyperparameters in Sec.~\ref{sec: evaluation}.
+Briefly, it is a reinforcement learning-based system to train an agent to choose a proper compression quality level $ c $ for one image to be compressed by JPEG.
+We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, \emph{inference-estimation-querying-retraining} mechanism, and insight of RL agent's behaviors separately in the following subsections.
+We provide experimental details of all the hyperparameters in Section.~\ref{Section: evaluation}.
 %% \\
@@
 % \colorbox{red}{notation table}
-Without loss of generality, we denote the cloud-based deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $, and it has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input image $ x \in X_{\rm ref} $.
-We use this $ \vec{y}_{\rm ref} $ as the ground truth label, and for each image $ x_c $ compressed at compression quality level $ c $, the output $ \vec{y}_c = M(x_c) $.
+Without loss of generality, we denote the cloud-based deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $.
+It has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input image $ x \in X_{\rm ref} $.
+We use this $ \vec{y}_{\rm ref} $ as the ground truth label.
+For each image $ x_c $ compressed at compression quality level $ c $, the output $ \vec{y}_c = M(x_c) $.
 Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $.
@@
 
-Where $ j = 1,...,5 $ indicates the prediction labels at top-5 score, meaning that if anyone of the top-5 predicted labels matches the ground truth label $ \vec{y}_{\rm ref} $, it would be regarded as a correct prediction.
-In general, we cannot get the cloud-based deep learning model's in-layer details (e.g., softmax probabilities) for a cloud-based deep learning service, therefore we use a binary hard label $ d(x, y) \in \{0, 1\} $ to evaluate the accuracy.
+Where $ j = 1,...,5 $ indicates the prediction labels at the top-5 score, meaning that if any one of the top-5 predicted labels matches the ground truth label $ \vec{y}_{\rm ref} $, it would be regarded as a correct prediction.
+In general, we cannot get the cloud-based deep learning model's in-layer details (e.g., softmax probabilities) for a cloud-based deep learning service.
+Therefore we use a binary hard label $ d(x, y) \in \{0, 1\} $ to evaluate the accuracy.
 %% $ d(x, y) \in \{0, 1\} $
@@
 We also denote JPEG input images as $ f_{ic} = J(x_i, c) $ that for an input image $ x_i $ and a given compression quality level $ c $, and it outputs a compressed file $ f_{ic} $ at the size of $ s_{ic} $.
-Especially for a reference compression quality level $ c_{\rm ref} $, the compressed file size is $ s_{\rm ref} $.
-Besides, the input image from a specific location usually belongs to a particular contextual group.
-For example, in daytime scenery, the input images are expected to have a bright background and high contrast while nighttime images are usually gray-scaled thermal images.
-Therefore, the agent in one place and one scenery does not need to know all the contextual features in all places and all ``sceneries''.
+For a reference compression quality level $ c_{\rm ref} $, the compressed file size is $ s_{\rm ref} $.
+Besides, the input image from a specific scenery usually belongs to a particular contextual group~\cite{mcdnn}.
+For example, in the daytime, the input images are expected to have a bright background, while nighttime images are usually gray-scaled thermal images.
+Therefore, the agent in one scenery does not need to know all the contextual features in all ``sceneries''.
 We formulate this as contextual group $ \mathcal{X} $.
-This contextual grouping concept is also discussed in the study~\cite{mcdnn}.
+%This contextual grouping concept is also discussed in~\cite{mcdnn}.
 
-Initially, the agent tries different compression quality levels $ c_{\min} < c < c_{\max}, c \in \mathbb{N} $ to obtain compressed image $ x_c $ from input image $ x $, and an image compressed at a reference level $ c_{\rm ref} $ is also uploaded to the cloud-end to obtain $ \vec{y}_{\rm ref} $.
-Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud-end recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, we can obtain the reference file size $ s_{\rm ref} $ and compressed file size $ s_c $, therefore compute the file compression ratio $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.
+Initially, the agent tries different compression quality levels $ c_{\min} < c < c_{\max}, c \in \mathbb{N} $ to obtain compressed image $ x_c $ from input image $ x $.
+To obtain cloud-end recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent uploads the compressed image $ x_c $ and the reference image $ x_{\rm ref} $ to the cloud-end.
+Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud-end recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent obtains the reference file size $ s_{\rm ref} $ and compressed file size $ s_c $, and computes the file compression ratio $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.
 
@@
 
-The RL agent is expected to give a proper compression quality level $ c $ that minimizing the file size $ s_c $ while keeping the accuracy $ \mathcal{A} $.
-For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $, therefore we can use the Deep Q-learning Network~ as the RL agent.
-But naive the Deep Q-learning Network can't work well in this task because of the following challenges: %% \\
+The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size $ s_c $ while keeping the accuracy $ \mathcal{A} $.
+For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $.
+Therefore we can use the Deep Q-learning Network as the RL agent.
+But the naive Deep Q-learning Network can not work well in this task because of the following challenges: %% \\
 
 \begin{itemize}
-    \item The state space of reinforcement learning is too large, and to preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge.
+	\item The state space of reinforcement learning is too large.
+To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge.
 	\item It takes a long time to train one step in a large inference neural network, making the training process too time-consuming.
-    \item The RL agent starts training from random trials and learns from the reward feedback.
+	\item The RL agent starts training from random trials and learns afterward from the reward feedback.
 When training from a randomly initialized neural network, the reward feedback is very sparse, making it difficult for the agent to learn.
@@
 
-To address these challenges, we use the early layers of a well-trained neural network to extract the structural information of an input image.
+To address these challenges, we use the early layers of a pre-trained neural network to extract the structural information of an input image.
 This is a commonly used strategy in training a deep neural network~\cite{finetunning,finetunning2}.
-Therefore instead of training an RL agent directly from the input image, we use a pre-trained small neural network to extract the features from the input image to reduce the input dimension and accelerate the training procedure.
+Therefore instead of training a RL agent directly from the input image, we use a pre-trained small neural network to extract the features from the input image to reduce the input dimension and accelerate the training procedure.
 In this work, we use the early convolution layers of MobileNetV2~\cite{MobileNetV2} as the image feature extractor $ \mathcal{E}(\cdot) $ for its efficiency in image classification.
 The Deep Q-learning Network $ \phi $ is connected to the feature extractor's last convolution layer.
-We update the RL agent's policy by changing the parameters of the Deep Q-learning Network $ \phi $ while the feature extractor $ \mathcal{E} $ remains fixed.
+We update the RL agent's policy by changing the parameters of the Deep Q-learning Network $ \phi $ while fixing the feature extractor $ \mathcal{E} $.
 %% \\
 
-\subsection{reinforcement learning-based Framework}
+\subsection{Reinforcement Learning-based Framework}
 
-In a specific scenery where the user input image $ x $ belongs context group $ \mathcal{X} $, we define the contextual information $ \mathcal{X} $, along with the backend cloud model $ M $, as the \emph{emulator environment} $ \{\mathcal{X}, M\} $ of the reinforcement learning problem.
+In a specific scenery where the user input image $ x $ belongs to the contextual group $ \mathcal{X} $, we define the contextual group $ \mathcal{X} $, along with the backend cloud model $ M $, as the \emph{emulator environment} $ \{\mathcal{X}, M\} $ of the reinforcement learning problem.
 
-Based on this insight, we formulate the feature extractor's output $ \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}.
+We formulate the feature extractor's output $ \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}.
 In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $.
-We denote the \emph{action-value function} as $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $, and the optimal compression quality level at time $ t $ is $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
-In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where $ s = \mathcal{E}(f_t) $, and $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $ is the target for each iteration.
-Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over sequences $ s $ and compression quality level $ c $~\cite{DQN}.
+We denote the \emph{action-value function} as $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $ and the optimal compression quality level at time $ t $ as $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
+In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where $ s = \mathcal{E}(f_t) $ and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $.
+Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over sequences $ s $ and the compression quality level $ c $~\cite{DQN}.
 When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.
 
-In such a formulation, it is similar to the Deep Q-learning Network problem but not the same.
 Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, i.e., there is no signal from the environment telling that an episode has finished.
 Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $.
-In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction, and decreases the randomness when training.
+In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction and decreases the randomness when training afterward.
 All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
@@
 Finally, the agent's action is based on its historical ``optimal'' experiences.
-The training procedure is presented in Algorithm~\ref{alg: rl-train}, and we list the parameters in Sec.~\ref{sec: evaluation}.
+The training procedure is presented in Algorithm~\ref{alg: rl-train}.
+% and we list the parameters in Section.~\ref{Section: evaluation}.
 
@@
 		\STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
-        \STATE Initialize action-value function $ Q $ with random weights $ \theta $
+		\STATE Initialize \emph{action-value function} $ Q $ with random weights $ \theta $
 		\STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
@@
 		\STATE With probability $ \epsilon $ select a random compression level $ c_t $ otherwise select $ c_t = {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
-        \STATE Compress image $ x_t $ at quality $ c_t $ and upload it to the cloud to get result $ (\vec{y}_{\rm ref}, \vec{y}_c) $ and calculate reward $ r = R(\Delta s, \mathcal{A}_c) $
+		\STATE Compress image $ x_t $ at quality $ c_t $ and upload it to the cloud-end to get result $ (\vec{y}_{\rm ref}, \vec{y}_c) $ and calculate reward $ r = R(\Delta s, \mathcal{A}_c) $
 		\STATE Set $ s_{t+1} = s_t $, generate $ c_t, x_{t+1} $ and preprocess $ \phi_{t+1} = \phi \big(\mathcal{E}(f_{t+1})\big) $
@@
 In our solution, the agent is trained by the reward feedback from the environment $ \{\mathcal{X}, M\} $.
-In the above formulation, we defined compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at compression quality level $ c $.
-Basically, we want the agent to choose a proper compression quality level that minimizing the upload image size while remaining acceptable accuracy, therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $.
+In the above formulation, we define compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at compression quality level $ c $.
+Basically, we want the agent to choose a proper compression quality level for minimizing the upload image size while remaining acceptable accuracy.
+Therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $.
 We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $.
@@
 %% The system diagram is shown in Figure~\ref{fig: diagram}.
-We build up the memory buffer $ \mathcal{D} $ and reinforcement learning (RL) training kernel based on the compression and upload driver.
+We build up the memory buffer $ \mathcal{D} $ and reinforcement learning training kernel based on the compression and upload driver.
 When the RL training kernel is called, it would load transitions from the memory buffer $ \mathcal{D} $ to train the compression quality level predictor $ \phi $.
-When the system is deployed, the pre-trained RL agent $ \phi $ guides the compression driver to compress the input image at an adaptive compression quality level $ c $ according to the input image, then uploads the compressed image to cloud.
+When the system is deployed, the pre-trained RL agent $ \phi $ guides the compression driver to compress the input image at an adaptive compression quality level $ c $, then uploads the compressed image to cloud-end.
 %% \\
 
-After the AdaCompress is deployed, the input image scenery context $ \mathcal{X} $ may change (e.g., day to night, sunny to rainy), when the scenery changes, the older RL agent's compression selection strategy may not be suitable anymore, causing the overall accuracy decreases.
-To cope with the scenery change, we invoke an estimator with a probability $ p_{\rm est} $.
-We do this by generating a random value $ \xi \in (0,1) $ and comparing it to $ p_{\rm est} $.
-If $ \xi \leq p_{\rm est} $, the estimator would be invoked, and AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, therefore calculate $ \mathcal{A}_i $, and save the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ to the memory buffer $ \mathcal{D} $.
+After the AdaCompress is deployed, the input image scenery context $ \mathcal{X} $ may change (e.g., day to night, sunny to rainy).
+When the scenery changes, the older RL agent's compression selection strategy may not be suitable anymore, causing the overall accuracy to decrease.
+To cope with the scenery change, AdaCompress invokes an estimator with a probability $ p_{\rm est} $.
+AdaCompress does this by generating a random value $ \xi \in (0,1) $ and comparing it to $ p_{\rm est} $.
+If $ \xi \leq p_{\rm est} $, the estimator would be invoked.
+AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, calculate $ \mathcal{A}_i $ and save the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ to the memory buffer $ \mathcal{D} $.
 The estimator also compares the recent $ n $ steps' average accuracy $ \bar{\mathcal{A}}_n $ and the initial accuracy threshold $ \mathcal{A}_0 $.
-Once the recent average accuracy is lower than the initial accuracy threshold, the estimator would query an RL agent model to replace the current agent model and test the performance of the loaded model.
+Once the recent average accuracy is lower than the initial accuracy threshold, the estimator would query a RL agent model to replace the current agent model and test the performance of the loaded model.
 To test the loaded model's performance, the estimator computes the average accuracy $ \bar{\mathcal{A}}^*_n $.
 If $ \bar{\mathcal{A}}^*_n $ is still lower than the accuracy threshold, the estimator would invoke the RL training kernel to re-train the agent.
-Once the estimator discovers that the trained reward is higher than the reward threshold, it would stop the training kernel, cache the trained RL agent and switch back to the normal inference state.
+Once the estimator discovers that the trained reward is higher than the reward threshold, it would stop the training kernel, cache the trained RL agent, and switch to the normal inference state.
 
@@
 To avoid unnecessary upload traffic load in the re-training phase, we build up the model caching library to cache the trained RL agent models.
-When capturing the scenery change, we query a pre-trained model from the model caching library rather than re-training from scratch.
+When capturing the scenery change, we firstly query a pre-trained model from the model caching library rather than re-training from scratch.
 %% \\
 
-AdaCompress adaptively switch itself between four states. The switching policy is shown as Figure~\ref{fig: state-switching}.
+The \emph{inference-estimation-querying-retraining} mechanism has four states, including inference, estimation, model querying and re-training.
+AdaCompress switches to these states adaptively.
+The state switching policy is shown as Figure~\ref{fig: state-switching}.
 %\begin{figure}[H]
@@
 %\end{figure}
-\begin{figure}[H]
+\begin{figure}[htbp]
 	\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.1cm, semithick]
@@
 
-\subsubsection{\textbf{Inference}}
+%\subsubsection{\textbf{Inference}}
+\subsubsection{Inference}
 
-For most times, AdaCompress runs in this state.
-In this state, only the compressed images are uploaded to the cloud to achieve minimum upload image size overhead.
-To keep a stable accuracy performance even the input image scenery changes, the agent would occasionally switch to the estimation state with the probability of $ p_{\rm est} $, meanwhile remain the inference state with the probability of $ 1 - p_{\rm est} $.
+Most of the time, AdaCompress runs in this state.
+In this state, only the compressed images are uploaded to the cloud-end to achieve less upload image size overhead.
+To keep a stable accuracy performance even the input image scenery changes, the agent would occasionally switch to the estimation state with probability $ p_{\rm est} $ since the estimator uploads the reference image to maintain inference accuracy, or remain in the inference state with probability $ 1 - p_{\rm est} $.
 %% \\
 
-\subsubsection{\textbf{Estimation}}
+%\subsubsection{\textbf{Estimation}}
+\subsubsection{Estimation}
 
-In this state, the reference image $ x_{\rm ref} $ and compressed image $ x_i $ are uploaded to the cloud simultaneously to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $ which are used to calculate $ \mathcal{A}_i $.
-In each epoch $ i $ the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ is logged in a memory buffer $ \mathcal{D} $.
-When the average accuracy $ \bar{\mathcal{A}}_n $ of the latest $ n $ steps is higher than the accuracy threshold $ \mathcal{A}_0 $, it stays in the estimation state with the probability of $ p_{\rm est} $ or switches back into the inference state with the probability of $ 1 - p_{\rm est} $.
-Once the average accuracy $ \bar{\mathcal{A}}_n $ is lower than the initial accuracy threshold $ \mathcal{A}_0 $, indicating that the current agent is no more suitable for the current input image scenery, AdaCompress would turn into the model querying state and loads a new RL agent model from the model caching library.
+In this state, the reference image $ x_{\rm ref} $ and compressed image $ x_i $ are uploaded to the cloud-end simultaneously to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $ which are used to calculate $ \mathcal{A}_i $.
+In each epoch $ i $, the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ is logged in the memory buffer $ \mathcal{D} $.
+When the average accuracy $ \bar{\mathcal{A}}_n $ of the latest $ n $ steps is higher than the accuracy threshold $ \mathcal{A}_0 $, the agent would stay in the estimation state with probability $ p_{\rm est} $ or switch to the inference state with probability $ 1 - p_{\rm est} $.
+Once the average accuracy $ \bar{\mathcal{A}}_n $ is lower than the initial accuracy threshold $ \mathcal{A}_0 $, indicating that the current agent is no more suitable for the current input image scenery, AdaCompress would turn into the model querying state and re-load a new RL agent model from the model caching library.
 %% \\
@@
 Therefore, the estimation probability of $ p_{\rm est} $ is vital to the whole system.
-On the one hand, the estimator should be invoked occasionally to estimate current agent's accuracy, so that to capture the scenery change on time; on the other hand, the estimator uploads the reference image $ x_{\rm ref} $ along with the compressed image, therefore the upload image size overhead is greater than the conventional benchmark solution, causing higher upload traffic load.
+On the one hand, the estimator should be invoked occasionally to estimate the current agent's accuracy for capturing the scenery change on time.
+On the other hand, the estimator uploads the reference image along with the compressed image.
+Therefore, the upload image size overhead is greater than the conventional benchmark solution, causing a high upload traffic load.
 %% \\
 
-To achieve trade-off between the risk of the scenery change and the objective of reducing upload traffic load, we design an accuracy-aware dynamic $ p_{\rm est} $ solution.
-We first define that after running for $ N $ steps, the recent $ n $ steps' average accuracy is:
+To achieve trade-off between the risk of the scenery change and the objective of reducing upload traffic load, we design an accuracy-aware dynamic solution.
+We first define that after running for $ N $ steps, the average accuracy of recent $ n $ steps is:
 
@@
 With this definition, an intuitive formulation of the change of $ p_{\rm est} $ is in inverse proportion of the gradient of $ \mathcal{A} $, meaning that when the recent accuracy decreases, the estimation probability $ p_{\rm est} $ would increase.
-We formulate that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a scaling factor.
-With this recursive formula, we have the general term of $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $, with an initial estimation probability $ p_0 $.
+We define that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a scaling factor.
+With this recursive formula, we have the general term of $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $ where $ p_0 $ is an initial estimation probability.
 
-\subsubsection{\textbf{Model Querying}}
+%\subsubsection{\textbf{Model Querying}}
+\subsubsection{Model Querying}
 
 The model querying state is designed to cope with the scenery change before re-training.
-It loads a new RL agent model from the model caching library and tests whether the loaded agent model is suitable for the current scenery by re-calculating the average accuracy.
-If the new average accuracy $ \bar{\mathcal{A}}^*_n $ is higher than the accuracy threshold $ \mathcal{A}_0 $, indicating that the loaded agent model is suitable for the current scenery, AdaCompress would switch back to the normal inference state using the loaded agent model.
-Otherwise, AdaCompress would switch into the re-training state and invokes the RL training kernel to re-train a new RL agent for the current scenery.
+It re-loads a new RL agent model from the model caching library and tests whether the loaded agent model is suitable for the current scenery by re-calculating the average accuracy.
+If the new average accuracy $ \bar{\mathcal{A}}^*_n $ is higher than the accuracy threshold $ \mathcal{A}_0 $, indicating that the loaded agent model is suitable for the current scenery, AdaCompress would switch to the normal inference state and use the loaded agent model to infer.
+Otherwise, AdaCompress would switch to the re-training state and invoke the RL training kernel to re-train a new RL agent for the current scenery.
 
-In this way, AdaCompress is capable to cope with the scenery change in a cached ``memory'' manner, avoiding re-training the agent model at every scenery change, therefore cutting down the upload image size overhead.
-However, the agent caching strategy would cause a little storage overhead on local terminal devices.
+In this way, AdaCompress is capable to cope with the scenery change in a cached ``memory'' manner, avoiding re-training the agent model at every scenery change to cut down the upload image size overhead.
+However, the agent caching strategy would cause a little storage overhead on local edge devices.
 
-\subsubsection{\textbf{re-training}}
+%\subsubsection{\textbf{Re-training}}
+\subsubsection{Re-training}
 
@@
 
-\subsection{Insight of RL Agent's Behavior}
+\subsection{Insight of RL Agent's Behaviors}
 \label{subsec:insight}
 
-In the inference phase, the pre-trained RL agent chooses a proper compression quality level according to the input image's feature.
-The reference image is not uploaded to the cloud anymore; only the compressed image is uploaded, therefore, the upload traffic load is reduced.
-We notice that the RL agent's behaviors are various for different input image ``sceneries'' and backend cloud services, therefore we try to make further investigations by plotting the RL agent's "attention map" (i.e., visual explanations of why the agent chooses a compression quality level).
+In the inference phase, the pre-trained RL agent chooses a proper compression quality level according to the input image's features and the backend service.
+The reference image is not uploaded to the cloud-end anymore; only the compressed image is uploaded.
+Therefore, the upload traffic load is reduced.
+We notice that the RL agent's behaviors are various for different input image ``sceneries'' and backend cloud services.
+Therefore we try to make further investigations by plotting the RL agent's ``attention map'' (i.e., visual explanations why the agent chooses a specific compression quality level).
 %% \\
 
-\subsubsection{\textbf{Compression Level Choice Variation}}
+%\subsubsection{\textbf{Compression Level Choice Variation}}
+\subsubsection{Compression Quality Level Choice Variation}
 
-In our experiment, we find that in different cloud application environments, the agent's chosen compression quality levels can be quite different.
-As shown in Figure~\ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's choices are distributed more evenly.
-Therefore, the ``optimal'' compression strategy should be different for different backend cloud services.
+In our experiment, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different.
+As shown in Figure~\ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's selections are distributed more evenly.
+The ``optimal'' compression strategies are different for different backend cloud services.
 This variation is caused by the interaction between the agent and the backend cloud model in the training phase.
@@
 
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\includegraphics[width=\linewidth]{figures/quality_chosen.pdf}
@@
 We randomly sample images from ImageNet~\cite{ImageNet} whose images are mostly taken in the daytime, to act as a daytime scenery, and randomly select nighttime images from the FLIR Thermal Dataset~\cite{FLIR} to form another dataset to act as a nighttime scenery.
-The histogram shown in Figure~\ref{fig: dataset_change} points out that, for the ImageNet images, the agent prefers a lower compression quality level, but its choices are distributed more evenly.
-For the FLIR Thermal images, the agent's choices are more accumulated in some relatively high compression quality levels.
-We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection changes as well.
+The histogram shown in Figure~\ref{fig: dataset_change} points out that, for the ImageNet images, the agent prefers a low compression quality level, but its choices are distributed more evenly.
+For the FLIR Thermal images, the agent's choices are more accumulated in some relatively higher compression quality levels.
+We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection would change as well.
 This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features.
@@
 
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\includegraphics[width=\linewidth]{figures/dataset_change.pdf}
@@
 
-\subsubsection{\textbf{Attention Map Variation}}
+%\subsubsection{\textbf{Attention Map Variation}}
+\subsubsection{Attention Map Variation}
 \label{subsec: attention map}
 
-To take insight investigations, we plot the importance map of a chosen compression quality level.
+To make insight investigations, we plot the importance map of a chosen compression quality level.
 We leverage a conventional visualization algorithm, Grad-Cam, to observe the Deep Q-Learning Network-based agent's interest when choosing compression quality levels.
-Grad-Cam is a widely used solution to present the importance map of a deep neural network, it is done by calculating the gradients of each target concept and backtracking to the final convolution layer.
+Grad-Cam is a widely used effective solution to present the importance map of a deep neural network by calculating the gradients of each target concept and backtracking to the final convolution layer.
 In this work, we plot the RL agent's attention map by Grad-Cam in Figure~\ref{fig: attention}.
@@
 
-In our investigations, we find that in different environments $ \{\mathcal{X}, M\} $, the RL agent picks up compression quality level based on the visual textures of different regions in the image.
-As shown in Figure~\ref{fig: attention}, picture 1a -- 1d are some pictures which the agent chooses to compress highly, the agent selects lower compression quality levels based on the complex texture of the images.
-On the contrary, for pictures 2a -- 2d, the agent chooses higher compression quality levels to preserve more details since its interest falls on some smooth regions.
-Especially for 1a and 2a, in picture 1a, the agent chooses a lower quality compression level based on the rough central region though there are smooth regions around it, but in picture 2a, the agent chooses a relatively higher compression quality level based on the surrounding smooth region rather than the central region.
+In our investigations, we find that in different environments $ \{\mathcal{X}, M\} $, the RL agent selects compression quality levels based on the visual textures of different regions in the image.
+As shown in Figure~\ref{fig: attention}, picture 1a -- 1d are some pictures which the agent chooses to compress aggressively.
+The agent selects low compression quality levels based on the complex texture of the images.
+On the contrary, for pictures 2a -- 2d, the agent chooses relatively higher compression quality levels to preserve more details since its interest falls on some smooth regions.
+Especially for 1a and 2a, for picture 1a, the agent chooses a low compression quality level based on the rough central region though there are smooth regions around it, for picture 2a, the agent chooses a relatively higher compression quality level based on the surrounding smooth region rather than the central region.
 %% \\

### 2020-03-22 paper/sections/evaluation.tex
proofread

@@
 \section{Evaluation}
-\label{sec: evaluation}
+\label{Section: evaluation}
 
-In this section, we present AdaCompress's behavior and effectiveness by some real-world experiments. %% \\
+In this section, we present AdaCompress's behaviors and effectiveness by some real-world experiments. %% \\
 
@@
 We use a desktop PC with an NVIDIA 1080ti graphic card as the edge infrastructure.
-For the cloud deep learning services, we choose Baidu Vision, Face++ object detection services, and Amazon Rekognition.
-In the experiments, we use two datasets mentioned before in Sec.~\ref{subsec:insight}, ImageNet dataset indicating daytime scenery and the FLIR Thermal Dataset indicating nighttime scenery.
+For the cloud-based deep learning services, we choose Baidu Vision, Face++ object detection services and Amazon Rekognition.
+In the experiments, we use two datasets mentioned before in Subsection.~\ref{subsec:insight}.
+The ImageNet dataset indicates daytime scenery, and the FLIR Thermal Dataset indicates nighttime scenery.
 Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.
 
-\begin{table}[H]
+\begin{table}[htbp]
 	\centering
@@
 	\end{tabular}
-    \caption{Experiment parameter settings}
+	\caption{Experiment parameter}
 	\label{tab: parameters}
-    %     \vspace{-0.3cm}
+	\vspace{-0.5cm}
 \end{table}
@@
 We use two datasets, the ImageNet dataset and the FLIR Thermal Dataset.
-The Imagenet dataset is a Large-Scale Hierarchical Image, in which each node of the hierarchy is depicted by hundreds and thousands of images.
-Its images are mostly taken in the daytime, and therefore we use it as a daytime scenery.
-Usually, a surveillance camera captures colored images in the daytime and gray-scaled thermal images in the nighttime.
+The ImageNet dataset is a Large-Scale Hierarchical Image, in which each node of the hierarchy is depicted by hundreds and thousands of images.
+Its images are mostly taken in the daytime.
+Therefore we use it as a daytime scenery.
+Usually, a surveillance camera captures colored pictures in the daytime and gray-scaled thermal images in the night.
 Therefore we choose a thermal image dataset to act as a nighttime image dataset.
@@
 
-We use the ImageNet dataset in size reduction and accuracy performance experiment, DeepN-JPEG comparative experiment, and end-to-end latency simulation.
-Moreover, we use ImageNet and the FLIR Thermal Dataset alternately to simulate the scenery change in the \emph{inference-estimation-querying-retraining} mechanism experiment, and analyze the RL agent's best compression strategy selection in different input image ``sceneries''.
+We use the ImageNet dataset in size reduction and accuracy performance experiment, DeepN-JPEG comparative experiment and end-to-end latency simulation experiment.
+Moreover, we use ImageNet and the FLIR Thermal Dataset alternately to simulate the scenery change in the \emph{inference-estimation-querying-retraining} mechanism experiment.
 
@@
 
-The default compression quality level for JPEG is usually 75~\cite{pillow_benchmark,imgmin}, therefore we regard this as a typical value $ c_{\rm ref} = 75 $ of the conventional benchmark. %% \\
+The default compression quality level for JPEG is usually 75~\cite{pillow_benchmark,imgmin}. Therefore we regard this as a reference value $ c_{\rm ref} = 75 $ of the conventional benchmark. %% \\
 
-In our experiments, we measure the compressed and original image's file size to obtain the compression rate $ \Delta s $.
-Since we don't have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric, the formula of $ \mathcal{A} $ is presented in Sec.~\ref{subsec: formulation}.
+In our experiments, we measure the compressed and reference image's file size to obtain the compression rate $ \Delta s $.
+Since we do not have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric.
+The formula of $ \mathcal{A} $ is presented in Subsection.~\ref{subsec: formulation}.
 
@@
 	\includegraphics[width=\linewidth]{figures/train_steps_new.pdf}
-    \caption{Size overhead in training and inference phase}
+	\caption{Size overhead in the training and inference phase}
 	\label{fig: train_steps}
@@
 
-Figure~\ref{fig: train_steps} presents the upload traffic load of the training and inference phase, to be more intuitionistic, we plot the size overhead $ \frac{s}{s_{\rm ref}} $ as the $ y $-axis where $ s $ is the real upload size of AdaCompress, $ s_{\rm ref} $ is the benchmark upload size.
+Figure~\ref{fig: train_steps} presents the upload traffic load of the training and inference phase.
+To be more intuitionistic, we plot the size overhead $ \frac{s}{s_{\rm ref}} $ as the $ y $-axis where $ s $ is the real upload size of AdaCompress and $ s_{\rm ref} $ is the benchmark upload size.
 Therefore $ y \geq 1 $ means that our solution uploads more data then benchmark, and $ y < 1 $ means the compression rate of AdaCompress.
-From Figure~\ref{fig: train_steps} we can see that as the training procedure runs, the upload image size decreases because the RL agent learns to choose better compression quality levels to upload fewer data.
-In the training phase, to train the agent while remaining a convincing recognition result, we have to upload the original image to the cloud to get the real result, along with the compressed image to obtain reward feedback, therefore the upload traffic load is even higher than the conventional solution.
+From Figure~\ref{fig: train_steps}, we can see that as the training procedure runs, the upload image size decreases because the RL agent learns to choose better compression quality levels to upload less data.
+In the training phase, to train the agent while remaining a convincing recognition result, AdaCompress has to upload the original image along with the compressed image to the cloud-end, obtaining the real result and the reward feedback.
+Therefore the upload traffic load is even higher than the conventional solution.
 But once the training phase has finished, the upload traffic load is lower than the benchmark.
@@
 Figure~\ref{fig: compress_performance} presents the compression performance in the inference phase for each cloud service.
-We test AdaCompress on Face++, Baidu Vision and Amazon Rekognition, comparing to the conventional compression level, for all tested cloud services, our solution can reduce the upload size by more than 1/2, meanwhile, the relative accuracy, indicated by brown bars, only decreases about 7\% on average, proving the efficiency of our design.
+We test AdaCompress on Face++, Baidu Vision and Amazon Rekognition.
+Comparing to the benchmark compression quality level, our solution can reduce the upload size by more than 1/2 for all tested cloud services, meanwhile maintain the relative accuracy that only decreases about 7\% on average, proving the efficiency of our design.
 %% \\
@@
 
+Figure~\ref{fig: compare_DeepN} presents a comparison performance between DeepN-JPEG and AdaCompress for each cloud service.
+As we can see, both DeepN-JPEG and AdaCompress cut down the upload size overhead more than 1/2.
+However, for all tested cloud services, AdaCompress's accuracy is higher than DeepN-JPEG's slightly.
+Compared with DeepN-JPEG's average accuracy is about 85\% on three cloud services, AdaCompress achieves a better average accuracy of 93\%.
+In a word, comparing to the DeepN-JPEG framework, AdaCompress presents a similar size reduction performance but achieving higher inference accuracy for online computer vision-based services.
+
 \begin{figure*}[htbp]
@@
 		\centerline{(1a) Origin Image (Q=75)}
-        \centerline{Baidu prediction \ = \ ["parrot"]}
+		\centerline{Baidu prediction \ = \ [``parrot'']}
 	\end{minipage}
@@
 		\centerline{(1b) AdaCompress (choose Q=15)}
-        \centerline{Baidu prediction \ = \ ["parrot"]}
+		\centerline{Baidu prediction \ = \ [``parrot'']}
 	\end{minipage}
@@
 		\centerline{(1c) DeepN-JPEG}
-        \centerline{Baidu prediction \ = \ ["parrot"]}
+		\centerline{Baidu prediction \ = \ [``parrot'']}
 	\end{minipage}
@@
 		\centerline{(2a) Origin Image (Q=75)}
-        \centerline{Baidu prediction \ = \ ["cake"]}
+		\centerline{Baidu prediction \ = \ [``cake'']}
 	\end{minipage}
@@
 		\centerline{(2b) AdaCompress (choose Q=65)}
-        \centerline{Baidu prediction \ = \ ["cake"]}
+		\centerline{Baidu prediction \ = \ [``cake'']}
 	\end{minipage}
@@
 		\centerline{(2c) DeepN-JPEG}
-        \centerline{Baidu prediction \ = \ ["fossil"]}
+		\centerline{Baidu prediction \ = \ [``fossil'']}
 	\end{minipage}
-    \vspace{0.2cm}
+	%	\vspace{0.2cm}
 	\caption{Comparative compressed images of DeepN-JPEG and AdaCompress}
@@
 
-Figure~\ref{fig: compare_DeepN} presents a comparison performance between DeepN-JPEG and AdaCompress for each cloud service.
-As we can see, both DeepN-JPEG and AdaCompress cut down the upload size overhead more than 1/2.
-However, for all tested cloud services, AdaCompress's accuracy is higher than DeepN-JPEG's slightly.
-Compared with DeepN-JPEG's average accuracy is about 85\% on three cloud services, while AdaCompress achieves a better average accuracy of 93\%.
-In a word, comparing to the DeepN-JPEG framework, AdaCompress presents a similar upload traffic load reduction performance but achieving higher inference accuracy for online computer vision-based services.
-
 AdaCompress compresses images in a more adaptive manner rather than DeepN-JPEG.
-(i.e., the explanation of why AdaCompress achieves a better accuracy).
-As shown in Figure~\ref{fig: compare_image}, for picture 1a, compared to DeepN-JPEG, AdaCompress compresses the image at the compression quality level of 15, a more aggressive compression quality level to reduce upload size overhead.
-On the contrary, for picture 2a of Figure~\ref{fig: compare_image}, DeepN-JPEG compresses the image with the same quantization table, but AdaComperss chooses a higher compression quality level to preserve more details so that the backend deep learning model can still recognize the picture.
-Being different from the DeepN-JPEG framework compresses all images with the same quantization table, our RL agent chooses a lower compression quality level for picture 1a and a relatively higher compression quality level for picture 2a based on the feature of the input image.
+(i.e., the explanation why AdaCompress achieves a better accuracy).
+As shown in Figure~\ref{fig: compare_image}, for picture 1a, compared to DeepN-JPEG, AdaCompress compresses the image at a more aggressive compression quality level of 15, reducing upload size overhead.
+On the contrary, for picture 2a of Figure~\ref{fig: compare_image}, DeepN-JPEG compresses the image with the same quantization table, but AdaComperss chooses a relatively higher compression quality level to preserve more details so that the backend deep learning model can still recognize the picture.
+Compared with DeepN-JPEG compresses all images with the same quantization table, AdaCompress chooses a low compression quality level for picture 1a and a relatively higher compression quality level for picture 2a based on the features of the input image.
 
@@
 
-Comparing to DeepN-JPEG, AdaCompress has three advantages and one disadvantage as following: %% \\    
+Comparing to DeepN-JPEG, AdaCompress has two advantages and one disadvantage as following: %% \\
+
 \begin{itemize}
+
 \item AdaCompress and DeepN-JPEG both decrease the upload size overhead more than 1/2, but AdaCompress maintains higher inference accuracy.
-        \item DeepN-JPEG requires the original dataset information to re-design the quantization table, while AdaCompress chooses compression quality level adaptively without any pre-knowledge of the original dataset.
-        \item When the scenery changes, DeepN-JPEG still compresses images with the same quantization table, while AdaCompress's \emph{inference-estimation-querying-retraining} mechanism captures the scenery change and invokes either model querying method or retraining kernel to \emph{generate} a more suitable compression selection strategy for the current scenery.
-        \item DeepN-JPEG re-designs the quantization table \emph{locally}, while AdaCompress needs to upload origin images and compressed images to the cloud in the training phase, leading some upload size overhead at the beginning.
+
+%\item DeepN-JPEG requires the original dataset information to re-design the quantization table, while AdaCompress chooses compression quality levels adaptively without any prior knowledge of the original dataset.
+%\item When the scenery changes, DeepN-JPEG still compresses images with the same quantization table, while AdaCompress's \emph{inference-estimation-querying-retraining} mechanism captures the scenery change and make a more suitable compression strategy for the current scenery.
+\item For different ``sceneries'' or cloud services, DeepN-JPEG compresses images with the same quantization table, while AdaCompress makes a more proper compression strategy adaptively.
+
+%\item For different cloud services, DeepN-JPEG compresses images with the same quantization table, while AdaCompress makes a more proper compression strategy adaptively.
+\item DeepN-JPEG re-designs the quantization table \emph{locally}, while AdaCompress needs to upload reference images and compressed images to the cloud-end in the training phase, leading some upload size overhead at the beginning.
 \end{itemize}
@@
 
-To evaluate the efficiency of the \emph{inference-estimation-querying-retraining} mechanism, we feed AdaCompress with a combined dataset whose first 2000 images from FLIR Thermal images, the later 3000 images randomly sampled from ImageNet, and the last 2000 images from FLIR Thermal images.
-We adapt AdaCompress's current RL agent to FLIR Thermal nighttime scenery by training it on the FLIR dataset, and we run AdaCompress on the combined dataset, observing AdaCompress's behavior upon the scenery changes at step 2000 and 5000.
+To evaluate the efficiency of the \emph{inference-estimation-querying-retraining} mechanism, we feed AdaCompress with a combined dataset whose first 2000 images from FLIR Thermal images, the next 3000 images randomly sampled from ImageNet and the last 2000 images from FLIR Thermal images.
+We adapt AdaCompress's current RL agent to FLIR nighttime scenery by training it on the FLIR dataset, and run AdaCompress on the combined dataset, observing AdaCompress's behaviors upon the scenery changes at step 2000 and 5000.
 %% \\
 
-We illustrate AdaCompress's behavior in Figure~\ref{fig: running-retrain}, the $ x $-axis indicates steps, the vertical red line means the dataset change (i.e.
-scenery change).
-We plot AdaCompress's overall accuracy as the green line and the estimation probability $ p_{\rm est} $ as the gray line.
-At the bottom of Figure~\ref{fig: running-retrain}, we also plot the scaled upload size of AdaCompress and benchmark solution to illustrate the upload size overhead in the inference phase.
+We illustrate AdaCompress's behaviors in Figure~\ref{fig: running-retrain}.
+The $ x $-axis indicates steps, and the reference line indicates the scenery change.
+We plot AdaCompress's overall accuracy and the estimation probability $ p_{\rm est} $.
+At the bottom of Figure~\ref{fig: running-retrain}, we also plot the scaled upload size of AdaCompress and benchmark solution to illustrate the upload size overhead.
 %with a $ \Delta $ mark on $ x $-axis
@@
 	\includegraphics[width=\linewidth]{figures/running-retrain.pdf}
-    \caption{AdaCompress's reaction upon scenery change}
+	\caption{AdaCompress's reactions upon scenery change}
 	%    \vspace{-0.2cm}
@@
 
-From Figure~\ref{fig: running-retrain} we can see that AdaCompress can adaptively update the estimation probability $ p_{\rm est} $, usually, when the overall accuracy decreases, AdaCompress would increase the estimation probability, trying to capture the scenery change.
+From Figure~\ref{fig: running-retrain}, we can see that AdaCompress can adaptively update the estimation probability $ p_{\rm est} $.
+When the overall accuracy decreases, AdaCompress would increase the estimation probability, trying to capture the scenery change.
 When the overall accuracy is stable and high enough, the estimation probability $ p_{\rm est} $ decreases to reduce transmission.
@@
 
-Upon the first data scenery changes (i.e., night to day) shown as the first vertical red line in Figure~\ref{fig: running-retrain}, comparing to the earlier steps, the accuracy decreases dramatically and therefore $ p_{\rm est} $ raises to determine whether the scenery changes.
-The accuracy keeps dropping in the following estimations, indicating that the current RL agent is no more suitable for the current input scenery.
-At the moment, AdaCompress should switch into the model querying state and re-load a new RL agent model from the model caching library.
-However, there is no model except the current RL agent in the model caching library at that time.
-Therefore, AdaCompress starts to re-train at once, to adapt the RL agent into the current scenery.
-The re-training steps are shown as the light-blue region in Figure~\ref{fig: running-retrain}.
-In the re-training phase, AdaCompress uses the reference image's prediction label $ \vec{y}_{\rm ref} $ as the output result, therefore the accuracy $ \mathcal{A} $ and $ p_{\rm est} $ are locked to 1.
-After finishing re-training the agent in the daytime scenery, the trained agent is cached in the model cachling library, and in the following iterations, sometimes the accuracy decreases accidentally, and the estimation probability $ p_{\rm est} $ also raises to get more samples.
-The accuracy is not lower than the accuracy threshold $ \mathcal{A}_0 $ , therefore the re-training phase would not be triggered again until the second data scenery changes.
+Upon the first image scenery changes (i.e., night to day) shown as the first reference line in Figure~\ref{fig: running-retrain}, comparing to the earlier steps, the accuracy decreases dramatically and the estimation probability $ p_{\rm est} $ raises to determine whether the scenery changes.
+The accuracy keeps dropping in the following steps, indicating that the current RL agent is no more suitable for the current input scenery.
+At the moment, AdaCompress should switch to the model querying state and re-load a new RL agent model from the model caching library.
+However, there is no model except the current RL agent at that time.
+Therefore, AdaCompress starts to re-train at once to adapt the RL agent to the current scenery.
+In the re-training phase, AdaCompress uses the reference image's prediction label $ \vec{y}_{\rm ref} $ as the output result.
+Therefore the accuracy $ \mathcal{A} $ and $ p_{\rm est} $ are locked to 1.
+After finishing re-training the agent in the daytime scenery, the trained agent is cached in the model caching library.
+In the following steps, sometimes the accuracy decreases accidentally, and the estimation probability $ p_{\rm est} $ also raises.
+The accuracy is not lower than the accuracy threshold $ \mathcal{A}_0 $.
+Therefore the re-training phase would not be triggered again until the second image scenery changes.
 %% \\
 
-Upon the second data scenery changes (i.e., day to night) shown as the second vertical red line in Figure~\ref{fig: running-retrain}, like the first scenery change, the accuracy decreases and $ p_{\rm est} $ raises, indicating that the current RL agent is no more suitable again.
-AdaCompress switches into the model querying state at once and re-loades a new RL agent model (i.e., the initial model trained on the FLIR Thermal images) from the model caching library.
-When using the new agent in this scenery, the accuracy stops decreasing and maintains above the accuracy threshold, indicating the current RL agent is suitable for the current scenery.
+Upon the second image scenery changes (i.e., day to night) shown as the second reference line in Figure~\ref{fig: running-retrain}, like the first scenery change, the accuracy decreases and $ p_{\rm est} $ raises, indicating that the current RL agent is no more suitable again.
+AdaCompress switches to the model querying state at once and re-loads a new RL agent model (the initial model trained on the FLIR Thermal images) from the model caching library.
+When using the new agent in this scenery, the accuracy stops decreasing and maintains more than the accuracy threshold, indicating the current RL agent is suitable for the current scenery.
 %% \\
 
-From Figure~\ref{fig: running-retrain} we can also observe the uploading file size overhead in different phases, in re-training phase, AdaCompress uploads more data than the conventional benchmark, but in inference phase, AdaCompress's upload size is only half of the benchmark's.
-Especially when the second data scenery changes, AdaCompress achieves a lower upload traffic load by loading a suitable RL agent model rather than re-training from scratch.
+From Figure~\ref{fig: running-retrain}, we can also observe the upload size overhead in different phases.
+In the re-training phase, AdaCompress uploads more data than the conventional benchmark.
+But in the inference phase, AdaCompress's upload size is only half of the benchmark's.
+Especially once the second image scenery changes, AdaCompress achieves a low upload traffic load by re-loading a suitable RL agent model rather than re-training from scratch.
 %% \\
@@
 
-Comparing to the conventional solution that uploads the image directly, in our solution, the image is passed to the RL agent first to estimate the compression level.
+Comparing to the conventional solution that uploads the image directly, in our solution, the image is passed to the RL agent firstly to estimate the compression quality level.
 Running this RL agent brings extra latency to the whole system.
-In this subsection, we evaluate this latency overhead.
+In this subsection, we evaluate the overall latency overhead.
 %% \\
 
-We test the RL agent's inference time and compressed file size for batches of images, and simulate the latency of uploading such compressed images.
+We compute compressed file size for batches of images, and test the RL agent's inference time and the latency of uploading such compressed images.
 We test the average inference latency on 1000 ImageNet images and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb.
@@
 
-Our solution brings in inference latency to the end-to-end latency, but the transmission latency is much lower by shrinking the upload file size.
+Our solution brings in inference latency to the end-to-end latency, but the transmission latency is low by reducing the upload file size.
 In today's network architecture where the edge infrastructure's computational power is increasing significantly ~\cite{satyanarayanan2017emergence,hu2015mobile}, we can use the computing power of the edge infrastructure in exchange for the reduction of upload traffic load and transmission latency.

### 2020-03-22 paper/sections/introduction.tex
proofread

@@
 \section{Introduction}
-\label{sec: introduction}
+\label{Section: introduction}
 
 \IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications.
-Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.
+Because of the enormous computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.
 
-To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it.
+To reduce the upload traffic load, one should compress the image before uploading it.
 Though JPEG has been used as the \emph{de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory.
-Liu et al.~\cite{DeepN-JPEG} showed that by re-designing the quantization table in the default JPEG configuration, one can compress an image to a smaller version while maintaining the same inference accuracy for a deep computer vision model.
+Liu et al.~\cite{DeepN-JPEG} showed that by re-designing the quantization table in the default JPEG configuration, one can compress an image to a smaller version while maintaining the comparable inference accuracy for a deep computer vision model.
 However, such quantization solutions usually assume the inference model is fixed.
+%To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it.
 
-We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different online computer vision-based services, without any prior knowledge of the original model and input images?
+We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different online computer vision-based services, without any prior knowledge of the original model?
 In this paper, we propose a reinforcement learning-based framework to select JPEG configurations adaptively.
 In our solution, we tackle the following design challenges.
+% and input images
 
@@
 \item \emph{Lack of information about the cloud-based computer vision models.} Previous studies~\cite{DeepN-JPEG, torfason2018towards, gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging the original computer vision model into it.
-However, the structure details of online computer vision models are usually proprietary and not open to the users.
+However, the structural details of online computer vision models are usually proprietary and not open to the users.
 
@@
 However, today's cloud-based computer vision algorithms, based on deep and convolutional computations, are quite hard to understand.
-The same compression quality level could lead to a totally different accuracy performance.
+The same compression quality level could lead to a different accuracy performance.
 Some examples are shown in Figure~\ref{fig: compress_accuracy}: picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning model gives different inference results, only because they are compressed at different quality levels.
@@
 
-\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which image should be compressed to which quality level, as in conventional supervised deep learning tasks.
+\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which image should be compressed at which quality level, as in conventional supervised deep learning tasks.
 In practice, such an image compression module is usually utilized in an online manner, and the solution has to learn from the images it uploads automatically.
@@
 %		\centerline{Face++ prediction=["donut"]}
-		\centerline{Face++ prediction \ = \ ["donut"]}
+		\centerline{Face++ prediction \ = \ [``donut'']}
 		\vspace{0.4cm}
@@
 %		\centerline{Face++ prediction=[]}
-		\centerline{Face++ prediction \ = \ ["biscuit"]}
+		\centerline{Face++ prediction \ = \ [``biscuit'']}
 		\vspace{0.4cm}
@@
 % 		\centerline{\quad Baidu prediction=["chameleon"]}
-		\centerline{Baidu prediction \ = \ ["chameleon"]}
+		\centerline{Baidu prediction \ = \ [``chameleon'']}
 		\vspace{0.4cm}
@@
 % 		\centerline{\qquad Baidu prediction=["electric fan"]}
- 		\centerline{Baidu prediction \ = \ ["electric fan"]}
+ 		\centerline{Baidu prediction \ = \ [``electric fan'']}
  		\vspace{0.4cm}
@@
 %		\centerline{Baidu prediction=["leopard"]}
-		\centerline{Baidu prediction \ = \ ["leopard"]}
+		\centerline{Baidu prediction \ = \ [``leopard'']}
 		\vspace{0.3cm}
@@
 	\caption{The prediction of a deep learning model is not completely related to the input image's quality, making it difficult to use a fixed compression quality for all images.
-For image 1a, 1b and 2a, 2b, minor changes cause different predictions though they are visually similar; for image 3a and 3b, the cloud model still output correct label from a severely compressed image though they look very different}
+For image 1a, 1b and 2a, 2b, minor changes cause different predictions though they are visually similar; for image 3a and 3b, the cloud-based model still output correct label from a severely compressed image though they look very different}
 	\label{fig: compress_accuracy}
@@
 
-To address the above challenges, we present a reinforcement learning-based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision-based APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner.
+To address the above challenges, we present a reinforcement learning-based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision-based APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose a proper compression quality level for an image to a computer vision model on the cloud-end, in an online manner.
 This paper is an extension of our earlier conference paper~\cite{2019adacompress}, with the following contributions:
@@
 The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size.
-Based on~\cite{2019adacompress}, we further propose an \emph{explore-exploit} mechanism to let the agent switch between ``sceneries''.
-In particular, after deploying the agent, an \emph{inference-estimate-retrain} solution is designed to restart the training once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.
+We further propose an \emph{explore-exploit} mechanism to let the agent switch between ``sceneries''.
+In particular, after deploying the agent, an \emph{inference-estimation-querying-retraining} solution is designed to switch the RL agent intelligently once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.
+%re-load or re-train a RL agent intelligently
+%restart the training
+%Based on~\cite{2019adacompress},
 
 $\rhd$~~In this journal extension, we provide more analysis and insights on our design.
-By analyzing the Deep Q-learning Network-based agent's behaviors using Grad-Cam~\cite{grad-cam}, we provide the reasons that the agent chooses a specific compression quality level.
+We notice that the Deep Q-learning Network-based agent's behaviors are various for different input image “sceneries” and backend cloud services.
+By analyzing the agent's behaviors using Grad-Cam~\cite{grad-cam}, we provide the reasons that the agent chooses a specific compression quality level.
 We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.
 
-$\rhd$ We evaluate our system on representative cloud deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy.
+$\rhd$ We evaluate our system on representative cloud-based deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}.
+We show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy.
 Compared to baseline DeepN-JPEG~\cite{DeepN-JPEG}, the overall accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.
@@
 The rest of this paper is organized as follows.
-We discuss related works in Sec.~\ref{sec: related_works}.
-In Sec.~\ref{sec: design} we present our framework and detailed design.
-We present our solution's performance in Sec.~\ref{sec: evaluation} and conclude the paper in Sec.~\ref{sec: conclusion}.
+We discuss related works in Section.~\ref{Section: related_works}.
+We present our framework and detailed design in Section.~\ref{Section: design}.
+We present our solution's performance in Section.~\ref{Section: evaluation} and conclude the paper in Section.~\ref{Section: conclusion}.
 

### 2020-03-22 paper/sections/relatedwork.tex
proofread

@@
 \section{Related Works}
-\label{sec: related_works}
+\label{Section: related_works}
 
@@
 Other studies proposed to run a part of a deep learning model \emph{locally}~\cite{ILP_Decoupling, jalad, Edge_LBP, Neurosurgeon}, by decoupling the deep learning model into different parts, e.g., based on the layers in the deep learning model, so that a part of the inference is done \emph{locally} to save some execution time.
-However, these solutions usually need to \emph{re-train} the model, using the original dataset of the model, which is not practical for today's online computer vision-based services that are merely a black box to end-users, e.g., in the form of a RESTful API.
+However, these solutions usually need to re-train the model using the original dataset of the model, which is not practical for today's online computer vision-based services that are merely a black box to end-users, e.g., in the form of a RESTful API.
 
@@
 
-Data compression solutions study how to compress the original data (e.g., a video or image) to be inferred by the cloud-based deep learning model, so that less traffic is used to upload the data to improve inference speed.
-Conventional data compression solutions (e.g., JPEG~\cite{jpeg}, WebP~\cite{calore2010meet} and JPEG2000~\cite{rabbani2002jpeg2000}, etc.) and some recent neural network-based compression solutions~\cite{toderici2017full, theis2017lossy, toderici2015variable, rippel2017real} are initially designed for the Human-Visual System.
-In recent years, researchers found that the human visually optimized-based data compression solutions are not usually applicable to deep learning vision models.
-Delac et al.~\cite{delac2005effects} observed that, in some cases, a higher compression quality level does not always deteriorates the model inference performance, even improves it slightly.
+Data compression solutions study how to compress the original data (e.g., a video or image) to be inferred by the cloud-based deep learning model so that less traffic is used to upload the data to improve inference speed.
+In recent years, researchers found that conventional human visually optimized-based data compression solutions (e.g., JPEG~\cite{jpeg}, WebP~\cite{calore2010meet} and JPEG2000~\cite{rabbani2002jpeg2000}, etc.) and some recent neural network-based compression solutions~\cite{toderici2017full, theis2017lossy, toderici2015variable, rippel2017real} are not usually applicable to deep learning vision models.
+Liu et al.~\cite{DeepN-JPEG} revealed that the conventional JPEG image compression framework is designed for the Human-Visual System, which is not suitable for the deep neural network, leading to the computer vision model's inference performance degradation.
 Dodge et al.~\cite{dodge2016understanding} further discovered that besides the JPEG compression, four types of quality distortions (blur, noise, contrast, and the JPEG2000 compression~\cite{rabbani2002jpeg2000}) can also affect the inference performance of the deep learning models.
-Liu et al.~\cite{DeepN-JPEG} proposed that the conventional JPEG image compression framework is designed for the Human-Visual System which is not suitable for the deep neural network, leading to computer vision models' inference performance degradation at lower images' compression quality levels.
+Delac et al.~\cite{delac2005effects} observed that, in some cases, a high compression quality level does not always reduce the model inference accuracy.
 %% \\
@@
 Based on these insights, Robert et al.~\cite{torfason2018towards} tried to train the deep neural network from the compressed representations of an auto-encoder.
-Chao et al.~\cite{chao2011preserving} proposed using variable quantization which is supported by the JPEG standard extension syntax~\cite{dis199110918} to compress the macroblocks in images.
-Furthermore, they~\cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance with reduced image size.
+Chao et al.~\cite{chao2011preserving} proposed using variable quantization, which is supported by the JPEG standard extension syntax~\cite{dis199110918} to compress the macroblocks in images.
+Furthermore, they~\cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance while reducing the image size overhead effectively.
 Liu et al.~\cite{DeepN-JPEG} proposed DeepN-JPEG that re-designs the quantization table by linking statistical information of defined features and defined quantization values so that the compressed image size is reduced for deep learning models.
 Chamain et al.~\cite{2019quannet} proposed a joint optimization of image classification network coupled with the image quantization, achieving image size reduction of JPGE2000~\cite{rabbani2002jpeg2000} encoded images.
-Recently, Lionel et al.~\cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform (DCT) coefficients in the middle of the JPEG codec.
+Recently, Lionel et al.~\cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform coefficients in the middle of the JPEG codec.
 Baluja et al.~\cite{baluja2019task} proposed task-specific compression that compresses images based on the end-use of images.
@@
 
-However, such proposals all need one to understand the characteristics of the cloud-based deep learning model and have access to the original training dataset, to \emph{generate} the appropriate color space and/or compression schemes.
-To the best of our knowledge, we are the first to propose an adaptive compression configuration solution named AdaCompress~\cite{2019adacompress} that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.
+However, such proposals all need one to understand the characteristics of the cloud-based deep learning model and have access to the original training dataset,  \emph{generating} the appropriate compression schemes.
+To the best of our knowledge, we are the first to propose an adaptive compression configuration solution that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.
 
-In this extension paper, we improve previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly.
-Especially on the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local terminal devices, which are different from online computer vision-based services.
-For comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Sec.~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision), the same experiment configuration as AdaCompress's.
+In this journal extension, we improve the previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly.
+Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection.~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).
 

### 2020-03-26 paper/sections/design.tex
minor

@@
 
-\begin{figure*}
+\begin{figure*}[!t]
 	%\begin{tabular}{cc}
@@
 
-\begin{algorithm}[htbp]
+\begin{algorithm}[!t]
 	\caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
@@
 		\STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
-		\FOR {t = 1, $ K $}
-		\STATE With probability $ \epsilon $ select a random compression level $ c_t $ otherwise select $ c_t = {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
-		\STATE Compress image $ x_t $ at quality $ c_t $ and upload it to the cloud-end to get result $ (\vec{y}_{\rm ref}, \vec{y}_c) $ and calculate reward $ r = R(\Delta s, \mathcal{A}_c) $
-		\STATE Set $ s_{t+1} = s_t $, generate $ c_t, x_{t+1} $ and preprocess $ \phi_{t+1} = \phi \big(\mathcal{E}(f_{t+1})\big) $
-		\STATE Store transition $ (\phi_t, c_t, r_t, \phi_{t+1}) $ in $ \mathcal{D} $
-		\IF {$ t \mod T == 0 $ and $ t \geq T_{\rm start} $}
-		\STATE Sample randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
-		\STATE Set $ y_i = r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
+		\FOR {$t \in 1,2,\cdots, K$}
+		\STATE \textbf{1) Exploration.} With probability $\epsilon$:
+		\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
+		\STATE Otherwise:
+		\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
+
+		\STATE
+
+		\STATE \textbf{2) Reward calcuation.} 
+		\STATE Compress image $ x_t $ at quality $ c_t $ to upload
+		\STATE Receive $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the cloud service
+		\STATE $ r \leftarrow R(\Delta s, \mathcal{A}_c) $
+
+		\STATE 
+		\STATE \textbf{3) Gradient decent.} Generate $ c_t, x_{t+1} $
+		\STATE $ s_{t+1} \leftarrow s_t $, $ \phi_{t+1} \leftarrow \phi \big(\mathcal{E}(f_{t+1})\big) $
+		\STATE $ \mathcal{D} \leftarrow \mathcal{D} \bigcup \{(\phi_t, c_t, r_t, \phi_{t+1}) \} $
+		\IF {$ t \mod T = 0 $ and $ t \geq T_{\rm start} $}
+		\STATE Sample a randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
+		\STATE $ y_i \leftarrow r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
 		\STATE Compute decay exploration rate \\
-		$ \epsilon = 
+		$ \epsilon \leftarrow 
 		\begin{cases}
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[!t]
 	\centerline{\includegraphics[width=0.8\linewidth]{figures/overall-diagram.pdf}}
@@
 %\end{figure}
-\begin{figure}[htbp]
+\begin{figure}[!t]
 	\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.1cm, semithick]
@@
 
-\begin{figure}[htbp]
+\begin{figure}[!t]
 	\includegraphics[width=\linewidth]{figures/quality_chosen.pdf}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[!t]
 	\includegraphics[width=\linewidth]{figures/dataset_change.pdf}
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[!t]
 	\begin{minipage}{0.2\linewidth}

### 2020-03-26 paper/sections/introduction.tex
minor

@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[!t]
 %	\begin{tabular}{cc}
@@
 % \end{itemize}
+
 The rest of this paper is organized as follows.
-We discuss related works in Section.~\ref{Section: related_works}.
-We present our framework and detailed design in Section.~\ref{Section: design}.
-We present our solution's performance in Section.~\ref{Section: evaluation} and conclude the paper in Section.~\ref{Section: conclusion}.
+We discuss related works in Section \ref{Section: related_works}.
+We present our framework and detailed design in Section \ref{Section: design}.
+We present our solution's performance in Section \ref{Section: evaluation} and conclude the paper in Section \ref{Section: conclusion}.
 

### 2020-04-03 paper/sections/design.tex
change to TOMM template

@@
 	%\end{tabular}
-	\vspace{0.1cm}
+	%\vspace{0.1cm}
 	\caption{Comparing to the conventional solution, our solution can update the compression strategy based on the backend model feedback}
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 	\centerline{\includegraphics[width=0.8\linewidth]{figures/overall-diagram.pdf}}
-	\vspace{0.2cm}
+%	\vspace{0.2cm}
 	\caption{Diagram of AdaCompress architecture}
 	\label{fig: diagram}
-\end{figure*}
+\end{figure}
+
+%\begin{figure}[H]
+%	\centerline{\includegraphics[width=0.8\linewidth]{figures/overall-diagram.pdf}}
+%	\vspace{0.2cm}
+%	\caption{Diagram of AdaCompress architecture}
+%	\label{fig: diagram}
+%\end{figure}
 
@@
 %\subsubsection{\textbf{Inference}}
-\subsubsection{Inference}
+\subsubsection{Inference:}
 
@@
 %\subsubsection{\textbf{Estimation}}
-\subsubsection{Estimation}
+\subsubsection{Estimation:}
 
@@
 %\subsubsection{\textbf{Model Querying}}
-\subsubsection{Model Querying}
+\subsubsection{Model Querying:}
 
@@
 %\subsubsection{\textbf{Re-training}}
-\subsubsection{Re-training}
+\subsubsection{Re-training:}
 
@@
 %\subsubsection{\textbf{Compression Level Choice Variation}}
-\subsubsection{Compression Quality Level Choice Variation}
+\subsubsection{Compression Quality Level Choice Variation:}
 
@@
 \begin{figure}[!t]
-	\includegraphics[width=\linewidth]{figures/quality_chosen.pdf}
+	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
 	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
@@
 
-%\begin{figure}[H]
+\begin{figure}[!t]
+    \includegraphics[width=0.8\linewidth]{figures/dataset_change.pdf}
+    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
+    \label{fig: dataset_change}
+\end{figure}
+
+%\begin{figure}[!t]
 %	\includegraphics[width=\linewidth]{figures/dataset_change.pdf}
-%    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
+%	\caption{Histogram of RL agent's best compression quality level selection for different input image ``sceneries''}
 %	\label{fig: dataset_change}
@@
 
-\begin{figure}[!t]
-	\includegraphics[width=\linewidth]{figures/dataset_change.pdf}
-	\caption{Histogram of RL agent's best compression quality level selection for different input image ``sceneries''}
-	\label{fig: dataset_change}
-\end{figure}
-
 %\subsubsection{\textbf{Attention Map Variation}}
-\subsubsection{Attention Map Variation}
+\subsubsection{Attention Map Variation:}
 \label{subsec: attention map}
@@
 	\begin{minipage}{0.2\linewidth}
-		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure1.png}}
+		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/robust_figure1.png}}
 		\centerline{(1a) Q=5}
@@
 	\begin{minipage}{0.2\linewidth}
-		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure2.png}}
+		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/robust_figure2.png}}
 		\centerline{(1b) Q=15}
@@
 	\begin{minipage}{0.2\linewidth}
-		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure3.png}}
+		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/robust_figure3.png}}
 		\centerline{(1c) Q=15}
@@
 	\begin{minipage}{0.2\linewidth}
-		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/robust_figure4.png}}
+		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/robust_figure4.png}}
 		\centerline{(1d) Q=15}
@@
 	\begin{minipage}{0.2\linewidth}
-		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure1.png}}
+		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/sensetive_figure1.png}}
 		\centerline{(2a) Q=85}
@@
 	\begin{minipage}{0.2\linewidth}
-		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure2.png}}
+		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/sensetive_figure2.png}}
 		\centerline{(2b) Q=85}
@@
 	\begin{minipage}{0.2\linewidth}
-		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure3.png}}
+		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/sensetive_figure3.png}}
 		\centerline{(2c) Q=75}
@@
 	\begin{minipage}{0.2\linewidth}
-		\centerline{\includegraphics[width=4.0cm, height=3.0cm]{figures/sensetive_figure4.png}}
+		\centerline{\includegraphics[width=3.5cm, height=3.0cm]{figures/sensetive_figure4.png}}
 		\centerline{(2d) Q=75}
 	\end{minipage}
-	\vspace{0.2cm}
+%	\vspace{0.2cm}
 	\caption{Visualization of the importance map for the RL agent to choose a compression quality level}

### 2020-04-03 paper/sections/evaluation.tex
minor
change to TOMM template

@@
 
-\begin{table}[htbp]
+\begin{table*}[!t]
 	\centering
+	\caption{Experiment parameter}
+	\label{tab: parameters}
 	%     \begin{tabular}{llllll}
@@
 	\end{tabular}
-	\caption{Experiment parameter}
-	\label{tab: parameters}
-	\vspace{-0.5cm}
-\end{table}
+%	\vspace{-0.5cm}
+\end{table*}
 
@@
 
-The default compression quality level for JPEG is usually 75~\cite{pillow_benchmark,imgmin}. Therefore we regard this as a reference value $ c_{\rm ref} = 75 $ of the conventional benchmark. %% \\
+The default compression quality level for JPEG is usually $75$ \cite{pillow_benchmark,imgmin}. Therefore we regard this as a reference value $ c_{\rm ref} = 75 $ of the conventional benchmark.
 
@@
 
-\begin{figure}[htbp]
-	\includegraphics[width=\linewidth]{figures/train_steps_new.pdf}
+\begin{figure}[!t]
+	\includegraphics[width=0.8\linewidth]{figures/train_steps_new.pdf}
 	\caption{Size overhead in the training and inference phase}
@@
 
-\begin{figure}[htbp]
-	\includegraphics[width=\linewidth]{figures/compress-performance.pdf}
+\begin{figure}[!t]
+	\includegraphics[width=0.8\linewidth]{figures/compress-performance.pdf}
 	\caption{Average size and relative accuracy on different cloud services}
@@
 
-\begin{figure}[htbp]
-	\includegraphics[width=\linewidth]{figures/compare_DeepN.pdf}
+\begin{figure}[!t]
+	\includegraphics[width=0.8\linewidth]{figures/compare_DeepN.pdf}
 	\caption{Comparative compression performance between DeepN-JPEG and AdaCompress}
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[!t]
 	\begin{minipage}{0.3\linewidth}
@@
 
-%\begin{figure}[htbp]
+%\begin{figure}[!t]
 %    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
@@
 %\end{figure}
-\begin{figure}[H]
-	\includegraphics[width=\linewidth]{figures/running-retrain.pdf}
+\begin{figure}[!t]
+	\includegraphics[width=0.8\linewidth]{figures/running-retrain.pdf}
 	\caption{AdaCompress's reactions upon scenery change}
@@
 
-\begin{table}[htbp]
-	% \begin{table}[H]
+\begin{table*}[!t]
 	\centering
+	\caption{Latency between image upload and inference result feedback}
+	\label{tab: latency-overhead}
 	%     \begin{tabular}{lll}
@@
 	\end{tabular}
-	\caption{Latency between image upload and inference result feedback}
-	\label{tab: latency-overhead}
 	% \vspace{-0.5cm}
-\end{table}
+\end{table*}
 

### 2020-04-03 paper/sections/introduction.tex
change to TOMM template

@@
 
-\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications.
+With the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications.
 Because of the enormous computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.
@@
 %	\begin{tabular}{cc}
-	\begin{minipage}{0.5\linewidth}
-		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q75.jpeg}}
+	\begin{minipage}{0.4\linewidth}
+		\centerline{\includegraphics[width=4.5cm, trim=0 150 0 150, clip]{figures/donut_q75.jpeg}}
 		\centerline{(1a) Q=75}
@@
 	\hfill
-	\begin{minipage}{0.5\linewidth}
-		\centerline{\includegraphics[width=6.0cm, trim=0 150 0 150, clip]{figures/donut_q55.jpeg}}
+	\begin{minipage}{0.4\linewidth}
+		\centerline{\includegraphics[width=4.5cm, trim=0 150 0 150, clip]{figures/donut_q55.jpeg}}
 		\centerline{(1b) Q=55}
@@
 	\vfill	
-	\begin{minipage}{0.5\linewidth}
-		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q75.jpeg}}
+	\begin{minipage}{0.4\linewidth}
+		\centerline{\includegraphics[width=4.5cm, trim=0 0 0 0]{figures/chameleon_q75.jpeg}}
 		\centerline{(2a) Q=75}
@@
 	\hfill
-	\begin{minipage}{0.5\linewidth}
-		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0]{figures/chameleon_q55.jpeg}}
+	\begin{minipage}{0.4\linewidth}
+		\centerline{\includegraphics[width=4.5cm, trim=0 0 0 0]{figures/chameleon_q55.jpeg}}
 		\centerline{(2b) Q=55}
@@
 	\vfill
-	\begin{minipage}{0.5\linewidth}
-		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_highq.jpeg}}
+	\begin{minipage}{0.4\linewidth}
+		\centerline{\includegraphics[width=4.5cm, trim=0 0 0 0, clip]{figures/tiger_highq.jpeg}}
 		\centerline{(3a) Q=75}
@@
 		\centerline{Baidu prediction \ = \ [``leopard'']}
-		\vspace{0.3cm}
+		\vspace{0.4cm}
 	\end{minipage}
 	\hfill
-	\begin{minipage}{0.5\linewidth}
-		\centerline{\includegraphics[width=6.0cm, trim=0 0 0 0, clip]{figures/tiger_lowq.jpeg}}
+	\begin{minipage}{0.4\linewidth}
+		\centerline{\includegraphics[width=4.5cm, trim=0 0 0 0, clip]{figures/tiger_lowq.jpeg}}
 		\centerline{(3b) Q=5}
@@
 		\centerline{Baidu prediction \ = \ [``leopard'']}
-		\vspace{0.3cm}
+%		\vspace{0.4cm}
 	\end{minipage}

### 2020-07-14 paper/sections/design.tex
response letter and revision

@@
 		\FOR {$t \in 1,2,\cdots, K$}
-		\STATE \textbf{1) Exploration.} With probability $\epsilon$:
+%		\STATE \textbf{1) Exploration.} %With probability $\epsilon$:
+		{\color{revise}\STATE \textbf{1) Exploration}}
+		{\color{revise}\STATE With probability $\epsilon$:}
 		\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
@@
 
-		\STATE \textbf{2) Reward calcuation.} 
+%		\STATE \textbf{2) Reward calcuation.} 
+		{\color{revise}\STATE \textbf{2) Reward calcuation}} 
 		\STATE Compress image $ x_t $ at quality $ c_t $ to upload
@@
 		\STATE 
-		\STATE \textbf{3) Gradient decent.} Generate $ c_t, x_{t+1} $
+%		\STATE \textbf{3) Gradient decent.} %Generate $ c_t, x_{t+1} $
+		{\color{revise}\STATE \textbf{3) Gradient decent}}
+		{\color{revise}\STATE Generate $ c_t, x_{t+1} $}
 		\STATE $ s_{t+1} \leftarrow s_t $, $ \phi_{t+1} \leftarrow \phi \big(\mathcal{E}(f_{t+1})\big) $
@@
 		\IF {$ t \mod T = 0 $ and $ t \geq T_{\rm start} $}
-		\STATE Sample a randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
+%		\STATE Sample a randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
+		{\color{revise}
+		\STATE Sample a randomly mini-batch of transitions $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
 		\STATE $ y_i \leftarrow r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
-		\STATE Compute decay exploration rate \\
+		\STATE Compute decay exploration rate 
 		$ \epsilon \leftarrow 
@@
 		\end{cases} $
-		\STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
+		\STATE Perform a gradient descent step on $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
+		}
+%		\STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
 		\ENDIF
@@
 Basically, we want the agent to choose a proper compression quality level for minimizing the upload image size while remaining acceptable accuracy.
-Therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $.
-We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $.
+\textcolor{revise}{Therefore the overall reward $ r $ should be positively correlated with the accuracy $ \mathcal{A} $ while negatively with the compression ratio $ \Delta s $.} We introduce two linear factors $ \alpha $ and $ \beta $ to form a linear combination $ r = \alpha \mathcal{A} - \Delta s + \beta $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $.
 %% \\
 
+% Therefore the overall reward $ r $ should be in proportion to the accuracy $ \mathcal{A} $ while in inverse proportion to the compression ratio $ \Delta s $.
 \subsection{Inference-Estimation-Querying-Retraining Mechanism}
@@
 \begin{cases}
-\frac{1}{n}\sum_{i=N-n}^{N} \mathcal{A}_i & \text{ if } N \geq n \\ 
-\frac{1}{n}\sum_{i=1}^{n} \mathcal{A}_i & \text{ if } N < n 
+%\frac{1}{n}\sum_{i=N-n}^{N} \mathcal{A}_i & \text{ if } N \geq n \\ 
+%\frac{1}{n}\sum_{i=1}^{n} \mathcal{A}_i & \text{ if } N < n 
+{\color{revise}\frac{1}{n}\sum_{i=N-n+1}^{N} } \mathcal{A}_i & \text{ if } N \geq n \\ 
+{\color{revise}\frac{1}{N}\sum_{i=1}^{N} }\mathcal{A}_i & \text{ if } N < n 
 \end{cases}
@@
 
-With this definition, an intuitive formulation of the change of $ p_{\rm est} $ is in inverse proportion of the gradient of $ \mathcal{A} $, meaning that when the recent accuracy decreases, the estimation probability $ p_{\rm est} $ would increase.
-We define that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a scaling factor.
-With this recursive formula, we have the general term of $p_{\rm est} = p_0 + \omega \sum_{i=0}^{N} \nabla \bar{\mathcal{A}_i} $ where $ p_0 $ is an initial estimation probability.
+With this definition, \textcolor{revise}{the change of $ p_{\rm est} $ should be negatively correlated with} the gradient of $ \mathcal{A} $, meaning that when the recent accuracy decreases, the estimation probability $ p_{\rm est} $ would increase.
+We define that $ p'_{\rm est} = p_{\rm est} + \omega \nabla \bar{\mathcal{A}} $ where $ \omega $ is a \textcolor{revise}{negative} scaling factor.
+With this recursive formula, we have the general term of $p_{\rm est} = p_0 + \omega {\color{revise}\sum_{i=1}^{N}} \nabla \bar{\mathcal{A}_i} $ where $ p_0 $ is an initial estimation probability.
+
+% an intuitive formulation of % is in inverse proportion of
+% \sum_{i=0}^{N}
 
@@
 
-In our experiment, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different.
-As shown in Figure~\ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's selections are distributed more evenly.
-The ``optimal'' compression strategies are different for different backend cloud services.
+\textcolor{revise}{As shown in Figure~\ref{fig: quality_chosen}, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different.
+We compute the \emph{mean} and \emph{standard deviation} of compression quality levels.
+The mean is respectively 33.4, 24.7 and 31.6 on Baidu Vison, Face++ and Amazon Rekognition.
+For Face++, the \emph{mean} of compression quality levels is lower than that for Baidu Vision.
+The standard deviation is respectively 22.77, 19.19 and 22.46 on Baidu Vison, Face++ and Amazon Rekognition.} The ``optimal'' compression strategies are different for different backend cloud services.
 This variation is caused by the interaction between the agent and the backend cloud model in the training phase.
@@
 
-\begin{figure}[!t]
-	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
-	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
+%In our experiment, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different.
+As shown in Figure~\ref{fig: quality_chosen}, for Face++ and Amazon Rekognition, the agent's choices are concentrated at around $ c=15 $, but for Baidu Vision, the agent's selections are distributed more evenly.
+
+\begin{figure*}[!t]
+{\color{revise}
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Baidu_choices1.pdf}}
+		\centerline{(a) Baidu Vision}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Facepp_choices1.pdf}}
+		\centerline{(b) Face++}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Amazon_choices1.pdf}}
+		\centerline{(c) Amazon Rekognition}
+	\end{minipage}		
+	\caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different cloud services}}
 	\label{fig: quality_chosen}
-	% \vspace{-0.3cm}
-\end{figure}
+}
+\end{figure*}
+
+%\begin{figure}[!t]
+%	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
+%	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
+%	\label{fig: quality_chosen}
+%	% \vspace{-0.3cm}
+%\end{figure}
 
@@
 We randomly sample images from ImageNet~\cite{ImageNet} whose images are mostly taken in the daytime, to act as a daytime scenery, and randomly select nighttime images from the FLIR Thermal Dataset~\cite{FLIR} to form another dataset to act as a nighttime scenery.
-The histogram shown in Figure~\ref{fig: dataset_change} points out that, for the ImageNet images, the agent prefers a low compression quality level, but its choices are distributed more evenly.
+\textcolor{revise}{The histogram shown in Figure~\ref{fig: dataset_change} points out that the distribution of compression quality levels is different on ImageNet and FLIR Thermal Dataset.
+For ImageNet and FLIR, the mean is respectively 43.3 and 47.5, and the standard deviation is respectively 19.52 and 26.56.} We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection would change as well.
+This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features.
+
+\textcolor{revise}{We can also find that Figure~\ref{fig: quality_chosen}(a) and Figure~\ref{fig: dataset_change}(a) is different, even if we use the same cloud service (Baidu Vision) and image dataset (ImageNet).
+When we use the same cloud service at different times, the cloud service commonly invokes different backend cloud models.
+Therefore the interaction between the agent and the backend cloud model is different.
+This result variation presents that the agent can adaptively make a proper compression strategy in different complex environments, indicating our solution's generality and practicality.} %% \\
+
+%The histogram shown in Figure~\ref{fig: dataset_change} points out that, for the ImageNet images, the agent prefers a low compression quality level, but its choices are distributed more evenly.
 For the FLIR Thermal images, the agent's choices are more accumulated in some relatively higher compression quality levels.
-We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection would change as well.
-This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features.
-%% \\
-
-\begin{figure}[!t]
-    \includegraphics[width=0.8\linewidth]{figures/dataset_change.pdf}
-    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
-    \label{fig: dataset_change}
-\end{figure}
 
 %\begin{figure}[!t]
-%	\includegraphics[width=\linewidth]{figures/dataset_change.pdf}
-%	\caption{Histogram of RL agent's best compression quality level selection for different input image ``sceneries''}
+%    \includegraphics[width=0.8\linewidth]{figures/dataset_change.pdf}
+%    \caption{Histogram of RL agent's best compression level selection for different scenery image inputs}
 %    \label{fig: dataset_change}
 %\end{figure}
+
+\begin{figure*}[!t]
+{\color{revise}
+	\begin{minipage}[t]{0.48\linewidth}
+		\centerline{\includegraphics[width=7cm]{figures/ImageNet_Baidu_choices.pdf}}
+		\centerline{(a) ImageNet images}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.48\linewidth}
+		\centerline{\includegraphics[width=7cm]{figures/FLIR_Baidu_choices.pdf}}
+		\centerline{(b) FLIR images}
+	\end{minipage}	
+    \caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different scenery image inputs}}
+	\label{fig: dataset_change}
+}
+\end{figure*}
 

### 2020-07-14 paper/sections/evaluation.tex
response letter and revision

@@
 		\toprule
-		notation          & value & & & notation     & value  \\ \midrule
+		Notation          & Value & & & Notation     & Value  \\ \midrule
 		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
@@
 		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
-		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ \bottomrule
+		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ 
+		{\color{revise} $ \mathcal{A}_0 $} & {\color{revise}0.8} & & & {\color{revise}$ T_{\rm start} $} & {\color{revise}128} \\
+		$ {\color{revise}\alpha} $ & {\color{revise}1} & & & {\color{revise}$ \beta $} & {\color{revise}1}  \\ \bottomrule
 	\end{tabular}
@@
 \end{table*}
+
+%\begin{table*}[!t]
+%	\centering
+%	\caption{Experiment parameter}
+%	\label{tab: parameters}
+%	%     \begin{tabular}{llllll}
+%	\begin{tabular}{cccccc}
+%		\toprule
+%		Notation          & Value & & & Notation     & Value  \\ \midrule
+%		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
+%		$\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
+%		$\gamma$      & 0.95  & & & $\omega$ & -3   \\
+%		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
+%		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ \bottomrule
+%	\end{tabular}
+%%	\vspace{-0.5cm}
+%\end{table*}
 
@@
 Running this RL agent brings extra latency to the whole system.
-In this subsection, we evaluate the overall latency overhead.
+In this subsection, we evaluate the end-to-end latency.
 %% \\
@@
 We compute compressed file size for batches of images, and test the RL agent's inference time and the latency of uploading such compressed images.
+\textcolor{revise}{We respectively test the average inference latency on 1000 ImageNet images and 1000 FLIR images}, and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb.
+2019, to verify the end-to-end latency performance.
+The latency comparison is listed in Table~\ref{tab: latency-overhead}.
+%% \\
+
+%We compute compressed file size for batches of images, and test the RL agent's inference time and the latency of uploading such compressed images.
 We test the average inference latency on 1000 ImageNet images and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb.
@@
 \begin{table*}[!t]
+{\color{revise}
 	\centering
-	\caption{Latency between image upload and inference result feedback}
+	\caption{\textcolor{revise}{Latency of edge device to cloud service}}
 	\label{tab: latency-overhead}
 	%     \begin{tabular}{lll}
-	\begin{tabular}{ccc}
+	\resizebox{\textwidth}{!}{
+	\begin{tabular}{cccccc}
 		\toprule
-		& Benchmark & AdaCompress  \\ \midrule
-		Average upload size          & 42.68 KB  &  18.46 KB            \\
-		Inference latency    & 0 s       & 2.09 ms          \\
-		Transmission latency & 12.35 ms       & 5.34 ms          \\
-		Overall latency      & 12.35 ms       & 7.43 ms          \\ \bottomrule
-	\end{tabular}
+		Dataset & Solution & Average upload size & Inference latency \
+		& Transmission latency & End-to-end latency \\ \midrule
+		ImageNet & Benchmark & 42.68 KB & 0 ms & 12.35 ms & 12.35 ms \\
+		ImageNet & AdaCompress & 18.64 KB & 2.09 ms & 5.34 ms & 7.43 ms \\
+		FLIR & Benchmark & 44.66 KB & 0 ms & 12.93 ms & 12.93 ms \\
+ 		FLIR & AdaCompress & 17.07 KB & 2.03 ms & 4.94 ms & 6.97 ms \\ \bottomrule
+	\end{tabular}}
 	% \vspace{-0.5cm}
+}
 \end{table*}
+%\begin{table*}[!t]
+%	\centering
+%	\caption{Latency between image upload and inference result feedback}
+%	\label{tab: latency-overhead}
+%	%     \begin{tabular}{lll}
+%	\begin{tabular}{ccc}
+%		\toprule
+%		& Benchmark & AdaCompress  \\ \midrule
+%		Average upload size          & 42.68 KB  &  18.46 KB            \\
+%		Inference latency    & 0 s       & 2.09 ms          \\
+%		Transmission latency & 12.35 ms       & 5.34 ms          \\
+%		Overall latency      & 12.35 ms       & 7.43 ms          \\ \bottomrule
+%	\end{tabular}
+%	% \vspace{-0.5cm}
+%\end{table*}
 
 Our solution brings in inference latency to the end-to-end latency, but the transmission latency is low by reducing the upload file size.
-In today's network architecture where the edge infrastructure's computational power is increasing significantly ~\cite{satyanarayanan2017emergence,hu2015mobile}, we can use the computing power of the edge infrastructure in exchange for the reduction of upload traffic load and transmission latency.
-%% \\
+In today's network architecture where the edge infrastructure's computational power is increasing significantly~\cite{satyanarayanan2017emergence,hu2015mobile}, we can use the computing power of the edge infrastructure in exchange for the reduction of upload traffic load and transmission latency.
+\textcolor{revise}{Compared with the benchmark solution, our solution effectively reduces the end-to-end latency on both ImageNet and FLIR dataset.} %% \\
+
+\subsection{\textcolor{revise}{Overall Memory and Latency Overhead}}
+
+\subsubsection{\textcolor{revise}{Memory Overhead:}}
+\textcolor{revise}{The memory overhead is divided into two parts: the static occupied memory space and dynamic memory usage.
+Firstly, the static occupied memory space is the memory of the model's size.
+We use Keras to construct and save MobileNetV2 and the RL agent.
+We check file size of the saved model as the model's size.
+A RL agent model's size is 1 MB, and the feature extractor MobileNetV2's size is 8.9 MB.
+The model caching library stores the most recent five RL agents.
+The overall memory of the model's size is at most 13.9 MB.
+Secondly, the dynamic memory usage is the memory usage during AdaCompress runs.
+The overall memory usage mainly includes the memory buffer of transitions and the memory usage caused by the RL agent and feature extractor.
+When caching transitions of 1000 images in the memory buffer, it occupies about 500 KB.
+We use Psutil to measure the peak memory usage during AdaCompress runs.
+The peak memory usage is about 367 MB.
+Thirdly, in real-world edge-application scenarios, common edge infrastructures have enough memory to deploy this algorithm, such as Raspberry Pi 4 Model B's \cite{Raspberry-Pi} memory is 2/4/8 GB, and Huawei Atlas 500 edge station's memory is 4/8 GB.}
+
+\subsubsection{\textcolor{revise}{Training and Re-loading Latency:}}
+\textcolor{revise}{Although AdaCompress can be highly efficient to run on today's edge infrastructures, it would cause extra latency overhead, such as training and re-loading latency.
+In this subsection, we evaluate the latency overhead.}
+
+%\begin{table*}[!t]
+%	\centering
+%	\caption{Time cost of training}
+%	\label{tab: training-time}
+%		\begin{tabular}{cccc}
+%			\toprule
+%			Dataset & Number of training images & Time cost & Real time cost \\ \midrule
+%			ImageNet & 898 & 15.86 min & 7.89 min \\
+%			FLIR & 910 & 15.63 min & 7.85 min \\ \bottomrule
+%	\end{tabular}
+%	% \vspace{-0.5cm}
+%\end{table*}
+
+\textcolor{revise}{In our experiments, the convergence condition of training is that the recent average accuracy over 0.8 meanwhile the recent average reward over 0.45.
+The experiment results show the number of training images is respectively 898 and 910 on ImageNet and FLIR.
+The time cost mainly depends on the frequency of sending images and the inference speed of the cloud service.
+If the end-user sends images continuously, and cloud service's inference speed is about 10 images per second, the time costs are respectively about 197.3s and 200.8s on ImageNet and FLIR.
+In the training phase, we need to upload reference images and compressed images.
+We consider the time cost of uploading reference images and obtaining the feedbacks as the benchmark latency.
+If we minus this benchmark latency, the real training time cost is not over 100s.
+It is worth to spend such upload size overhead and time cost at the beginning when we need to infer thousands of images.}
+
+%And the training time respectively is 15.36 min and 15.63 min on ImageNet and FLIR.
+
+\textcolor{revise}{The \emph{inference-estimation-querying-retraining} mechanism would either re-load or re-train a RL agent intelligently when capturing the scenery change.
+The re-training time cost is similar to the training time cost which is described above.
+The latency of re-loading a RL agent model is about 1.85s.
+To \emph{erase} this latency, we use another process to re-load the model in our experiments.
+The mechanism still uses the old RL agent to choose a compression quality level before the re-loading process has finished.}

### 2020-07-14 paper/sections/introduction.tex
response letter and revision

@@
 
-$\rhd$ We design an interactive training environment that can be applied to different online computer vision-based services.
+\begin{itemize}
+
+\item We design an interactive training environment that can be applied to different online computer vision-based services.
 We propose a Deep Q-learning Network-based~\cite{DQN} agent to evaluate and predict the performance of a compression quality level on an input image.
 In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU~\cite{google-tpu}, Huawei Atlas 500 edge station~\cite{huawei-atlas500}).
-
-$\rhd$ We build a reinforcement learning-based framework to train the agent in the above environment.
+%$\rhd$	
+\item We build a reinforcement learning-based framework to train the agent in the above environment.
 The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size.
@@
 
-$\rhd$~~In this journal extension, we provide more analysis and insights on our design.
+\item In this journal extension, we provide more analysis and insights on our design.
 We notice that the Deep Q-learning Network-based agent's behaviors are various for different input image “sceneries” and backend cloud services.
@@
 
-$\rhd$ We evaluate our system on representative cloud-based deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}.
+\item We evaluate our system on representative cloud-based deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}.
 We show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy.
 Compared to baseline DeepN-JPEG~\cite{DeepN-JPEG}, the overall accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.
-
+\end{itemize}
 % \begin{itemize}

### 2020-07-15 paper/sections/evaluation.tex
minor table 1

@@
 		{\color{revise} $ \mathcal{A}_0 $} & {\color{revise}0.8} & & & {\color{revise}$ T_{\rm start} $} & {\color{revise}128} \\
-		$ {\color{revise}\alpha} $ & {\color{revise}1} & & & {\color{revise}$ \beta $} & {\color{revise}1}  \\ \bottomrule
+		$ {\color{revise}\alpha} $ & {\color{revise}1} & & & {\color{revise}$ \beta $} & {\color{revise}0}  \\ \bottomrule
 	\end{tabular}

### 2020-07-15 paper/sections/design.tex
r1

@@
 We compute the \emph{mean} and \emph{standard deviation} of compression quality levels.
-The mean is respectively 33.4, 24.7 and 31.6 on Baidu Vison, Face++ and Amazon Rekognition.
+The mean is $33.4$, $24.7$ and $31.6$ on Baidu Vison, Face++ and Amazon Rekognition, respectively.
 For Face++, the \emph{mean} of compression quality levels is lower than that for Baidu Vision.
-The standard deviation is respectively 22.77, 19.19 and 22.46 on Baidu Vison, Face++ and Amazon Rekognition.} The ``optimal'' compression strategies are different for different backend cloud services.
+The standard deviation is $22.77$, $19.19$ and $22.46$ on Baidu Vison, Face++ and Amazon Rekognition, respectively.} The ``optimal'' compression strategies are different for different backend cloud services.
 This variation is caused by the interaction between the agent and the backend cloud model in the training phase.
@@
 \textcolor{revise}{The histogram shown in Figure~\ref{fig: dataset_change} points out that the distribution of compression quality levels is different on ImageNet and FLIR Thermal Dataset.
-For ImageNet and FLIR, the mean is respectively 43.3 and 47.5, and the standard deviation is respectively 19.52 and 26.56.} We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection would change as well.
+For ImageNet and FLIR, the mean is 43.3 and 47.5, respectively; and the standard deviation is 19.52 and 26.56, respectively.} To maintain high accuracy when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection should change as well.
 This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features.
@@
 Therefore the interaction between the agent and the backend cloud model is different.
-This result variation presents that the agent can adaptively make a proper compression strategy in different complex environments, indicating our solution's generality and practicality.} %% \\
+This variation presents that the agent can adaptively make a proper compression strategy in different complex environments, indicating our solution's generality and practicality.} %% \\
 

### 2020-07-15 paper/sections/evaluation.tex
r1

@@
 \textcolor{revise}{In our experiments, the convergence condition of training is that the recent average accuracy over 0.8 meanwhile the recent average reward over 0.45.
-The experiment results show the number of training images is respectively 898 and 910 on ImageNet and FLIR.
+The experiment results show the number of training images is 898 and 910 on ImageNet and FLIR, respectively.
 The time cost mainly depends on the frequency of sending images and the inference speed of the cloud service.
-If the end-user sends images continuously, and cloud service's inference speed is about 10 images per second, the time costs are respectively about 197.3s and 200.8s on ImageNet and FLIR.
+If the end-user sends images continuously, and cloud service's inference speed is about 10 images per second, the time costs are 197.3s and 200.8s on ImageNet and FLIR, respectively.
 In the training phase, we need to upload reference images and compressed images.
@@
 The latency of re-loading a RL agent model is about 1.85s.
-To \emph{erase} this latency, we use another process to re-load the model in our experiments.
+To \emph{reduce} this latency, we use another process to re-load the model in our experiments.
 The mechanism still uses the old RL agent to choose a compression quality level before the re-loading process has finished.}

### 2020-10-10 paper/sections/design.tex
second revision

@@
 
-We also denote JPEG input images as $ f_{ic} = J(x_i, c) $ that for an input image $ x_i $ and a given compression quality level $ c $, and it outputs a compressed file $ f_{ic} $ at the size of $ s_{ic} $.
-For a reference compression quality level $ c_{\rm ref} $, the compressed file size is $ s_{\rm ref} $.
+We also denote JPEG input images as $ f_{ic} = J(x_i, c) $ that for an input image $ x_i $ and a given compression quality level $ c $, and it outputs a compressed file $ f_{ic} $ at the size of {\color{revise2} $ \hat{s}_{ic} $}.
+For a reference compression quality level $ c_{\rm ref} $, the compressed file size is {\color{revise2} $ \hat{s}_{\rm ref} $}.
 Besides, the input image from a specific scenery usually belongs to a particular contextual group~\cite{mcdnn}.
@@
 To obtain cloud-end recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent uploads the compressed image $ x_c $ and the reference image $ x_{\rm ref} $ to the cloud-end.
-Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud-end recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent obtains the reference file size $ s_{\rm ref} $ and compressed file size $ s_c $, and computes the file compression ratio $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.
+Comparing the two uploaded instances $ \{x_{\rm ref}, x_c\} $ and cloud-end recognition results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent obtains the reference file size {\color{revise2}$ \hat{s}_{\rm ref} $} and compressed file size {\color{revise2}$ \hat{s}_c $}, and computes the file compression ratio {\color{revise2}$ \Delta s = \frac{\hat{s}_c}{\hat{s}_{\rm ref}} $} and accuracy metric $ \mathcal{A}_c $.
 
@@
 
-The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size $ s_c $ while keeping the accuracy $ \mathcal{A} $.
+The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size {\color{revise2}$ \hat{s}_c $} while keeping the accuracy $ \mathcal{A} $.
 For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $.
@@
 
-We formulate the feature extractor's output $ \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}.
+We formulate the feature extractor's output {\color{revise2} $ s = \mathcal{E}(J(\mathcal{X}, c)) $} \iffalse $ \mathcal{E}(J(\mathcal{X}, c)) $ \fi as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}.
 In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $.
-We denote the \emph{action-value function} as $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $ and the optimal compression quality level at time $ t $ as $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
-In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where $ s = \mathcal{E}(f_t) $ and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $.
-Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over sequences $ s $ and the compression quality level $ c $~\cite{DQN}.
+We denote the \emph{action-value function} as {\color{revise2} $ Q(\mathcal{E}(f_t), c; \theta) $} \iffalse $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi and the optimal compression quality level at time $ t $ as {\color{revise2} $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $} \iffalse $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
+In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where {\color{revise2} state $ s = \mathcal{E}(f_i) $} and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $.
+Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over {\color{revise2} state} \iffalse sequences \fi $ s $ and the compression quality level $ c $~\cite{DQN}.
 When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.
@@
 In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction and decreases the randomness when training afterward.
-All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
+{\color{revise2} In iteration t, we  leverage the feature extractor $\mathcal{E}$ to obtain state $s_t = \mathcal{E}(J(x_t,c_{ref}))$.
+The RL agent $\phi$ generates a compresion quality level $c_t$.
+The framework compresses image $x_t$ at quality $c_t$ to upload and obtains reward $r_t$.
+The framework obtains next image $x_{t+1}$ and generates next state $ s_{t+1} = \mathcal{E}\big(J(x_{t+1},c_{ref})\big) $.
+The framework stores transition $(s_t, c_t, r_t, s_{t+1},\mathcal{A}_t )$ in a memory buffer $\mathcal{D}$.
+Especially, $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in \ref{subsec: mechanism}  Inference-Estimation-Querying-Retraining Mechanism.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
 The training procedure would converge when the agent's randomness keeps decaying.
@@
 \begin{algorithm}[!t]
+{\color{revise2}
 	\caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
@@
 		\STATE Initialize \emph{action-value function} $ Q $ with random weights $ \theta $
-		\STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
+		{\color{revise2}
+		\STATE Initialize state $ s_1 \leftarrow \mathcal{E}\big(J(x_1, c_{ref})\big), x_1 \in \mathcal{X} $ }
+%		and $ \phi_1 = \phi(f_1) $
 		\FOR {$t \in 1,2,\cdots, K$}
 %		\STATE \textbf{1) Exploration.} %With probability $\epsilon$:
-		{\color{revise}\STATE \textbf{1) Exploration}}
-		{\color{revise}\STATE With probability $\epsilon$:}
+		\STATE \textbf{1) Exploration}
+		\STATE With probability $\epsilon$:
 		\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
 		\STATE Otherwise:
-		\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
-
+		{\color{revise2}
+		\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $ }
+%		{\rm argmax}_cQ\Big(\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
 		\STATE
@@
 %		\STATE \textbf{2) Reward calcuation.} 
-		{\color{revise}\STATE \textbf{2) Reward calcuation}} 
+		\STATE \textbf{2) Reward calcuation} 
 		\STATE Compress image $ x_t $ at quality $ c_t $ to upload
 		\STATE Receive $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the cloud service
-		\STATE $ r \leftarrow R(\Delta s, \mathcal{A}_c) $
+		{\color{revise2} \STATE compute reward $ r \leftarrow R(\Delta s, \mathcal{A}_c) $ according to \ref{subsec: reward} Reward Feedback Design}
 
@@
 %		\STATE \textbf{3) Gradient decent.} %Generate $ c_t, x_{t+1} $
-		{\color{revise}\STATE \textbf{3) Gradient decent}}
-		{\color{revise}\STATE Generate $ c_t, x_{t+1} $}
-		\STATE $ s_{t+1} \leftarrow s_t $, $ \phi_{t+1} \leftarrow \phi \big(\mathcal{E}(f_{t+1})\big) $
-		\STATE $ \mathcal{D} \leftarrow \mathcal{D} \bigcup \{(\phi_t, c_t, r_t, \phi_{t+1}) \} $
+		\STATE \textbf{3) Gradient descent}
+		{\color{revise2}\STATE Obtain next image $ x_{t+1} $
+		\STATE Generate next state $ s_{t+1} \leftarrow \mathcal{E}\big(J(x_{t+1},c_{ref})\big) $
+%		, $ \phi_{t+1} \leftarrow \phi \big(\mathcal{E}(f_{t+1})\big) $
+%		\STATE $ s_{t+1} \leftarrow s_t $, $ \phi_{t+1} \leftarrow \phi \big(\mathcal{E}(f_{t+1})\big) $
+		\STATE $ \mathcal{D} \leftarrow \mathcal{D} \bigcup \{(s_t, c_t, r_t, s_{t+1},\mathcal{A}_t ) \} $
+%		\STATE $ \mathcal{D} \leftarrow \mathcal{D} \bigcup \{(\phi_t, c_t, r_t, \phi_{t+1}) \} $
 		\IF {$ t \mod T = 0 $ and $ t \geq T_{\rm start} $}
 %		\STATE Sample a randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
-		{\color{revise}
-		\STATE Sample a randomly mini-batch of transitions $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
-		\STATE $ y_i \leftarrow r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
+		\STATE Sample a randomly mini-batch of transitions $ (s_j, c_j, r_j, s_{j+1},\mathcal{A}_j ) $ from memory buffer $ \mathcal{D} $
+		\STATE $ y_j \leftarrow r_j + \gamma \max_{c'}Q(s_{j+1}, c'; \theta) $
 		\STATE Compute decay exploration rate 
@@
 		\end{cases} $
-		\STATE Perform a gradient descent step on $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
-		}
+		\STATE Perform a gradient descent step on $ \big(y_j - Q(s_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
+
 %		\STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
 		\ENDIF
+	    }
 		\ENDFOR
 	\end{algorithmic}
+}
 \end{algorithm}
 
+%\begin{algorithm}[!t]
+%	\caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
+%	\label{alg: rl-train}
+%	\begin{algorithmic}[1]
+%		\STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
+%		\STATE Initialize \emph{action-value function} $ Q $ with random weights $ \theta $
+%		\STATE Initialize sequence $ s_1 = \mathcal{E}\big(J(x_1, c_1)\big), x_1 \in \mathcal{X} $ and $ \phi_1 = \phi(f_1) $
+%		\FOR {$t \in 1,2,\cdots, K$}
+%		%		\STATE \textbf{1) Exploration.} %With probability $\epsilon$:
+%		{\color{revise}\STATE \textbf{1) Exploration}}
+%		{\color{revise}\STATE With probability $\epsilon$:}
+%		\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
+%		\STATE Otherwise:
+%		\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ\Big(\phi\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
+%		
+%		\STATE
+%		
+%		%		\STATE \textbf{2) Reward calcuation.} 
+%		{\color{revise}\STATE \textbf{2) Reward calcuation}} 
+%		\STATE Compress image $ x_t $ at quality $ c_t $ to upload
+%		\STATE Receive $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the cloud service
+%		\STATE $ r \leftarrow R(\Delta s, \mathcal{A}_c) $
+%		
+%		\STATE 
+%		%		\STATE \textbf{3) Gradient decent.} %Generate $ c_t, x_{t+1} $
+%		{\color{revise}\STATE \textbf{3) Gradient decent}}
+%		{\color{revise}\STATE Generate $ c_t, x_{t+1} $}
+%		\STATE $ s_{t+1} \leftarrow s_t $, $ \phi_{t+1} \leftarrow \phi \big(\mathcal{E}(f_{t+1})\big) $
+%		\STATE $ \mathcal{D} \leftarrow \mathcal{D} \bigcup \{(\phi_t, c_t, r_t, \phi_{t+1}) \} $
+%		\IF {$ t \mod T = 0 $ and $ t \geq T_{\rm start} $}
+%		%		\STATE Sample a randomly mini-batch of transitions \\ $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
+%		{\color{revise}
+%			\STATE Sample a randomly mini-batch of transitions $ (\phi_j, c_j, r_j, \phi_{j+1}) $ from memory buffer $ \mathcal{D} $
+%			\STATE $ y_i \leftarrow r_j + \gamma \max_{c'}Q(\phi_{j+1}, c'; \theta) $
+%			\STATE Compute decay exploration rate 
+%			$ \epsilon \leftarrow 
+%			\begin{cases}
+%			\mu_{\rm dec}\cdot \epsilon & \text{ if } \ \mu_{\rm dec}\cdot \epsilon > \epsilon_{\min} \\ 
+%			\epsilon_{\min}             & \text{ if } \ \mu_{\rm dec}\cdot \epsilon \leq \epsilon_{\min}
+%			\end{cases} $
+%			\STATE Perform a gradient descent step on $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
+%		}
+%		%		\STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
+%		\ENDIF
+%		\ENDFOR
+%	\end{algorithmic}
+%\end{algorithm}
+
 \subsection{Reward Feedback Design}
+\label{subsec: reward}
 
 In our solution, the agent is trained by the reward feedback from the environment $ \{\mathcal{X}, M\} $.
-In the above formulation, we define compression rate $ \Delta s = \frac{s_c}{s_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at compression quality level $ c $.
+In the above formulation, we define compression rate {\color{revise2}$ \Delta s = \frac{\hat{s}_c}{\hat{s}_{\rm ref}} $} \iffalse $ \Delta s = \frac{s_c}{s_{\rm ref}} $ \fi and accuracy metric $ \mathcal{A}_c $ at compression quality level $ c $.
 Basically, we want the agent to choose a proper compression quality level for minimizing the upload image size while remaining acceptable accuracy.
@@
 \subsection{Inference-Estimation-Querying-Retraining Mechanism}
-
+\label{subsec: mechanism}
 As a running system, we introduce an \emph{inference-estimation-querying-retraining} mechanism to cope with the scenery change in the inference phase, building a system with different components to inferring, capturing the scenery change, then either re-loading or re-training the RL agent based on the performance of the cached model.
@@
 If $ \xi \leq p_{\rm est} $, the estimator would be invoked.
-AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, calculate $ \mathcal{A}_i $ and save the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ to the memory buffer $ \mathcal{D} $.
+AdaCompress would upload the reference image $ x_{\rm ref} $ along with the compressed image $ x_i $ to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $, calculate $ \mathcal{A}_i $ and save the transition {\color{revise2}$ (s_i, c_i, r_i, s_{i+1},\mathcal{A}_i ) $} \iffalse $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ \fi to the memory buffer $ \mathcal{D} $.
 The estimator also compares the recent $ n $ steps' average accuracy $ \bar{\mathcal{A}}_n $ and the initial accuracy threshold $ \mathcal{A}_0 $.
@@
 In this state, the reference image $ x_{\rm ref} $ and compressed image $ x_i $ are uploaded to the cloud-end simultaneously to obtain $ \vec{y}_{\rm ref} $ and $ \vec{y}_i $ which are used to calculate $ \mathcal{A}_i $.
-In each epoch $ i $, the transition $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ is logged in the memory buffer $ \mathcal{D} $.
+In each epoch $ i $, the transition {\color{revise2}$ (s_i, c_i, r_i, s_{i+1},\mathcal{A}_i ) $} \iffalse $ (\phi_i, c_i, r_i, \mathcal{A}_i) $ \fi is logged in the memory buffer $ \mathcal{D} $.
 When the average accuracy $ \bar{\mathcal{A}}_n $ of the latest $ n $ steps is higher than the accuracy threshold $ \mathcal{A}_0 $, the agent would stay in the estimation state with probability $ p_{\rm est} $ or switch to the inference state with probability $ 1 - p_{\rm est} $.

### 2020-10-10 paper/sections/evaluation.tex
second revision

@@
 Figure~\ref{fig: train_steps} presents the upload traffic load of the training and inference phase.
-To be more intuitionistic, we plot the size overhead $ \frac{s}{s_{\rm ref}} $ as the $ y $-axis where $ s $ is the real upload size of AdaCompress and $ s_{\rm ref} $ is the benchmark upload size.
+To be more intuitionistic, we plot the size overhead {\color{revise2} $ \frac{\hat{s}}{\hat{s}_{\rm ref}} $} \iffalse $ \frac{s}{s_{\rm ref}} $ \fi as the $ y $-axis where {\color{revise2} $ \hat{s} $} is the real upload size of AdaCompress and {\color{revise2} $ \hat{s}_{\rm ref} $} is the benchmark upload size.
 Therefore $ y \geq 1 $ means that our solution uploads more data then benchmark, and $ y < 1 $ means the compression rate of AdaCompress.

### 2020-10-10 paper/sections/design.tex
the second revision

@@
 		\STATE Receive $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the cloud service
-		{\color{revise2} \STATE compute reward $ r \leftarrow R(\Delta s, \mathcal{A}_c) $ according to \ref{subsec: reward} Reward Feedback Design}
+		{\color{revise2} \STATE Compute reward $ r \leftarrow R(\Delta s, \mathcal{A}_c) $ according to \ref{subsec: reward} Reward Feedback Design}
 

### 2020-10-21 paper/sections/design.tex
second letter

@@
 We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, \emph{inference-estimation-querying-retraining} mechanism, and insight of RL agent's behaviors separately in the following subsections.
-We provide experimental details of all the hyperparameters in Section.~\ref{Section: evaluation}.
+We provide experimental details of all the hyperparameters in Section~\ref{Section: evaluation}.
 %% \\
@@
 The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size {\color{revise2}$ \hat{s}_c $} while keeping the accuracy $ \mathcal{A} $.
-For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $.
+{\color{revise2} In our design, each compression is treated as a complete RL task that only has one step, and the agent performs the action only once to accomplish the task.
+The agent is able to learn across consecutive tasks, because the input sequence (i.e., consecutive images likely to be captured by the same camera) shares similar contextual characteristics.
+The similar design has also been used in previous studies, including RL-based cache strategy \cite{wang2020intelligent_RL,zhong2018deep_RL,sadeghi2019deep_RL}.} For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $.
 Therefore we can use the Deep Q-learning Network as the RL agent.

### 2020-10-21 paper/sections/evaluation.tex
second letter

@@
 For the cloud-based deep learning services, we choose Baidu Vision, Face++ object detection services and Amazon Rekognition.
-In the experiments, we use two datasets mentioned before in Subsection.~\ref{subsec:insight}.
+In the experiments, we use two datasets mentioned before in Subsection~\ref{subsec:insight}.
 The ImageNet dataset indicates daytime scenery, and the FLIR Thermal Dataset indicates nighttime scenery.
@@
 Since we do not have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric.
-The formula of $ \mathcal{A} $ is presented in Subsection.~\ref{subsec: formulation}.
+The formula of $ \mathcal{A} $ is presented in Subsection~\ref{subsec: formulation}.
 

### 2020-10-21 paper/sections/relatedwork.tex
second letter

@@
 In this journal extension, we improve the previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly.
-Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection.~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).
+Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).
 

### 2020-10-24 paper/sections/design.tex
TOMM R2 submission

@@
 In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction and decreases the randomness when training afterward.
-{\color{revise2} In iteration t, we  leverage the feature extractor $\mathcal{E}$ to obtain state $s_t = \mathcal{E}(J(x_t,c_{ref}))$.
+{\color{revise2} In iteration $t$, we  leverage the feature extractor $\mathcal{E}$ to obtain state $s_t = \mathcal{E}(J(x_t,c_{ref}))$.
 The RL agent $\phi$ generates a compresion quality level $c_t$.
 The framework compresses image $x_t$ at quality $c_t$ to upload and obtains reward $r_t$.
-The framework obtains next image $x_{t+1}$ and generates next state $ s_{t+1} = \mathcal{E}\big(J(x_{t+1},c_{ref})\big) $.
+Then the framework obtains the next image $x_{t+1}$ and generates the next state $ s_{t+1} = \mathcal{E}\big(J(x_{t+1},c_{ref})\big) $.
 The framework stores transition $(s_t, c_t, r_t, s_{t+1},\mathcal{A}_t )$ in a memory buffer $\mathcal{D}$.
-Especially, $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in \ref{subsec: mechanism}  Inference-Estimation-Querying-Retraining Mechanism.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
+Especially, $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in the inference-estimation-querying-retraining mechanism to be discussed in Section \ref{subsec: mechanism}.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
 The training procedure would converge when the agent's randomness keeps decaying.

### 2021-01-07 paper/sections/design.tex
third response

@@
 \label{Section: design}
+
+A brief framework of AdaCompress is shown in Figure~\ref{fig: framework}.
+Briefly, it is a reinforcement learning-based system to train an agent to choose a proper compression quality level $ c $ for one image to be compressed by JPEG.
+We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, \emph{inference-estimation-querying-retraining} mechanism, and insight of RL agent's behaviors separately in the following subsections.
+We provide experimental details of all the hyperparameters in Section~\ref{Section: evaluation}.
+%% \\
 
@@
 
-A brief framework of AdaCompress is shown in Figure~\ref{fig: framework}.
-Briefly, it is a reinforcement learning-based system to train an agent to choose a proper compression quality level $ c $ for one image to be compressed by JPEG.
-We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, \emph{inference-estimation-querying-retraining} mechanism, and insight of RL agent's behaviors separately in the following subsections.
-We provide experimental details of all the hyperparameters in Section~\ref{Section: evaluation}.
-%% \\
+\vspace{-1em}
 
@@
 \label{subsec: formulation}
-
 % \colorbox{red}{notation table}
@@
 \subsection{RL Agent Design}
-
+\label{RL Design}
 The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size {\color{revise2}$ \hat{s}_c $} while keeping the accuracy $ \mathcal{A} $.
@@
 
-We formulate the feature extractor's output {\color{revise2} $ s = \mathcal{E}(J(\mathcal{X}, c)) $} \iffalse $ \mathcal{E}(J(\mathcal{X}, c)) $ \fi as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}.
+{\color{revise3} We start by giving some basics on Markov decision processes (MDPs) \cite{MDP}, which is represented by a tuple $<S,C,P,R,\gamma>$, where $S$ denotes a set of possible states $s$, $C$ a set of feasible actions $c$, $P$ the set of state transition probabilities, $R$ a reward function, and $\gamma$ a discount factor.
+We formulate the feature extractor's output  $ s = \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}.
 In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $.
-We denote the \emph{action-value function} as {\color{revise2} $ Q(\mathcal{E}(f_t), c; \theta) $} \iffalse $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi and the optimal compression quality level at time $ t $ as {\color{revise2} $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $} \iffalse $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
+We use $P_{ss'}^{c} = P \big[s' \mid s, c = \pi(s) \big]$ to denote the state transition probability from state $s$ to $s'$, where $\pi$ is a compression strategy mapping state to actions.
+We therefore obtain a sequence of states and actions $\{ s_1,c_1,s_2,...,c_{t-1},s_t \}$, and this formulation is a MDP.}
+
+{\color{revise3} The goal of the agent is to interact with the emulator environment $ \{\mathcal{X}, M\} $ by selecting actions in a way that maximises future reward $R$.
+We define the future discounted reward at time t as $R_t = \sum_{\hat{t}=t}^{T'} \gamma^{\hat{t}-t}r_{\hat{t}}$ , where $T'$ is the step at which the task terminates.
+In our design, a compression task only has one step, detailed discussed in \ref{RL Design}}.
+
+{\color{revise3} We denote the optimal \emph{action-value function} as the maximum expected reward $ Q^{*}(\mathcal{E}(f_t), c; \theta) = \max_{\pi} \mathbb{E} \big[R_t \mid s_t=s,c_t=c,\pi\big]$ to learn the optimal compression strategy $\pi$, where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
+The optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $.
+Also, the optimal action-value function obeys an important identity known as the Bellman equation, and the optimal strategy is to select the action $c'$ maximising the expected value of $r + \gamma Q^{*}(s', c'; \theta) $ \cite{DQN}.}
+
+%The basic idea behind many reinforcement learning algorithms is to estimate the action-value function, by using the Bellman equation as an iterative update $ Q(s, c; \theta_{i}) = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $.
+
+%We denote the \emph{action-value function} as {\color{revise2} $ Q(\mathcal{E}(f_t), c; \theta) $} \iffalse $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi and the optimal compression quality level at time $ t $ as {\color{revise2} $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $} \iffalse $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
+
 In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where {\color{revise2} state $ s = \mathcal{E}(f_i) $} and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $.
@@
 {\color{revise2} In iteration $t$, we  leverage the feature extractor $\mathcal{E}$ to obtain state $s_t = \mathcal{E}(J(x_t,c_{ref}))$.
-The RL agent $\phi$ generates a compresion quality level $c_t$.
+The RL agent $\phi$ generates a compression quality level $c_t$.
 The framework compresses image $x_t$ at quality $c_t$ to upload and obtains reward $r_t$.
@@
 The framework stores transition $(s_t, c_t, r_t, s_{t+1},\mathcal{A}_t )$ in a memory buffer $\mathcal{D}$.
-Especially, $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in the inference-estimation-querying-retraining mechanism to be discussed in Section \ref{subsec: mechanism}.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
+Especially, $(s_t, c_t, r_t, s_{t+1} )$ is used to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in the inference-estimation-querying-retraining mechanism to be discussed in Section \ref{subsec: mechanism}.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.
 The training procedure would converge when the agent's randomness keeps decaying.
@@
 
+%\setlength{\textfloatsep}{0.8cm}
 \begin{algorithm}[!t]
@@
 \end{algorithm}
+%\setlength{\textfloatsep}{0.8cm}
 
@@
 }
+\vspace{-0.2cm} 
 \end{figure*}
-
+%\vspace{-0.3cm}
 %\begin{figure}[!t]
@@
 }
+\vspace{-0.1cm} 
 \end{figure*}

### 2021-01-07 paper/sections/evaluation.tex
third response

@@
 For the cloud-based deep learning services, we choose Baidu Vision, Face++ object detection services and Amazon Rekognition.
-In the experiments, we use two datasets mentioned before in Subsection~\ref{subsec:insight}.
+{\color{revise3}For the compression framework, we choose the JPEG compression method and use PIL library \cite{pillow_benchmark} to complete the JPEG compression process, which can take the compression quality level input.
+Especially, each compression quality level represents a quantization table in JPEG compression standard \cite{jpeg}.} In the experiments, we use two datasets mentioned before in Subsection~\ref{subsec:insight}.
 The ImageNet dataset indicates daytime scenery, and the FLIR Thermal Dataset indicates nighttime scenery.
@@
 In the training phase, to train the agent while remaining a convincing recognition result, AdaCompress has to upload the original image along with the compressed image to the cloud-end, obtaining the real result and the reward feedback.
-Therefore the upload traffic load is even higher than the conventional solution.
-But once the training phase has finished, the upload traffic load is lower than the benchmark.
+\textcolor{revise3}{Therefore the upload traffic load is even higher than the conventional solution, and the accuracy is locked to 1 because AdaCompress uses the original image’s prediction label as the output result.} But once the training phase has finished, the upload traffic load is lower than the benchmark.
 As shown in Figure~\ref{fig: compress_performance}, in the inference phase, AdaCompress's upload size is only 1/2 of the benchmark's.
 %% \\
-
+%Therefore the upload traffic load is even higher than the conventional solution.
 \subsection{Size Reduction and Accuracy Performance}
@@
 	\label{fig: running-retrain}
+\vspace{-0.1cm} 
 \end{figure}
@@
 The mechanism still uses the old RL agent to choose a compression quality level before the re-loading process has finished.}
+
+\subsection{Applicability for Different Image Compression Methods}
+
+{\color{revise3} In our experiment, we choose the JPEG compression method as the compression framework.
+Furthermore, our framework is applicative for different image compression techniques, both traditional compression methods and neural network-based learned compression methods.
+Existing traditional compression methods all have an optional compression level, e.g., JPEG and WebP have the compression quality level, H.265/HEVC \cite{hevc} and H.266/VVC \cite{vvc} have the quantization parameter (QP).
+Neural network-based learned image compression is a Lagrangian multiplier-based rate-distortion optimization, which commonly has a tradeoff parameter that controls the rate-distortion tradeoff \cite{endtoend1,endtoend2,endtoend3,endtoend4}.
+Different values are corresponding to different bit rates.
+We can regard this tradeoff parameter as the compression level.
+These different compression techniques all can flexibly take a compression level as the input.}

### 2021-01-07 paper/sections/relatedwork.tex
third response

@@
 Baluja et al.~\cite{baluja2019task} proposed task-specific compression that compresses images based on the end-use of images.
-%% \\
+{\color{revise3}Yang et al.~\cite{endtoend} suggested using a powerful regularization to optimize the loss function in the end-to-end compression framework by considering the downstream perception task.} %% \\
 
-However, such proposals all need one to understand the characteristics of the cloud-based deep learning model and have access to the original training dataset,  \emph{generating} the appropriate compression schemes.
-To the best of our knowledge, we are the first to propose an adaptive compression configuration solution that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.
+{\color{revise3}However, such proposals all need one to understand the characteristics of the cloud-based deep learning model or details of the compression framework, and have access to the original training dataset, \emph{generating} the appropriate compression schemes.
+To the best of our knowledge, we are the first to propose an adaptive compression configuration solution that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures and the compression framework.}
 
@@
 Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).
-
 %Liu et al.~\cite{DeepN-JPEG} developed the DeepN-JPEG framework, a deep %neural network favorable JPEG-based image compression framework.

### 2021-01-10 paper/sections/design.tex
third revision

@@
 For a reference compression quality level $ c_{\rm ref} $, the compressed file size is {\color{revise2} $ \hat{s}_{\rm ref} $}.
+{\color{revise3}Besides JPEG compression method, our framework is applicative for different image compression techniques, both traditional compression methods \cite{jpeg,webp,hevc,vvc} and neural network-based learned compression methods \cite{endtoend1,endtoend2,endtoend3,endtoend4}, which all have an optional compression level (rate-distortion tradeoff parameter).}
+
 Besides, the input image from a specific scenery usually belongs to a particular contextual group~\cite{mcdnn}.
@@
 
-{\color{revise3} We start by giving some basics on Markov decision processes (MDPs) \cite{MDP}, which is represented by a tuple $<S,C,P,R,\gamma>$, where $S$ denotes a set of possible states $s$, $C$ a set of feasible actions $c$, $P$ the set of state transition probabilities, $R$ a reward function, and $\gamma$ a discount factor.
+{\color{revise3} We start by giving some basics on Markov decision processes (MDPs) \cite{MDP}, which is represented by a tuple $<S,C,P,R,\gamma>$, where $S$ denotes a set of possible states $s$, $C$ a set of feasible actions $c$, $P$ the set of state transition probabilities, $R$ a future reward function, and $\gamma$ a discount factor.
 We formulate the feature extractor's output  $ s = \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}.
 In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $.
-We use $P_{ss'}^{c} = P \big[s' \mid s, c = \pi(s) \big]$ to denote the state transition probability from state $s$ to $s'$, where $\pi$ is a compression strategy mapping state to actions.
-We therefore obtain a sequence of states and actions $\{ s_1,c_1,s_2,...,c_{t-1},s_t \}$, and this formulation is a MDP.}
+In our design, a compression task only has one step, detailed discussed in \ref{RL Design}.
+Therefore the next state and current action are only related to the current state, not to the historical states (i.e., $P_{s_{t}s_{t+1}}^{c_{t}} = P [s_{t+1} \mid s_{t}, c_t , s_{t-1}, c_{t-1},...
+] = P [s_{t+1} \mid s_{t}, c_t ] ; P [ a_{t} \mid s_{1},s_{2},...,s_{t},a_{1},a_{2},...a_{t-1}] = P [ a_{t} \mid s_{t} ]$ ), satisfying Markov property.}
 
-{\color{revise3} The goal of the agent is to interact with the emulator environment $ \{\mathcal{X}, M\} $ by selecting actions in a way that maximises future reward $R$.
-We define the future discounted reward at time t as $R_t = \sum_{\hat{t}=t}^{T'} \gamma^{\hat{t}-t}r_{\hat{t}}$ , where $T'$ is the step at which the task terminates.
-In our design, a compression task only has one step, detailed discussed in \ref{RL Design}}.
+%Therefore the next state is only  We use $P_{ss'}^{c} = P \big[s' \mid s, c = \pi(s) \big]$ to denote the state transition probability from state $s$ to $s'$, where $\pi$ is a compression strategy mapping state to actions.
+%
+%We therefore obtain a sequence of states and actions $\{ s_1,c_1,s_2,...,c_{t-1},s_t \}$, and this formulation is a MDP.}
 
-{\color{revise3} We denote the optimal \emph{action-value function} as the maximum expected reward $ Q^{*}(\mathcal{E}(f_t), c; \theta) = \max_{\pi} \mathbb{E} \big[R_t \mid s_t=s,c_t=c,\pi\big]$ to learn the optimal compression strategy $\pi$, where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
+{\color{revise3} The goal of the agent is to interact with the emulator environment $ \{\mathcal{X}, M\} $ by selecting actions in a way that maximizes future reward $R$.
+We define the future discounted reward at time t as $R_t = \sum_{\hat{t}=t}^{T'} \gamma^{\hat{t}-t}r_{\hat{t}}$ , where $T'$ is the step at which the task terminates.}{\color{revise3} We denote the optimal \emph{action-value function} as the maximum expected reward $ Q(\mathcal{E}(f_t), c; \theta) = \max_{\pi} \mathbb{E} \big[R_t \mid s_t=s,c_t=c,\pi\big]$ to learn the optimal compression strategy $\pi$, where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
 The optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $.
-Also, the optimal action-value function obeys an important identity known as the Bellman equation, and the optimal strategy is to select the action $c'$ maximising the expected value of $r + \gamma Q^{*}(s', c'; \theta) $ \cite{DQN}.}
+Also, the optimal action-value function obeys an important identity known as the Bellman equation, and the optimal strategy is to select the action $c'$ maximising the expected value of $r + \gamma Q(s_{t+1}, c'; \theta) $ \cite{DQN}.}
 
@@
 
-In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where {\color{revise2} state $ s = \mathcal{E}(f_i) $} and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $.
+%In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where {\color{revise2} state $ s = \mathcal{E}(f_i) $} and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $.
 Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over {\color{revise2} state} \iffalse sequences \fi $ s $ and the compression quality level $ c $~\cite{DQN}.
 When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.
+In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_t(\theta_t) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_t - Q(s, c; \theta_t)\big)^2 \Big] $ that changes at each iteration $ t $ where {\color{revise2} state $ s = \mathcal{E}(f_t) $} and target $ y_t = \mathbb{E}_{s^{t+1} \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s_{t+1}, c'; \theta_{t-1}) \mid s, c \big] $.
+Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over {\color{revise2} state} \iffalse sequences \fi $ s $ and the compression quality level $ c $~\cite{DQN}.
+When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_t $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.
 
@@
 }
-\vspace{-0.2cm} 
+%\vspace{-0.2cm} 
 \end{figure*}
@@
 %\end{figure}
+
+\begin{figure*}[!t]
+	{\color{revise}
+		\begin{minipage}[t]{0.48\linewidth}
+			\centerline{\includegraphics[width=7cm]{figures/ImageNet_Baidu_choices.pdf}}
+			\centerline{(a) ImageNet images}
+		\end{minipage}
+		\hfill
+		\begin{minipage}[t]{0.48\linewidth}
+			\centerline{\includegraphics[width=7cm]{figures/FLIR_Baidu_choices.pdf}}
+			\centerline{(b) FLIR images}
+		\end{minipage}	
+		\caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different scenery image inputs}}
+		\label{fig: dataset_change}
+	}
+	\vspace{-0.2cm} 
+\end{figure*}
 
@@
 %\end{figure}
-
-\begin{figure*}[!t]
-{\color{revise}
-	\begin{minipage}[t]{0.48\linewidth}
-		\centerline{\includegraphics[width=7cm]{figures/ImageNet_Baidu_choices.pdf}}
-		\centerline{(a) ImageNet images}
-	\end{minipage}
-	\hfill
-	\begin{minipage}[t]{0.48\linewidth}
-		\centerline{\includegraphics[width=7cm]{figures/FLIR_Baidu_choices.pdf}}
-		\centerline{(b) FLIR images}
-	\end{minipage}	
-    \caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different scenery image inputs}}
-	\label{fig: dataset_change}
-}
-\vspace{-0.1cm} 
-\end{figure*}
 

### 2021-01-10 paper/sections/evaluation.tex
third revision

@@
 	\label{fig: compare_image}
+\vspace{-0.2cm}
 \end{figure*}
@@
 
-\subsection{Applicability for Different Image Compression Methods}
-
-{\color{revise3} In our experiment, we choose the JPEG compression method as the compression framework.
-Furthermore, our framework is applicative for different image compression techniques, both traditional compression methods and neural network-based learned compression methods.
-Existing traditional compression methods all have an optional compression level, e.g., JPEG and WebP have the compression quality level, H.265/HEVC \cite{hevc} and H.266/VVC \cite{vvc} have the quantization parameter (QP).
+%\subsection{Applicability for Different Image Compression Methods}
+%
+%{\color{revise3} In our experiment, we choose the JPEG compression method as the compression framework.
+Furthermore, our framework is applicative for different image compression techniques, both traditional compression methods \cite{jpeg,webp,hevc,vvc} and neural network-based learned compression methods \cite{endtoend1,endtoend2,endtoend3,endtoend4}, which all have an optional compression level ( we can use this as the agent's action in our solution).
+%	
+%Existing traditional compression methods all have an optional compression level, e.g., JPEG and WebP have the compression quality level, H.265/HEVC \cite{hevc} and H.266/VVC \cite{vvc} have the quantization parameter (QP).
 Neural network-based learned image compression is a Lagrangian multiplier-based rate-distortion optimization, which commonly has a tradeoff parameter that controls the rate-distortion tradeoff \cite{endtoend1,endtoend2,endtoend3,endtoend4}.
